---
title: "Fuel sample size"
author: "Laura Kwong"
date: "November 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(epiR)
```


exposed	= the expected incidence risk (cumulative incidence) for exposed subjects (see below).

unexposed	= the expected incidence risk (cumulative incidence) for unexposed subjects (see below).

n	= scalar, defining the total number of subjects in the study (i.e. the number in the exposed and unexposed groups).

power	= scalar, the required study power.

r	= scalar, the number in the treatment group divided by the number in the control group. This argument is ignored when method = "proportions".

design = scalar, the estimated design effect.

Calculate the design effect, given rho = (design - 1) / (nbar - 1) so design = rho * (nbar - 1) + 1
where rho is the inter-cluster correlation and nbar equals the average number of individuals per cluster:

sided.test = use a one- or two-sided test? Use a two-sided test if you wish to evaluate whether or not the treatment group is better or worse than the control group. Use a one-sided test to evaluate whether or not the treatment group is better than the control group.

conf.level = scalar, defining the level of confidence in the computed result.

output: lambda = the outcome proportion in the exposed group divided by the outcome proportion in the unexposed group (a risk ratio).

## Rohingya fuel sample size calculation based on prevalence of pneumonia

ICC is 0.1 (Mortimer, 2017 - clean cookstoves in Malawi)

```{r}
ICC <- 0.1

n.per.cluster <- 1 # cluster = one structure, which has 3 hh 

design <- ICC * (n.per.cluster - 1) + 1

epi.cohortsize(
  exposed = 0.47, # exposed means exposed to the intervention
  unexposed = 0.55,  # 55% of control hh have respiratory complaints
  n = NA, 
  power = 0.90, 
  r = 1, 
  design = design, 
  sided.test = 2, 
  conf.level = 0.95
)
```
With an average of 1 child/cluster, you need 1048 total children to detect a 10% difference at 90% power. 

With an average of 1 child/cluster, you need 462 total children to detect a 15% difference at 90% power. 

With an average of 1 child/cluster, you need 1638 total children to detect a 8% difference at 90% power. 


With an average of 2 children/cluster, you need 862 total children -> 862 hh surveys in 862/2 = 431 sturctures




Note from before when I was using sub-blocks as clusters 
I don't know how many total sub-blocks there are, but there are 20-24 sub-blocks per block and each camp has 20+ blocks so there are at least 400 sub-blocks. 


Calculation for IUCN, which probably has more money:
With a power of 90% With an average of 1 children/cluster, you need 1048 total children to detect a change of 10%. 









# Sample size based on firewood use

treat	= the expected value for the treatment group (see below).

control	= the expected value for the control group (see below).

n	= scalar, defining the total number of subjects in the study (i.e. the number in the treatment and control group).

sigma	= the expected standard deviation of the variable of interest for both treatment and control groups.

power	= scalar, the required study power.

r	= scalar, the number in the treatment group divided by the number in the control group. This argument is ignored when method = "proportions".

design = scalar, the estimated design effect.

Calculate the design effect, given rho = (design - 1) / (nbar - 1) so design = rho * (nbar - 1) + 1
where rho is the inter-cluster correlation and nbar equals the average number of individuals per cluster:

sided.test = use a one- or two-sided test? Use a two-sided test if you wish to evaluate whether or not the treatment group is better or worse than the control group. Use a one-sided test to evaluate whether or not the treatment group is better than the control group.

conf.level = scalar, defining the level of confidence in the computed result.

output: delta	= the minimum detectable difference given the specified level of confidence and power.


# Rohingya sample size based on reduction in PM
```{r}

ICC <- 0.1

n.per.cluster <- 1 # cluster = one structure, which has 4 hh 

design <- ICC * (n.per.cluster - 1) + 1

epi.meansize(
  treat = 200, # LPG hh 101 mg/m3 (sd = 130)
  control = 400, # control hh 400 mg/m3 
  n = NA, 
  sigma = 640, # pooled sd 640 mg/m3 
  power = 0.90, 
  r = 1, 
  design = design,
  sided.test = 2, 
  conf.level = 0.95
  )

212*1.10
```

PM needs to be measured for 2 days/hh. Given the need to collect and recharge (for which we allow 1 extra day), the fastest that all hh could be measured is 
```{r}
((233*3/2)/2) / 20 

```

335 days. Considering 20 working days per month and two PM monitors, this is 9 months




Stove use monitoring system

```{r}
ICC <- 0.1

n.per.cluster <- 1 # cluster = one structure, which has 3 hh 

design <- ICC * (n.per.cluster - 1) + 1

epi.meansize(
  treat = 150, # Pillarsetti_2004: Post-introduction of a clean--burning biomass cooking stove, 9 hh that exclusively used the stove in the first month used it for an average of 111 minutes/day (SD not given). This decreased to 78 min (SD not given) of the clean cookstove + 52 min of the traditional stove (SD not given) (130 min total) after a few months  
  control = 200, # Pillarsetti_2004: Pre-intervention traditional stove use averaged 209 min/day (SD = 105; 177 homes measured for an average of 34 days each)
  n = NA, 
  sigma = 100,
  power = 0.90, 
  r = 1, 
  design = design, 
  sided.test = 2, 
  conf.level = 0.95
)

170/(50/3.2)
```
With 85 households per arm, we can detect a mean difference in cooking time of 50 min, assuming a standard deviation of 100 minutes, power of 90% and confidence level of 95%. 

Each hh needs to be measured for at least 2 weeks, preferably one month, so we need 170 months of monitoring. With 50 monitors (3.2 per LPG/control pair), it would take 170/(50/3.2) = 11 months. 
 
 
 # Rohingya sample size based on fuel reduction by HOUSEHOLD (Assume initial is 0.8/person/day * 5 ppl; want 20% reduction to 0.64/person/day)
```{r}

ICC <- 0.1

n.per.cluster <- 2 # cluster = one structure, which has 4 hh 

design <- ICC * (n.per.cluster - 1) + 1

epi.meansize(
  treat = 0.745 * 5, # treatment 0.745 kg firewood/person/day for a 5-person family
  control = 0.80 * 5, # control 0.80 kg firewood/person/day for a 5-person family
  n = NA, 
  sigma = 1, 
  power = 0.80, 
  r = 1, 
  design = design,
  sided.test = 2, 
  conf.level = 0.95
  )

# Difference per family/day = 0.275 kg/family/day

# (0.80*5-0.745*5)*7 = 0.385
# 0.385*5 = 1.925 kg / family / kg

epi.meansize(
  treat = NA, 
  control = NA, 
  n = 431 * 1.5, # Not sure why I have to multiple by 1.5 to get close to the correct n.total
  sigma = 1, 
  power = 0.80, 
  r = 1, 
  design = design,
  sided.test = 2, 
  conf.level = 0.95
  )
```


With 1176 clusters (hh structures), min diff is 0.16 kg of fuel per household/day

 
 # Radon measurements
 We have two radon monitors and they need to be at each home for 1 week. The ventilation project will be finished with the monitors by Feb 2020, so they can be sampling homes for up to 16 months. Subtract 4 weeks for holidays, charging, maintenance, etc. 
 
```{r}
 16*4*2
```
We could measure 128 housing structures. 











COVID mask study

```{r}
ICC <- 0.2

n.per.cluster <- 100 # cluster = one structure, which has 3 hh 

design <- ICC * (n.per.cluster - 1) + 1

epi.ssxsectn(
  pexp1 = NA, # exposed means exposed to the intervention
  pexp0 = 0.25,  # 55% of control hh have respiratory complaints
  n = 20000, 
  power = 0.80, 
  r = 1, 
  design = design, 
  sided.test = 2, 
  conf.level = 0.95
)
```