---
title: 
author: 
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
# Libraries
library(tidyverse)
library(lubridate)

# Parameters

file_events <- here::here("data-raw/Geocene/events.csv")
file_mission_logs <- here::here("data-raw/Geocene/mission_logs.csv")
file_missions <- here::here("data-raw/Geocene/missions.csv")
file_sensors <- here::here("data-raw/Geocene/sensors.csv")
file_tags <- here::here("data-raw/Geocene/tags.csv")

list_of_file_path_geocene <- here::here("data-raw/Geocene/metrics") 

file_survey_data_base <- here::here("data", "RohingyaFuelMaster_tidy_long.rds")

#===============================================================================

df_events <- read.csv(file_events)
df_mission_logs <- read.csv(file_mission_logs)
df_missions <- read.csv(file_missions)
df_sensors <- read.csv(file_sensors)
df_tags <- read.csv(file_tags)

survey_data <- read_rds(file_survey_data_base) %>% select(timepoint, study_arm_overall, fcn_id, camp_id, block_id, subblock_id, first_enrolled_lpg, first_receive_lpg)
```

## load files
```{r}
# list_of_file_geocene <-   
# 	list.files(
# 		path = list_of_file_path_geocene,
# 		recursive = TRUE, 
# 		pattern = "*.csv", 
# 		full.names = TRUE 
# 	)

# length(list_of_file_geocene) #134
```


### get by hh

processors

cooking_time_50_70C_3_40min
stove_on_50_70C_3_3min
 - for this select only stove_on

```{r}
df_mission_id_to_analyze_base <-
	df_tags %>%
	# filter(tag %notin% c("practice", "not_normal", "empty")) %>%
	mutate(
				study_arm_overall =
			case_when(
				tag == "intervention_period:pre_intervention" ~ "intervention",
				tag %in% c("intervention_period:intervention", "intevention_period:intervention") ~ "comparison" # Note that intervention is misspelled in the tag
			),
		fuel_type = 
			case_when(
		tag == "fuel_type:biomass" ~ "biomass",
		tag == "fuel_type:lpg" ~ "lpg"
		)
		)
	
mission_id_study_arm_overall <-
	df_mission_id_to_analyze_base %>%
	filter(!is.na(study_arm_overall)) %>%
		select(-c(tag, fuel_type))

mission_id_fuel_type <-
	df_mission_id_to_analyze_base %>%
	filter(!is.na(fuel_type)) %>%
		select(-c(tag, study_arm_overall))

df_mission_id_to_analyze <-
	mission_id_study_arm_overall %>%
	left_join(mission_id_fuel_type, by = c("mission_id"))

	
# get the mission_name (which includes the hhid) associated with each mission id
# CF_20191013_0_10GG38108799_11:00

df_missions_hh_id <-
	df_missions %>%
	separate("mission_name", into = c("nothing_1", "date", "study_arm_overall_numeric", "hh_id", "start_time"), sep = "_", remove = FALSE) %>%
	
	# there have incorrect hh_ids so remove for now
	filter(
		mission_id %notin% 
			c(
				"5d8d140d-0000-0000-0000-806FB0636675",
				"5d8f5e42-0000-0000-0000-806FB0636675",				
				"5d901f23-0000-0000-0000-806FB063449C",				
				"5d902936-0000-0000-0000-806FB0636675",
				"5f7d5f6c-0000-0000-0000-806FB06347B3",
				"5f7d5fd1-0000-0000-0000-806FB06369A3",
				"5d77cb8a-0000-0000-0000-806FB06367DD",
				"5d79e91e-0000-0000-0000-806FB063698F",				
				"5d79f0de-0000-0000-0000-806FB06367DD",
				"5d7e7e84-0000-0000-0000-806FB06369B4",
				"5dad34dc-0000-0000-0000-806FB0636187",
				"5dbd2046-0000-0000-0000-806FB063449C",
				"5dbd12a8-0000-0000-0000-806FB06347D5",
				"5dc8f6bc-0000-0000-0000-806FB0636794",
				"5d7de18d-0000-0000-0000-806FB063667A",
				"5d7a928a-0000-0000-0000-806FB063698F",
				"5d7a7527-0000-0000-0000-806FB06369B2",			
				"5d77e4bf-0000-0000-0000-806FB06367DD",
				"5d769836-0000-0000-0000-806FB06367DD",
				"5dd4e462-0000-0000-0000-806FB0636397",			
				"5dd4e46f-0000-0000-0000-806FB0636397",
				"5dd77254-0000-0000-0000-806FB0635AF6",
				"5dd8ece8-0000-0000-0000-806FB06367C8",
				"5dd8e8e3-0000-0000-0000-806FB0636995",
				"5dda053f-0000-0000-0000-806FB063426D"
			)
	) %>%
		mutate(fcn_id = str_extract(hh_id, ".{6}$") ) %>%
	select(mission_id, hh_id, fcn_id)
	


df_events_stove_on <-
	df_missions_hh_id %>%
	left_join(df_events, by = "mission_id") %>%
	right_join(df_mission_id_to_analyze, by = "mission_id") %>% # keep only those mission_ids that have the correct tags
	# separate(mission_id, into = c("fcn_id", "nothing_1", "nothing_2", "nothing_3", "sensor"), sep = "-", extra = "merge", remove = FALSE)
	filter(processor_name == "stove_on_50_70C_3_3min") %>%
	# convert start_time to date so I can analyze events by date # 2019-09-24T13:19:06Z
	mutate(date = ymd(str_extract(start_time, "^[0-9]{4}-[0-9]{2}-[0-9]{2}"))) %>%
	ungroup() %>%
	
	group_by(study_arm_overall, hh_id, fcn_id, fuel_type, date) %>% # study_arm_overall
	count(fuel_type) %>% # count number of cooking events for each fuel type
	pivot_wider(names_from = fuel_type, values_from = n) %>%
	mutate(
		exclusive_lpg = if_else(is.na(biomass), TRUE, FALSE),
		exclusive_biomass = if_else(is.na(lpg), TRUE, FALSE),
		mixed_use = if_else(!is.na(biomass) & !is.na(lpg), TRUE, FALSE)
		) # %>%
	# filter(mission_id == "5d7dbb50-0000-0000-0000-806FB0635AC1")
```


Missions ids that have problems with mission name such that cannot extract fcn_id

5d8d140d-0000-0000-0000-806FB0636675
5d8f5e42-0000-0000-0000-806FB0636675				
5d901f23-0000-0000-0000-806FB063449C				
5d902936-0000-0000-0000-806FB0636675
5f7d5f6c-0000-0000-0000-806FB06347B3
5f7d5fd1-0000-0000-0000-806FB06369A3
5d77cb8a-0000-0000-0000-806FB06367DD
5d79e91e-0000-0000-0000-806FB063698F				
5d79f0de-0000-0000-0000-806FB06367DD
5d7e7e84-0000-0000-0000-806FB06369B4
5dad34dc-0000-0000-0000-806FB0636187
5dbd2046-0000-0000-0000-806FB063449C
5dbd12a8-0000-0000-0000-806FB06347D5
5dc8f6bc-0000-0000-0000-806FB0636794
5d7de18d-0000-0000-0000-806FB063667A
5d7a928a-0000-0000-0000-806FB063698F
5d7a7527-0000-0000-0000-806FB06369B2			
5d77e4bf-0000-0000-0000-806FB06367DD
5d769836-0000-0000-0000-806FB06367DD
5dd4e462-0000-0000-0000-806FB0636397			
5dd4e46f-0000-0000-0000-806FB0636397
5dd77254-0000-0000-0000-806FB0635AF6
5dd8ece8-0000-0000-0000-806FB06367C8
5dd8e8e3-0000-0000-0000-806FB0636995
5dda053f-0000-0000-0000-806FB063426D
















should have a marker for whether or not the hh had LPG dep on survey data 
first_enrolled_lpg
first_receive_lpg


# Of course, not working well, 
```{r, eval=FALSE}

# survey_data %>% filter(!is.na(first_enrolled_lpg)) %>% select(timepoint, fcn_id, first_enrolled_lpg, first_receive_lpg) %>%
# 	left_join(df_events_stove_on, by = "fcn_id")

survey_data %>%
		filter(!is.na(first_enrolled_lpg)) %>%
	mutate(
		first_enrolled_lpg_ymd = dmy(as.character(first_enrolled_lpg)),
				 first_receive_lpg_ymd = dmy(as.character(first_receive_lpg))
		) %>%

	select(fcn_id, first_enrolled_lpg_ymd, first_receive_lpg_ymd)
	filter(fcn_id %in% c(no_exclusive_use_fcn_id)) %>%
	
```


# For now, assume that all baseline hh received LPG by 10/15 since last survey in pre-intervention group was 10/1
```{r}

exclusive_use <-
   df_events_stove_on %>%
	ungroup() %>%
	mutate(
		lpg_enrolled = 
				 	case_when(
				 		study_arm_overall == "comparison" ~ TRUE,
				 		study_arm_overall == "intervention" & date > "2019-12-15" ~ TRUE,
				 		TRUE ~ FALSE # defaul to false
				 		)
		) %>%
	
	# examine exclusive use only when the hh was receiving LPG
	filter(lpg_enrolled == TRUE) %>%
	
	# what percent of days did the hh exclusively use LGP
	group_by(study_arm_overall, lpg_enrolled, fcn_id) %>%
	summarise(mean = mean(exclusive_lpg == TRUE, na.rm = TRUE),
						sd = mean(exclusive_lpg == TRUE, na.rm = TRUE)
						)
	
exclusive_use %>%
tabyl(study_arm_overall)



no_exclusive_use_fcn_id <-
	exclusive_use %>%
	filter(mean == 0) %>% pull(fcn_id)
	
fig_exclusive_use <-
	exclusive_use %>%
	mutate(
		study_arm_overall = 
				 	ordered(
				 		study_arm_overall,
				 		levels = c("intervention", "comparison"),
				 		labels = c("Intervention", "Comparison"),
				 	)
				 ) %>%
	ggplot(aes(x = study_arm_overall, y = mean, color = study_arm_overall)) + 
	# geom_boxplot() + 
	geom_jitter(size = 2) +
	viridis::scale_fill_viridis(
	discrete = TRUE,
	end = 2/3
) +
	scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
		scale_color_manual(
		name = "Group",
		breaks = c("Intervention", "Comparison"),
		# labels = c("Pre-intervention", "Intervention", "Outdoor"),
		labels = c("Intervention", "Comparison"),
		values = c("#138b87",  "#430154"),
		# values = c("#7570b3",  "#d95f02", "#1b9e77")
	) +
	theme_classic() +
	theme(
		# axis.text.x = element_text(angle = 0, hjust = 1)
		# axis.text.x = element_blank(),
		# axis.ticks.x = element_blank(),
		# axis.line.x = element_blank(),
		legend.position = "none"
		# legend.position = "bottom",
		# legend.direction = "horizontal"
	) + 
	guides(
		color = guide_legend(title.position="top", title.hjust = 0.5)
	) +
	labs(
		title = "Households' exclusive use of LPG, \nafter enrollment into LPG distribution program",
		x =  "", # "Health category",
		y = "Percent of days LPG used exclusively"
	) 


fig_exclusive_use

ggsave(
	here::here("docs", "fig_exclusive.png"),
	plot = last_plot(),
	scale = 1,
	height = 6,
	width = 10,
	units = "in",
	device = "png"
)

exclusive_use %>% 
	group_by(study_arm_overall) %>%
	summarise(mean = mean(mean, na.rm = TRUE), sd = sd(mean, na.rm = TRUE))
```
study_arm_overall  n   percent
        comparison 81 0.4628571
      intervention 94 0.5371429
      
      Average exclusive use 94% in comparison and 85% in intervention group





