---
title: "PM2.5 weighted exposures"
author: "Chris LeBoa"
date: "7/3/2022"
output: html_document
---
## Analysis Objective
    This file is meant to summarize PM2.5 data collected from the PATS+ particulate monitors and find the amount of time people spend inside in order to create a time weighted analysis for the HAPIT shinyapp https://householdenergy.shinyapps.io/hapit3/ which outputs the number of DALYs and deaths averted due to a clean cookstove intervention. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```



#Data Preparation
    
##Read in data 

```{r}

#pm2.5 data 
pm_data_hour_csv <- here::here("4_data/pm_data_hour.csv") #this file is created in the 1_PM2.5_analysis_rohingya.rmd file in the scripts folder

pm_data_hour <- read_csv(pm_data_hour_csv)

pm_data_hour %>% 
  count(timepoint, study_arm, note)

#paired survey data 

file_survey_data_base <- here::here("4_data/RohingyaFuel_survey_data_triple.rds")
#This file is the paired survey data containing baseline and midline survey responses on a hh level

survey_data <- read_rds(file_survey_data_base)

#individual level midline survey data (at basline asked for single response per household. At midline asked for a response per hh member)
all_files <-
  list.files(path = "/Volumes/GoogleDrive/.shortcut-targets-by-id/1g4FGyxS0paoGycT8REXc9ZEXkWLVDMJr/Rohingya_analysis/2_data_raw", pattern = ".csv", full.names = TRUE)
#finds all files from raw folder with .csv pattern


selected_files <-
  all_files[str_detect(all_files, "location")]
#selects files with location in the name

midline_location_repeat <-
  selected_files %>%
  map_dfr(read_csv, col_types = cols(.default = "c", hours_inside = "d", hours_outside = "d"))
#reads in all selected files

## Individual level endline data 
all_files_endline <-
  list.files(path = "/Volumes/GoogleDrive/.shortcut-targets-by-id/1g4FGyxS0paoGycT8REXc9ZEXkWLVDMJr/Rohingya_analysis/2_data_raw/survey_endline_with_review", pattern = ".csv", full.names = TRUE)

selected_files_endline <-
  all_files_endline[str_detect(all_files_endline, "hh_members")]
#selects files with hh_members in the name becuase that is where the hours outside variable is 

endline_location_repeat <-
  selected_files_endline %>%
  map_dfr(
    read_csv,  
    col_types = cols(
      mem_serial = "c", 
      hhh_relation = "c",
      hhh_reln_dmmy = "c", 
      age_yrs = "d", 
      sex = "d", 
      .default = "c", 
    #  hours_inside = "d",
      hours_outside = "d"
      ))


#output file location 
 file_location_out <- here::here("4_data/weighted_pm2.5_av.csv")

```

```{r}
midline_location_clean <-
midline_location_repeat %>%
  mutate(
       hours_inside_mid= if_else(is.na(hours_inside) == TRUE, 24 - hours_outside, hours_inside),
       hours_outside_mid = if_else(is.na(hours_outside) == TRUE, 24 - hours_inside, hours_outside)
  ) 
  #select(KEY, PARENT_KEY, locatihours_inside, hours_outside_mid)
#Some versions had only hours inside and the endline had only hours outside so setting them all to have both with inside + outside == 24

endline_location_clean <-
endline_location_repeat %>%
  mutate(
       hours_inside_end = 24 - hours_outside,
       hours_outside_end = hours_outside
  )

 
  

```


##Clean data 
```{r}

joined_data <-
  midline_location_clean%>%
  full_join(survey_data, by = c("PARENT_KEY" = "KEY"))

joined_data_endline <-
  survey_data %>% 
  filter(timepoint == "endline") %>% 
  full_join(endline_location_clean, by = c("KEY" = "PARENT_KEY"))


joined_data %>% 
  count(hours_outside_mid, name_respondent)

joined_data_endline %>% 
  count(hours_outside_end, name_respondent, timepoint)


#This was useful when using midline data
#  survey_data <- 
#   survey_data %>% 
#    mutate(
# #     #timepoint = if_else(timepoint == "endline", "midline", "baseline"), 
#    study_arm = if_else(str_detect(study_arm, "pre-|post-") == TRUE, "intervention", "comparison")) 

pm_group <- 
pm_data_hour %>% 
  group_by(timepoint, study_arm) %>% 
  summarize(
    pm_group = mean(PM_Estimate, na.rm = TRUE), 
    sd_pm_group = sd(PM_Estimate, na.rm = TRUE),
    )


#survey_data$KEY
#endline_location_clean$PARENT_KEY
#from overall survey data find columns needed to specify hh members at midline  
```
## Check all timepoints in the data io make sure all accounted for 


#Rough weighted mean assuming outside time was the same at all timepoints based on baseline time outsides 
```{r}

hours_baseline <- 
survey_data %>% 
  group_by(study_arm_overall, timepoint) %>% 
  summarise(
    mean_hr_inside_hh = mean(hours_inside, na.rm = TRUE), 
    sd_resp = sd(hours_inside, na.rm = TRUE), 
    child_mean_hour_inside = 24 - mean(target_child_hours_outside, na.rm = TRUE), 
    sd_child_mean_hour_inside = sd(target_child_hours_outside, na.rm = TRUE)
    ) %>% 
  filter(!is.na(mean_hr_inside_hh))

pm_outdoor <- 
  pm_group %>% 
  filter(study_arm == "outdoor") %>% 
  mutate(outdoor_pm = pm_group) %>% 
  select(-c(pm_group, study_arm))

pm_group %>%
  left_join(hours_baseline, by = c("study_arm" = "study_arm_overall")) %>% 
  
  left_join(pm_outdoor, by = c("timepoint.x" = "timepoint")) %>% 
  mutate(
    respondent_weighted_pm = 
      pm_group * (mean_hr_inside_hh / 24) +
      outdoor_pm *((24 - mean_hr_inside_hh) / 24) , 
    child_weighted_pm = 
       pm_group * (mean_hr_inside_hh / 24) +
      outdoor_pm *((24 - mean_hr_inside_hh) / 24)
  ) %>% 
  filter(study_arm != "outdoor")
```


### baseline results 
At baseline we asked about the respondent and target child time outside only 

###respondent time outside
```{r}
respondent_baseline <- 
survey_data %>% 
  group_by(timepoint, study_arm_overall) %>% 
  summarise(mean_hr_outside_hh = mean(hours_outside)) %>% 
  filter(!is.na(mean_hr_outside_hh)) %>% 
  mutate(individual = "respondent")

target_child_baseline <- 
survey_data %>% 
  group_by(study_arm_overall, timepoint) %>% 
  summarise(mean_hr_outside_hh = mean(target_child_hours_outside)) %>% 
  filter(!is.na(mean_hr_outside_hh)) %>% 
  mutate(individual = "target child")
```

#midline results 
### respondent mean time outside 
```{r}
respondent_midline <- 
joined_data %>% 
  filter(location_name_roster == name_respondent) %>% 
  group_by(timepoint, study_arm_overall, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside_mid)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm_overall) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside)) %>% 
  mutate(individual = "respondent")
```
#target child mean time outside
```{r}
target_child_midline <- 
joined_data %>% 
  filter(location_name_roster == target_child_name) %>% 
  group_by(timepoint, study_arm_overall, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside_mid)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm_overall) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside)) %>% 
  mutate(individual = "target child")
```

#other adult time spent outside of hh
```{r}
other_member_midline <- 
joined_data %>% 
  filter(
    location_name_roster != target_child_name, 
    location_name_roster != name_respondent
    ) %>% 
  group_by(timepoint, study_arm_overall, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside_mid)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm_overall) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside)) %>% 
   mutate(individual = "other member")

```

#Endline results 
```{r}
respondent_endline <-  #respondent 
joined_data_endline %>% 
  filter(name == name_respondent) %>% 
  group_by(timepoint, study_arm_overall, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside_end)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm_overall) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside)) %>% 
  mutate(individual = "respondent")

target_child_endline <- #target child 
joined_data_endline %>% 
  filter(name == target_child_name) %>% 
  group_by(timepoint, study_arm_overall, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside_end)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm_overall) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside)) %>% 
  mutate(individual = "target child")

other_member_endline <- 
joined_data_endline %>% 
  filter(
    name != target_child_name, 
    name != name_respondent
    ) %>% 
  group_by(timepoint, study_arm_overall, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside_end)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm_overall) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside)) %>% 
   mutate(individual = "other member")

```






```{r}
data_hours_outside <- 
  bind_rows(
    respondent_baseline,
    target_child_baseline,
    respondent_midline,
    target_child_midline, 
    other_member_midline, 
    respondent_endline, 
    target_child_endline, 
    other_member_endline
    ) %>% 
  mutate(
    av_time_inside = 24 - mean_hr_outside_hh,
    pct_time_inside = av_time_inside / 24 * 100, 
    arm_time = str_glue("{timepoint}_{study_arm_overall}"))

```


# PM2.5 exposures 
instead of doing hh specific adjusted exposures we multiplied by study mean since not all hh had sensors in them. 
```{r}
#Create hh av pm 2.5 dataset
hh_av_pm2.5 <- 
  pm_data_hour %>% 
	group_by(timepoint, study_arm, hh_id) %>% 
	summarise(
		time_range = max(dateTime_hour) - min(dateTime_hour),
		hh_mean = mean(PM_Estimate),
		
		hh_sd = sd(PM_Estimate)
	) 
#   mutate(
#     timepoint = if_else(timepoint == "endline", "midline", "baseline")) %>% 
# 	ungroup() 

#summarize by study arm
arm_mean_pm2.5 <- 
  hh_av_pm2.5 %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(
		sensor_on_time = mean(time_range, na.rm = TRUE),
		mean_pm2.5_hh = mean(hh_mean), 
		sd_pm2.5_hh = sd(hh_sd), 
		n = n()
	) %>% 
  mutate(
    arm_time = str_glue("{timepoint}_{study_arm}")
  ) %>% 
  select(-timepoint)

outdoor_pm2.5 <- 
  arm_mean_pm2.5 %>% 
  filter(study_arm == "outdoor") %>% 
  transmute(
    timepoint,
    mean_pm2.5_outdoor = mean_pm2.5_hh
    )



pm_data_sum <-  
  pm_data_hour %>% 
  mutate(over_1000 = if_else(PM_Estimate >= 1000, 1, 0)) %>% 
  group_by(hh_id, study_arm, timepoint) %>% 
  summarize(time = max(dateTime_hour) - min(dateTime_hour), over_100_hours_24 = sum(over_100, na.rm = TRUE)/as.numeric(time), over_1000_hh = sum(over_1000, na.rm = TRUE)) 

# Number of hh with PM values < 1000 
pm_data_sum %>% 
  ungroup() %>% 
  count(over_1000_hh == 0)
108/(108+241) #hh with pm values over 1000

pm_data_sum %>% 
  ungroup() %>% 
  group_by(study_arm, timepoint) %>% 
  summarise(mean(over_100_hours_24, na.rm = TRUE))
```
### create weighted dataset of mean pm2.5 * percent time indoors for each group 
```{r}
combined_hr_outside_pm_weighted <- 
  data_hours_outside %>% 
  left_join(arm_mean_pm2.5, by = c("arm_time", "timepoint", "study_arm_overall" = "study_arm")) %>% 
  left_join(outdoor_pm2.5, by = "timepoint") %>% 
  mutate(
    weighted_mean_pm2.5_hh = 
      mean_pm2.5_hh * (pct_time_inside/100) + 
      mean_pm2.5_outdoor * ((100 - pct_time_inside)/100), 
    lower_non_weighted = mean_pm2.5_hh - 1.96 * sd_pm2.5_hh / sqrt(n), 
    upper_non_weighted = mean_pm2.5_hh + 1.96 * sd_pm2.5_hh / sqrt(n)
    )

#Outdoor 95% ci

outdoor_pm2.5 %>% 
mutate(
    lower_non_weighted = mean_pm2.5_hh - 1.96 * sd_pm2.5_hh / sqrt(n), 
    upper_non_weighted = mean_pm2.5_hh + 1.96 * sd_pm2.5_hh / sqrt(n))

write_csv(combined_hr_outside_pm_weighted, file_location_out)

combined_hr_outside_pm_weighted %>% 
  select(individual, timepoint, study_arm_overall, pct_time_inside, mean_pm2.5_hh, weighted_mean_pm2.5_hh, sd_pm2.5_hh) %>% 
  #filter(individual == "respondent") %>% 
  write_csv("/Users/ChrisLeBoa/Desktop/table_hapit_slide_endline.csv")
#%>% 
  # pivot_wider(names_from = timepoint, values_from = c(pct_time_inside, mean_pm2.5_hh, weighted_mean_pm2.5_hh))
```

### Time comparisons between cooking member and other hh Members

Took average between baseline and midline for these 
```{r}
#cooking person average time outside 
respondent_indoor <- 
  combined_hr_outside_pm_weighted %>% 
  ungroup() %>% 
  filter(individual == "respondent", timepoint == "baseline") %>% 
  summarise(mean(pct_time_inside)) %>% 
  pull()

#child u5 time outside hh
child_indoor <- 
combined_hr_outside_pm_weighted %>% 
  filter(individual == "target child",  timepoint == "baseline") %>% 
  summarise(mean(pct_time_inside)) %>% 
  pull()

#other adult time outside hh
adult_indoor <- 
combined_hr_outside_pm_weighted %>% 
  ungroup() %>% 
  filter(individual == "other member", timepoint == "midline") %>% 
  summarise(mean(pct_time_inside, na.rm = TRUE)) %>% 
  pull()

```

#Exposure ratios 

####Mother-Child (< 5) Exposure Ratio
 The scaling factor applied to user-input cook pre- and post-exposures to adjust under five children's exposures. The default value of 0.80 is based on smith 2014
 
Child/ respondent pct indoor ratio
```{r}
child_indoor/respondent_indoor
```

 
#### Cook to Other Adult Exposure Ratio
 The scaling factor applied to user-input cook pre- and post-exposures to adjust non-cook adults. The default value of 0.60 is based on the ratio of the men to women's exposures as described in Smith et al 2014.
 Other / respondent time indoor 
 
```{r}
adult_indoor/respondent_indoor
```

```{r}
survey_data$hh_size_2mo_u5

survey_data %>% 
  group_by(timepoint) %>% 
  summarize(
    mean(hh_size), 
    mean((hh_size_u2mo + hh_size_2mo_u5), na.rm = TRUE))
```

### Total hh targeted is 250,000 
Citation is here 
https://openaid.se/en/activities/SE-0-SE-6-12515A0102-BGD-15190
