---
title: "PM2.5 weighted exposures"
author: "Chris LeBoa"
date: "7/3/2022"
output: html_document
---
## Analysis Objective
    This file is meant to summarize PM2.5 data collected from the PATS+ particulate monitors and find the amount of time people spend inside in order to create a time weighted analysis for the HAPIT shinyapp https://householdenergy.shinyapps.io/hapit3/ which outputs the number of DALYs and deaths averted due to a clean cookstove intervention. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```



#Data Preparation
    
##Read in data 

```{r}

#pm2.5 data 
pm_data_hour_csv <- here::here("4_data/pm_data_hour.csv") #this file is created in the 1_PM2.5_analysis_rohingya.rmd file in the scripts folder

pm_data_hour <- read_csv(pm_data_hour_csv)

pm_data_hour %>% 
  count(timepoint)

#paired survey data 

file_survey_data_base <- here::here("4_data/RohingyaFuel_survey_data_triple.rds")
#This file is the paired survey data containing survey responses on a hh level

survey_data <- read_rds(file_survey_data_base)

#individual level midline survey data (at basline asked for single response per household. At midline asked for a response per hh member)
all_files <- 
  list.files(path = here::here("2_data_raw"), pattern = ".csv", full.names = TRUE)
#finds all files from raw folder with .csv pattern


selected_files <- 
  all_files[str_detect(all_files, "location")]
#selects files with location in the name

midline_location_repeat <- 
  selected_files %>% 
  map_dfr(read_csv, col_types = cols(.default = "c", hours_inside = "d", hours_outside = "d"))
#reads in all selected files 

 file_location_out <- here::here("4_data/weighted_pm2.5_av.csv")
 
 
 all_files <- 
  list.files(path = here::here("2_data_raw/survey_endline_with_review"), pattern = ".csv", full.names = TRUE)
#finds all files from raw folder with .csv pattern


selected_files <- 
  all_files[str_detect(all_files, "hh_members")]
#selects files with location in the name

endline_location_repeat <- 
  selected_files %>% 
  map_dfr(read_csv, col_types = cols(.default = "c", hours_inside = "d", hours_outside = "d"))
#reads in all selected files 



 file_location_out <- here::here("4_data/weighted_pm2.5_av.csv")

```

##Clean data 
```{r}
#Midline 
midline_location_clean <- 
midline_location_repeat %>% 
  mutate(
       hours_inside = if_else(is.na(hours_inside) == TRUE, 24 - hours_outside, hours_inside), 
       hours_outside = if_else(is.na(hours_outside) == TRUE, 24 - hours_inside, hours_outside)#, 
  ) #Some versions had only hours inside and the endline had only hours outside so setting them all to have both with inside + outside == 24

#Endline 
endline_location_clean <- 
endline_location_repeat %>% 
  mutate(
       hours_inside = 24 - hours_outside, 
       hours_outside = hours_outside 
  )

table(survey_data$study_arm)

survey_data_interest <- 
  survey_data %>% 
  select(KEY, name_respondent, target_child_name, hh_id, study_arm, timepoint, starttime)
#from overall survey data find columns needed to specify hh members at midline  
```

## Join data 
```{r}
joined_data <- 
  midline_location_clean %>%
  right_join(survey_data_interest, (.by = c("PARENT_KEY"= "KEY")))

joined_data_end <- 
  endline_location_clean %>%
  right_join(survey_data_interest, (.by = c("PARENT_KEY"= "KEY")))

survey_data_interest %>% 
  count(timepoint)


joined_data %>% 
  count(timepoint, hours_outside)
#join survey responses with individual level data 
```


### baseline results 
At baseline we asked about the respondent and target child time outside only 

###respondent time outside
```{r}
respondent_baseline <- 
survey_data %>% 
  group_by(timepoint) %>% 
  summarise(mean_hr_outside_hh = mean(hours_outside), sd_hr_inside = sd(hours_inside)) %>% 
  filter(!is.na(mean_hr_outside_hh)) %>% 
  mutate(individual = "respondent", study_arm = "intervention")
  



```


### respondent mean time outside 
```{r}
respondent_midline <- 
joined_data %>% 
  filter(location_name_roster == name_respondent) %>% 
  group_by(timepoint, study_arm, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside, na.rm = TRUE)) %>% 
  mutate(individual = "respondent")
```


#target child mean time outside
```{r}
target_child_midline <- 
joined_data %>% 
  filter(location_name_roster == target_child_name) %>% 
  group_by(timepoint, study_arm, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside)) %>% 
  ungroup() %>% 
	group_by(timepoint) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside), sd = sd(mean_hr_outside)) %>% 
  mutate(individual = "target child")
```

#other adult time spent outside of hh
```{r}
other_member_midline <- 
joined_data %>% 
  filter(
    location_name_roster != target_child_name, 
    location_name_roster != name_respondent
    ) %>% 
  group_by(timepoint, study_arm, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside)) %>% 
   mutate(individual = "other member")




```
#Endline calculations 
```{r}

respondent_endline <-  
  joined_data_end %>% 
  filter(name == name_respondent) %>% 
  group_by(timepoint, study_arm, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside, na.rm = TRUE)) %>% 
  mutate(individual = "respondent")

target_child_endline <- 
  joined_data_end %>% 
  filter(name == target_child_name) %>% 
  group_by(timepoint, study_arm, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside)) %>% 
  mutate(individual = "target child")
  
  
other_member_endline <- 
joined_data_end %>% 
  filter(
    name != target_child_name, 
    name != name_respondent
    ) %>% 
  group_by(timepoint, study_arm, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside)) %>% 
   mutate(individual = "other member")
  
```



```{r}
data_hours_outside <- 
  bind_rows(
    respondent_baseline,
    respondent_midline,
    target_child_midline, 
    other_member_midline, 
    respondent_endline,
    target_child_endline, 
    other_member_endline
    ) %>% 
  mutate(
    av_time_inside = 24 - mean_hr_outside_hh,
    pct_time_inside = av_time_inside / 24 * 100, 
    study_arm = case_when(
      study_arm == "pre-intervention" ~ "intervention",
      study_arm == "post-intervention" ~ "intervention",
      #study_arm == "intervention" ~ "comparison",   
      study_arm == "comparison rd3" ~ "comparison", 
      study_arm == "post-intervention rd3" ~ "intervention",
      study_arm == "intervention follow-up" ~ "comparison",  
      .default = NA), 
    arm_time = str_glue("{timepoint}_{study_arm}"))

```


# PM2.5 exposures 
instead of doing hh specificn adjusted exposures we multiplied by study mean since not all hh had sensors in them. 
```{r}
#Create hh av pm 2.5 dataset
hh_av_pm2.5 <- 
  pm_data_hour %>% 
	group_by(timepoint, study_arm, hh_id) %>% 
	summarise(
		time_range = max(dateTime_hour) - min(dateTime_hour),
		hh_mean = mean(PM_Estimate),
		hh_sd = sd(PM_Estimate)
	)

#summarize by study arm
arm_mean_pm2.5 <- 
  hh_av_pm2.5 %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(
		sensor_on_time = mean(time_range),
		mean_pm2.5_hh = mean(hh_mean), 
		sd_pm2.5_hh = sd(hh_sd)
	) %>% 
  mutate(
    arm_time = str_glue("{timepoint}_{study_arm}")
  ) %>% 
  select(-timepoint)

outdoor_pm2.5 <- 
  arm_mean_pm2.5 %>% 
  filter(study_arm == "outdoor") %>% 
  transmute(
    timepoint,
    mean_pm2.5_outdoor = mean_pm2.5_hh
    )
```
### create weighted dataset of mean pm2.5 * percent time indoors for each group 
```{r}
combined_hr_outside_pm_weighted <- 
  data_hours_outside %>% 
  left_join(arm_mean_pm2.5, by = "arm_time") %>% 
  mutate(timepoint = timepoint.x, study_arm = study_arm.x) %>% 
  select(-c(timepoint.y, timepoint.x, study_arm.x, study_arm.y)) %>% 
  left_join(outdoor_pm2.5, by = "timepoint") %>% 
  mutate(
    weighted_mean_pm2.5_hh = 
      mean_pm2.5_hh * (pct_time_inside/100) + 
      mean_pm2.5_outdoor * ((100 - pct_time_inside)/100)
    )



combined_hr_outside_pm_weighted %>% 
  select(individual, timepoint, study_arm, pct_time_inside, mean_pm2.5_hh, weighted_mean_pm2.5_hh) %>% 
  #filter(individual == "respondent") %>% 
  write_csv(here::here("table_hapit_slide_endline.csv"))
#%>% 
  # pivot_wider(names_from = timepoint, values_from = c(pct_time_inside, mean_pm2.5_hh, weighted_mean_pm2.5_hh))
```

### Time comparisons between cooking member and other hh Members

Took average between baseline and midline for these 
```{r}
#cooking person average time outside 
respondent_indoor <- 
  combined_hr_outside_pm_weighted %>% 
  filter(individual == "respondent") %>% 
  summarise(mean(pct_time_inside)) %>% 
  pull()

#child u5 time outside hh
child_indoor <- 
combined_hr_outside_pm_weighted %>% 
  filter(individual == "target child") %>% 
  summarise(mean(pct_time_inside)) %>% 
  pull()

#other adult time outside hh
adult_indoor <- 
combined_hr_outside_pm_weighted %>% 
  filter(individual == "other member") %>% 
  summarise(mean(pct_time_inside), sd(pct_time_inside)) %>% 
  pull()

```

#Exposure ratios 

####Mother-Child (< 5) Exposure Ratio
 The scaling factor applied to user-input cook pre- and post-exposures to adjust under five children's exposures. The default value of 0.80 is based on smith 2014
 
Child/ respondent pct indoor ratio
```{r}
child_indoor/respondent_indoor
```

 
#### Cook to Other Adult Exposure Ratio
 The scaling factor applied to user-input cook pre- and post-exposures to adjust non-cook adults. The default value of 0.60 is based on the ratio of the men to women's exposures as described in Smith et al 2014.
 Other / respondent time indoor 
 
```{r}
adult_indoor/respondent_indoor
```

```{r}
survey_data$hh_size_2mo_u5

survey_data %>% 
  group_by(timepoint) %>% 
  summarize(
    mean(hh_size), 
    mean((hh_size_u2mo + hh_size_2mo_u5), na.rm = TRUE))
```

### Total hh targeted is 200,000 
Citation is here 
https://openaid.se/en/activities/SE-0-SE-6-12515A0102-BGD-15190
