---
title: RohingyaFuel_food_analysis
author: Laura Kwong
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
---

To do
1.  house_material


Errors:
# There was MORE beef in the pre-intervention communities? Look for outliers/mistakes
# fuel_ever_receive_lpg = 1 is not true for all the intervention hh and it should be!!
# fuel_30_receive_lpg = 1 (%) is not all true for all the intervention hh!!
# What is the "other fuel"  - need to ask in FGD

# We can use this question and the price of firewood in August / Sep (when the survey was conducted), to estimate the number of bundles of firewood purchased, then get the average weight of 100 bundles to calculate demand
buy_wood_cost 
"In the past 30 days, how much money (taka) did you spend on firewood?"


Considerations:

# buy_wood_cost There are 4 hh above 3000 - check their hh size and if they a for others or cooking to sell or boiling frequently

"Who in your family gathers scraps/leaves/twigs?" - is this question interpreted as who has EVER gathered? Or only, who currently gathers? If so, do we think this is a problem?

Add question: fuel_30_other is 10% of homes - what is this other?


Many hh have drudgery_most_diff == drudgery_second_most_diff == drudgery_easiest! Need to train that this shouldn't happen. 
The drudgery questions were accidentally not required, but still why did many skip them?  
Will probably have to throw this question out. = (

The dates are in three different formats. 



Need to factor everything -- look at DataChallenge notes

Instead of refactoring or labeling everything, why not just have the label equal the choices tab "name"? Or does the name have to be a number. 

I averaged as many MUAC measurements as were taken - is that right?

Need to know what breathing rate and MUAC should be for each age group to know if ther are fewer out of the ordinary. 

How does icddrb do PCR for wealth? Should have some way to see if the hh are different in terms of SES. 




- percent of hh involved in ngo or wage labor

pre-intervention sep expenditure charts for people 
- percentage of people buying wood 
- percentage of those collecting X fuel and being harassed
- 


```{r setup, include=FALSE}
library(tableone)
library(janitor) #tabyl() adorn_...()
library(dplyr)
library(readxl)
library(lubridate)
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggpubr)

knitr::opts_chunk$set(echo = TRUE)

`%notin%` <- Negate(`%in%`)

```



```{r}
# file_in

file_survey_data_base <- here::here("4_data/RohingyaFuel_survey_data_paired.rds")
# file_out_2 <- here::here("4_data/RohingyaFuel_data_hh_member_paired.rds") 

file_survey_data_intervention_baseline <- here::here("4_data/RohingyaFuel_survey_data_intervention_baseline.rds")
file_survey_data_intervention_endline <- here::here("4_data/RohingyaFuel_survey_data_intervention_endline.rds")
file_survey_data_comparison_baseline <- here::here("4_data/RohingyaFuel_comparison_baseline.rds")
file_survey_data_comparison_endline <- here::here("4_data/RohingyaFuel_comparison_endline.rds")
file_survey_data_intervention <- here::here("4_data/RohingyaFuel_intervention.rds")
file_survey_data_comparison <- here::here("4_data/RohingyaFuel_comparison.rds")

file_survey_data_base_wide <- here::here("4_data/RohingyaFuel_survey_data_wide_paired.rds")


# file_out
camp_block_id_path <- here::here("4_data/camp_block_id.csv")
camp_block_sublock_id_path <- here::here("4_data/camp_block_subblock_ids.csv")
camp_block_subblock_id_100_largest_path <- here::here("4_data/camp_block_subblock_ids_100_largest.csv")


file_barplot_firewood_collection_hours <- here::here("6_figures/barplot_firewood_collection_hours.tiff")
file_barplot_firewood_collection_frequency <- here::here("6_figures/barplot_firewood_collection_frequency.tiff")
file_barplot_sexual_harassment <- here::here("6_figures/barplot_sexual_harassment.tiff")


file_out_CES_D_data <- here::here("4_data/CES_D_data.rds")
file_out_anxiety_data  <- here::here("4_data/anxiety.rds")
file_out_FCS_HDDS_data <- here::here("4_data/FCS_HDDS_data.rds")
file_out_harassment_analysis <- here::here("4_data/harassment_analysis.rds")
file_out_harassment_freq_prev <- here::here ("4_data/harassment_freq_prev.rds")
```


```{r load_data, include=FALSE} 
survey_data <- read_rds(file_survey_data_base)

survey_data_intervention_baseline <- read_rds(file_survey_data_intervention_baseline)
survey_data_intervention_endline <- read_rds(file_survey_data_intervention_endline)
survey_data_control_baseline <- read_rds(file_survey_data_comparison_baseline)
survey_data_control_endline <- read_rds(file_survey_data_comparison_endline)
survey_data_intervention <- read_rds(file_survey_data_intervention)
survey_data_control <- read_rds(file_survey_data_comparison)
survey_data_base_wide <- read_rds(file_survey_data_base_wide)
```





DiD estimator
```{r}
# survey_data$total_income_30 %>%View()
library(estimatr)
lm_did_income <- lm_robust(data = survey_data, formula = income ~ timepoint_num + study_arm_overall_num + did, clusters = fcn_id)
summary(lm_did_income)

lm_did_wage <- lm_robust(data = survey_data, formula = income_wage_labor ~ timepoint_num + study_arm_overall_num + did, clusters = fcn_id)
summary(lm_did_wage)

lm_did_NGO <- lm_robust(data = survey_data, formula = income_cash_ngo ~ timepoint_num + study_arm_overall_num + did, clusters = fcn_id)
summary(lm_did_NGO)

lm_did_expenditures <- lm_robust(data = survey_data, formula = spent_total_month_with_6mo_monthly ~ timepoint_num + study_arm_overall_num + did, clusters = fcn_id)
summary(lm_did_expenditures)

lm_did_food <- lm_robust(data = survey_data, formula = spent_food ~ timepoint_num + study_arm_overall_num + did, clusters = fcn_id)
summary(lm_did_food)

lm_did_tobacco_pan <- lm_robust(data = survey_data, formula = spent_tobacco_pan ~ timepoint_num + study_arm_overall_num + did, clusters = fcn_id)
summary(lm_did_tobacco_pan)

lm_did_wood <- lm_robust(data = survey_data, formula = buy_wood_cost ~ timepoint_num + study_arm_overall_num + did, clusters = fcn_id)
summary(lm_did_wood)
```














