---
title: RohingyaFuel_food_analysis
author: Laura Kwong
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
---

To do
1.  house_material


Errors:
# There was MORE beef in the pre-intervention communities? Look for outliers/mistakes
# fuel_ever_receive_lpg = 1 is not true for all the intervention hh and it should be!!
# fuel_30_receive_lpg = 1 (%) is not all true for all the intervention hh!!
# What is the "other fuel"  - need to ask in FGD

# We can use this question and the price of firewood in August / Sep (when the survey was conducted), to estimate the number of bundles of firewood purchased, then get the average weight of 100 bundles to calculate demand
buy_wood_cost 
"In the past 30 days, how much money (taka) did you spend on firewood?"


Considerations:

# buy_wood_cost There are 4 hh above 3000 - check their hh size and if they a for others or cooking to sell or boiling frequently

"Who in your family gathers scraps/leaves/twigs?" - is this question interpreted as who has EVER gathered? Or only, who currently gathers? If so, do we think this is a problem?

Add question: fuel_30_other is 10% of homes - what is this other?

Almost 150 of 393 hh report burning plastic every day!  We need to better understand how many meals and if they are relying on plastic for all of the fuel they need or if it is used in combination with other fuel sources --> ask about how often they burned plastic

1. fuel_ever_plastic 
0. How often per week do you burn plastic? --> Need a recall period?
2. When you burned plastic, was the only fuel you used plastic or did you combine plastic with other fuels?
3. Why did you burn plastic
Select_multiple
a. We can't access other fuels
b. If we burn plastic, we don't have to spend money buying other fuels 
c. Burning plastic is a good way to get rid of trash
d. Other
Specify other

Add questions about burning plastic to the focus group discussions - doesn't quite fit with any of the FGDs, but add to distribution and training. 

Many hh have drudgery_most_diff == drudgery_second_most_diff == drudgery_easiest! Need to train that this shouldn't happen. 
The drudgery questions were accidentally not required, but still why did many skip them?  
Will probably have to throw this question out. = (

The dates are in three different formats. 



Need to factor everything -- look at DataChallenge notes

Instead of refactoring or labeling everything, why not just have the label equal the choices tab "name"? Or does the name have to be a number. 

I averaged as many MUAC measurements as were taken - is that right?

Need to know what breathing rate and MUAC should be for each age group to know if ther are fewer out of the ordinary. 

How does icddrb do PCR for wealth? Should have some way to see if the hh are different in terms of SES. 



This script is to analyze the Rohingya LPG Assessment household survey data



- percent of hh involved in ngo or wage labor

pre-intervention sep expenditure charts for people 
- percentage of people buying wood 
- percentage of those collecting X fuel and being harassed
- 
- send Mickael my requests for cost info
- add Peter, Rajib, Ritu, Geophrey to IRB


```{r setup, include=FALSE}
library(tableone)
library(janitor) #tabyl() adorn_...()
library(dplyr)
library(readxl)
library(lubridate)
library(tidyverse)
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(echo = TRUE)

`%notin%` <- Negate(`%in%`)
```


```{r}
# source(here::here("file_paths.Rmd"))

file_survey_data_base <- here::here("data", "RohingyaFuelMaster_tidy_host.rds")


file_barplot_firewood_collection_hours <- here::here("docs", "barplot_firewood_collection_hours_host.png")
file_barplot_firewood_collection_frequency <- here::here("docs", "barplot_firewood_collection_frequency_host.png")
file_barplot_sexual_harassment <- here::here("docs", "barplot_sexual_harassment_host.png")

```

```{r load_data, include=FALSE} 
survey_data <- read_rds(file_survey_data_base)
```


```{r vars}
asset_vars <- 
	c(
		"mattress", "blanket", "mosquito_net", "solar_lamp", "portable_lamp",
		"umbrella", "table", "chair_bench", "almirah_wardrobe_show_case", 
		"electric_fan", "refrigerator",
		"shovel", "sickle", "weaving_tool", "fish_net",
		"mobile_phone", "smartphone", "radio", 
		"television", "DVD_VCD_player", "computer_laptop", 
		"bicycle", "motorcycle", "rickshaw_van", "CNG_tempo_electric_bike",
		"chicken_duck_pigeon", "goat_sheep", "cow_buffalo"
	)

spent_monthly_vars <- 
	c(
		"spent_food",
		"buy_wood_cost", # "In the past 30 days, how much money (taka) did you spend on firewood?"
		"spent_hh_items",
		"spent_hygiene",
		"spent_tobacco_pan",
		"spent_transport",
		"spent_phone",
		"spent_clothing_month", 
		"spent_shelter_month",
		"spent_celebrations_month",
		"spent_debt_month",
		"spent_medical_month",
		"spent_education_month",
		"spent_other_month"
	)
# 		"spent_total_month",

nonrespiratory_vars <- 
	c(
		"target_child_eye_red", "target_child_eye_itch",  
		"respondent_eye_red", "respondent_eye_itch", "respondent_eye_sore",
		"respondent_headache", "respondent_backache"
	)

nonrespiratory_vars_yn <-  
	map_chr(nonrespiratory_vars, ~ paste0(., "_yn"))

respiratory_vars <- 
	c(
		"target_child_cough", "target_child_resp_rate", 
		"target_child_clinic_resp", "target_child_wheezing", 
		"target_child_disturbed_sleep", "target_child_distrubed_speech", 
		"respondent_cough", "respondent_resp_rate", 
		"respondent_weight_loss", "respondent_wheezing", 
		"respondent_disturbed_sleep", "respondent_disturbed_speech"
	)

respiratory_vars_yn <-  
	map_chr(respiratory_vars, ~ paste0(., "_yn"))

generalhealth_vars <-  
	c(
		"target_child_fever", "target_child_weight_loss", "target_child_lethargy"
	)

generalhealth_vars_yn <-  
	map_chr(generalhealth_vars, ~ paste0(., "_yn"))

MUAC_vars <- 
	c(
		"target_child_arm_measurements_yn", "target_child_mid_arm_circ_av"
	)

breathing_vars <- 
	c(
		"target_child_breathing_yn", "target_child_resp_rate_measured"
	)

mental_health_good_vars <- c("happy", "enjoyed_life", "self_worth", "hopeful")

mental_health_bad_vars <- 
	c(
		"bothered", "sick", 
		"no_appetite", "diff_concentrating", "restless_sleep",
		"exert_effort", "less_talkative", 
		"feeling_disliked", "unfriendly_people",
		"fearful", "lonely", "crying_spells",
		"cant_get_going", "feeling_down", "life_failure", "depressed" 
	)

mental_health_vars <-
	c(mental_health_good_vars, mental_health_bad_vars, "suicidal_thoughts_30")


mental_health_good_twodays_vars <-  
	map_chr(mental_health_good_vars, ~ paste0(., "_twodays"))

mental_health_bad_twodays_vars <-  
	map_chr(mental_health_bad_vars, ~ paste0(., "_twodays"))

mental_health_twodays_vars <-
	c(mental_health_good_twodays_vars, mental_health_bad_twodays_vars, "suicidal_thoughts_30")


# food soure
# This question was select_multiple. For each category there is a column with a y/n response for that food/source category
food_source <- 
	c(
		"rice_source", "bread_source", "corn_source", 
		"potatoes_source", "lentils_source", "eggs_source", 
		"dairy_source", "veggies_source", "fruit_source", 
		"fish_source", "poultry_source", "goat_sheep_source",
		"beef_source", "oil_source", "sugar_source" 
	)

food_source_sources = 
	c(
		"Don't eat",
		"Food aid",
		"Purchased",
		"Purchased", #"Purchased with wages",
		"Gift",
		"Borrowed",
		"Own production",
		"Exchanged labor",
		"Exchanged items",
		"Gathered",
		"Other"
	)

food_source_all <- c()
for (food in food_source){
	for (i in c(1:9, 66)){
		food_source_all <- c(food_source_all, paste(food, i, sep = ""))
	}
}


# food_cant_afford
food_cant_afford <-
	c(
		"food_cant_afford_action",
		"food_cant_afford_difficult",
		"food_cant_afford_easiest"
	)

# fuel_cant_afford
fuel_cant_afford <-
	c(
		"food_cant_afford_action"
	)

food_cant_afford_reasons = 
	c(
		"Borrowed food",
		"Reduce food per meal",
		"Reduce meals per day",
		"Skip meals",
		"Restrict adult food",
		"Sold goods",
		"Purchased on credit",
		"Borrowed money",
		"Reduced expenditures",
		"Spent savings",
		"Worked for money for food",
		"Sold or consumed livestock",
		"Exchanged food",
		"Other",
		"Did not need to manage"
	)

fuel_cant_afford_reason = 
	c(
		"Borrowed fuel", # Response was "borrow food", which is also possible, but I'm going to interpret as "borrow fuel"
		"Reduce food per meal",
		"Reduce meals per day",
		"Skip meals",
		"Restrict adult food",
		"Sold goods",
		"Purchased on credit",
		"Borrowed money",
		"Reduced expenditures",
		"Spent savings",
		"Worked for money for fuel",
		"Sold livestock to purchase fuel",
		"Sold food to purchase fuel",
		"Eat food that doesn't need to be cooked",
		"Eat food that wasn't fully cooked",
		"Other",
		"Did not need to manage"
	)

# This question was select_multiple. For each category there is a column with a y/n response for that response category
food_cant_afford_all <- c()
for (type in food_cant_afford){
	for (i in c(1:13, 66, 88)){ # 
		food_cant_afford_all <- c(food_cant_afford_all, paste(type, i, sep = ""))
	}
}

# This question was select_multiple. For each category there is a column with a y/n response for that response category
fuel_cant_afford_all <- c()
for (type in fuel_cant_afford){
	for (i in c(1:15, 66, 88)){ #
		fuel_cant_afford_all <- c(fuel_cant_afford_all, paste(type, i, sep = ""))
	}
}

# mutate_at(
# 		vars(food_cant_afford_action),
# 		funs(factor),
# 			levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 66, 88),
# 		labels = c(
# 			"Borrowed food",
# 			"Reduce food per meal",
# 			"Reduce meals per day",
# 			"Skip meals",
# 			"Restrict adult food",
# 			"Sold goods",
# 			"Purchased on credit",
# 			"Borrowed money",
# 			"Reduced expenditures",
# 			"Spent savings",
# 			"Worked for money for food",
# 			"Sold or consumed livestock",
# 			"Exchanged food",
# 			"Other",
# 			"Did not need to manage"
# 		)
# 	)
# 	
# 	mutate_at(
# 		vars(fuel_cant_afford_action),
# 		funs(factor),
# 		levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 66, 88),
# 		labels = c(
# 			"Borrowed fuel", # Response was "borrow food", which is also possible, but I'm going to interpret as "borrow fuel"
# 			"Reduce food per meal",
# 			"Reduce meals per day",
# 			"Skip meals",
# 			"Restrict adult food",
# 			"Sold goods",
# 			"Purchased on credit",
# 			"Borrowed money",
# 			"Reduced expenditures",
# 			"Spent savings",
# 			"Worked for money for fuel",
# 			"Sold livestock to purchase fuel",
# 			"Sold food to purchase fuel",
# 			"Eat food that doesn't need to be cooked",
# 			"Eat food that wasn't fully cooked",
# 			"Other",
# 			"Did not need to manage"
# 		)
# 	) 


fuel_use_non_lpg_type <-
	c(
		"fuel_use_non_lpg_type_buy_lpg",
		"fuel_use_non_lpg_type_buy_wood",
		"fuel_use_non_lpg_type_collect_wood",
		"fuel_use_non_lpg_type_other"
	)

credit <-
	c(
		"credit_access",
		"credit_relatives",
		"credit_charities", 
		"credit_village_head", 
		"credit_lender", 
		"credit_bank",
		"credit_cooperative"
	)

# Ugh! We could have done a much better job of naming the variables so they would be easy to separate


# for fuel_collection_who, the denominator is hh that EVER collected type X fuel
fuel_collection_who <- c()
for (fuel in c("gather_scraps", "collect_wood", "receive_wood", "buy_wood", "receive_lpg", "buy_lpg", "receive_crh", "buy_crh")){
	for (person in c("w", "g", "m", "b")){
		fuel_collection_who <- c(fuel_collection_who, paste(fuel, person, sep = "_"))
	}
}

# for any_harassment_hh, the denominator is ALL households
any_harassment_hh <- # did anyone in the hh experience this type of harassment FOR ANY REASON? Y/N
	c(
		"insult_hh", "belittle_hh", "scare_hh", "push_hh", 
		"hit_hh", "kick_hh", "choke_hh", "weapon_hh", 
		"sex_lang_hh", "sex_contact_hh", "sex_rumor_hh", 
		"clothing_pull_hh", "sex_corner_hh"
	)

# for fuel_harassment_hh, the denominator is households that said they EvER collected type X fuel 
fuel_harassment_hh <- # did anyone in the hh experience this type of harassment related to fuel collection? Y/N
	survey_data %>% 
	select(
		ends_with("insult_hh"), ends_with("belittle_hh"), ends_with("scare_hh"), ends_with("push_hh"), 
		ends_with("hit_hh"), ends_with("kick_hh"), ends_with("choke_hh"), ends_with("weapon_hh"), 
		ends_with("sex_lang_hh"), ends_with("sex_contact_hh"), ends_with("sex_rumor_hh"), 
		ends_with("clothing_pull_hh"), ends_with("sex_corner_hh")
	) %>%
	select(
		-any_harassment_hh
	) %>%
	names()

# What was the frequency of harassment by the specific people? (Categorical number of times per week)
# Determine prev with harassment_vars_yn
# Need to make the gender-specific denominator the fuel_collection_who - fuel-and gender-specifc 
harassment_vars <- 
	survey_data %>%
	select( 
		starts_with("gather_scraps"), 
		starts_with("collect_wood"), 
		starts_with("receive_wood"), 
		starts_with("buy_wood"), 
		starts_with("receive_lpg"), 
		starts_with("buy_lpg"), 
		starts_with("receive_crh"), 
		starts_with("buy_crh")
	) %>%
	select(
		-c(
			fuel_collection_who, # remove the vars that only indicate of that type of person collects the type of fuel
			# any_harassment_hh, # These weren't selected by the section criteria
			fuel_harassment_hh, # remove the vars that are the hh level of harassment 
			gather_scraps_dead,
			collect_wood_times_week, collect_wood_walk_hr, collect_wood_forest_start, collect_wood_forest_stop,
			receive_wood_wait,
			buy_wood_cost, buy_wood_reason, buy_wood_when_start,
			receive_lpg_walk, receive_lpg_wait,
			buy_lpg_cost, buy_lpg_walk, buy_lpg_wait,
			receive_crh_walk, receive_crh_wait
		)
	) %>%
	names()
```

Responses for health questions are all categorical

vars(
mental_health_vars,
borrow_food, reduce_food, 
reduce_meals_lack_food, not_eat_lack_food, restrict_food, 
borrow_fuel, reduce_fuel, reduce_meals_lack_fuel, not_eat_lack_fuel,
burn_plastic_frequency
)
choices: [weekly_choices]
0	Never
1	One or two days
2	Three to four days
3	Five to six days
4	Every day

vars(nonrespiratory_vars)
choices: [illness_freq]
0	Never
1	A few  days (1-5 days) 
2	Most days (5-12 days) 
3	Almost every day (13-14 days) 

vars(generalhealth_vars, respiratory_vars)
choices: [yes_no_dk]	
0	No
1	Yes
77	Refused
99	Don't know

vars(
UNHCR_card, 
food_cant_afford_2wk, fuel_cant_afford_2wk,
window_door_wall, stove_reason_sell_food,  
harassment_continue
)
choices: [yes_no]	
0	No
1	Yes
77	Refused



vars(
stove_reason_cook_together, 
stove_boil_drink, stove_boil_bathe, 
stove_reason_stay_warm,
soak_rice, soak_lentils, cover_pot, fuel_use_non_lpg_ever, lpg_prior_use, 
stove_used, stove_training,
lpg_safety_visit, lpg_gas_leak, 
gather_wood, forest_collect_not_wood

)
choices: [yes_no_only]	
0	No
1	Yes


vars(
starts_with("time")
)
choices: [more_less]
[more_less]	1	more 
[more_less]	2	same
[more_less]	3	less

vars(food_source)
*This question was select_multiple. For each category there is a column with a y/n response for that food/source category*
choices: [food_source]
0	Don't eat / don't have
1	Ration card / food aid
2	Purchased
3	Purchased with wages
4	Gift from relative or friend
5	Borrow from relative or friend
6	Own production (own garden or animals)
7	Exchange labour for food
8	Exchange items for food
9	Gather, hunt, fish
66 Other

vars(food_cant_afford)
*This question was select_multiple. For each category there is a column with a y/n response for that response category*
choices: [food_cant_afford]
1	Borrow food of rely on help from a relative or friend
2	Reduce the amount of food eaten per meal
3	Reduce the amount of meals eaten per day
4	Not eat any food (skipped all meals) on some days
5	Restrict the amount of food consumed by adults so there was more for children <5 years old?
6	Sold household goods
7	Purchased food on credit
8	Borrowed money
9	Reduced expenditures on health and education
10	Spent savings
11	Worked specificially to earn money to buy food
12	Sold or consumed livestock
13	Exchanged food for other type of food
66	Other
88	NA/Nothing is difficult

vars(fuel_cant_afford)
*This question was select_multiple. For each category there is a column with a y/n response for that response category*
choices: [fuel_cant_afford]
1	Borrow food of rely on help from a relative or friend
2	Reduce the amount of food eaten per meal
3	Reduce the amount of meals eaten per day
4	Not eat any food (skipped all meals) on some days
5	Restrict the amount of food consumed by adults so there was more for children <5 years old?
6	Sold household goods
7	Purchased fuel on credit
8	Borrowed money
9	Reduced expenditures on health and education
10	Spent savings
11	Worked specificially to earn money to buy fuel
12	Sold livestock
13	Sold food to purchase fuel for cooking
14	Rely on food that doesn't need to be cooked
15	Ate food that wasn’t fully cooked
66	Other
88	NA/Nothing is difficult

vars(credit, fuel_use_non_lpg_type)
choices: [yes_no_dk]	
0	No
1	Yes
99	Don't know

vars(harassment_vars)
choices: [frequency_times]
0	Never
1	Once
2	Twice
3	Three times
4	More than three times




# Access to phones
We didn't collect phone numbers (phone are not allowed so we )
```{r}
survey_data %>% select(hh_id, mobile_phone_yn) %>% summarise(phone.pc = mean(mobile_phone_yn)) 
# 49.2% of our sample has mobile phones; we should've collected their phone numbers! but we didn't, so couldn't do an endline survey by phone. 
```

# Where are the hh located?
```{r}
camp_block_id <-
	survey_data %>%
	# tabyl(camp_id)
	# tabyl(camp_id, lpg_depots) # lpg_depots = "What LPG distribution center do you go to?
	tabyl(camp_id, block_id)
# unite(block_sub_block_id, c("block_id", "subblock_id")) %>%
# tabyl(camp_id, block_sub_block_id)
write.csv(camp_block_id, camp_block_id_path)

camp_block_subblock_id <-
	survey_data %>%
	group_by(camp_id, block_id, subblock_id) %>% 
	count() %>%
	ungroup() %>%
	arrange(camp_id, block_id, subblock_id) 
# tabyl(camp_id)
# tabyl(camp_id, lpg_depots) # lpg_depots = "What LPG distribution center do you go to?
# tabyl(camp_id, block_id)

write.csv(camp_block_subblock_id, camp_block_sublock_id_path)

# For the Rohingya COVID-19 proposal, we need the 100 sub-blocks with the most hh interviewed
camp_block_subblock_id_100_largest <-
	camp_block_subblock_id %>%
	arrange(desc(n)) %>%
	slice(1:100) %>%
	arrange(camp_id, block_id, subblock_id)

write.csv(camp_block_subblock_id_100_largest, camp_block_subblock_id_100_largest_path)

```

There are 38 hh in camp 4 that do not have a block_id

camp_id 10 has one hh in block E - should be F?
camp_id 9 has 2 hh in block C - correct? and 3 hh in block F - correct?

Is the LPG depot written on their refill card? We should look at the card and record ourselves
Why are there such strange lpg depot designations? - someone from 8W goes to depot 25 but no one else is receiving LPG? 

# Respiratory data
```{r}
respiratory_vars_data <-
	survey_data %>%
	select(
		hh_id, camp_id, block_id, subblock_id,
		respiratory_vars, generalhealth_vars
	)

saveRDS(respiratory_vars_data, "respiratory_vars_data.rds")
```



# Who is collecting wood
```{r}
survey_data %>%
	tabyl(fuel_ever_collect_wood)

survey_data %>%
	tabyl(study_arm, fuel_30_buy_wood)

survey_data %>%
	tabyl(fuel_30_collect_wood, fuel_30_buy_wood, study_arm)

survey_data %>%
	tabyl(fuel_30_gather_scraps, fuel_30_buy_wood, study_arm)
```
81% (n = 968 / (597 + 599)) of all hh in the baseline sample report ever collecting wood. 

360 hh in the pre-intervention arm report collecting wood in the past 30 days while none of the hh in the intervention arm report collecting firewood. 

In the pre-intervention arm, 155 do not collect and do not purchase; 326 do not collect but do prchase wood; 82 collect and don't purchase; 34 collect and purchas





Make this into a function then use map_dfr to apply it to all of the column of interest

survey_data %>%
ggplot(aes(x = income)) +
geom_histogram(binwidth = 500) + 
geom_vline(aes(xintercept = mean(income, na.rm = TRUE), col = 'red'), size = 2, show.legend = TRUE) + 
geom_vline(aes(xintercept = median(income, na.rm = TRUE), col = 'blue'), size = 2, show.legend = TRUE) +
scale_colour_manual("Legend", values = c(red = "red", blue = "blue"), labels = c("mean", "median"))


```{r}
# names(survey_data %>% select(ends_with("_hh")))
# str(survey_data)
```

# Descriptive statistics
[47] "hh_size"                             "hh_size_u2mo"                       
[49] "hh_size_2mo_u5"                      "hh_size_5_18"                       
[51] "hh_size_o18"                         "hh_size_o40"

Use the very convenient R package tableone! 
https://cran.r-project.org/web/packages/tableone/vignettes/introduction.html

```{r Table1}

## Vector of variables to summarize
table1Vars <- 
	c(
		"target_child_sex", 
		"target_child_months", 
		"hh_size", "hh_size_2mo_u5", "hh_size_u2mo", 
		"hh_ppl_smoke",
		"electricity",
		"mattress_yn", "blanket_yn", "mosquito_net_yn", 
		"solar_lamp_yn", "portable_lamp_yn",
		"umbrella_yn", 
		"chair_bench_yn", "table_yn",
		"electric_fan_yn", 
		"shovel_yn", "sickle_yn", "weaving_tool_yn", 
		"mobile_phone_yn", "smartphone_yn", "radio_yn", 
		"chicken_duck_pigeon_yn", 
		"income", 
		"income_home_garden",
		"income_cash_ngo", "income_own_business", "income_wage_labor", 
		"income_skill_labor", "income_selling_wood", "income_abroad", 
		"income_humanitarian_asst", "income_handicrafts_tailoring", "income_farming",
		"spent_total_month",
		"spent_clothing_month",
		"spent_shelter_month",
		"spent_celebrations_month",
		"spent_debt_month",
		"spent_medical_month",
		"spent_education_month",
		"spent_other_month"
	)

## Vector of categorical variables that need transformation
table1FactorVars <- 
	c(
		"target_child_sex", "electricity", 	
		"blanket_yn", "mattress_yn", "mosquito_net_yn", 
		"solar_lamp_yn", "portable_lamp_yn",
		"umbrella_yn", 
		"chair_bench_yn", "table_yn", "almirah_wardrobe_show_case_yn", 
		"electric_fan_yn", 
		"shovel_yn", "sickle_yn", "weaving_tool_yn",
		"mobile_phone_yn", "smartphone_yn", "radio_yn",	
		"chicken_duck_pigeon_yn",
		"income_home_garden"
	)

## Create a TableOne object
tab1 <- CreateTableOne(data = survey_data, vars = table1Vars, factorVars = table1FactorVars, strata = "study_arm")

tab1
# survey_data %>%
#   tabyl(target_child_sex, study_arm) %>%
#   # adorn_totals(c("row", "col")) %>%
#   adorn_percentages("row") %>% 
#   adorn_pct_formatting(rounding = "half up", digits = 0) %>%
#   adorn_ns() %>%
#   adorn_title("combined") %>%
#   knitr::kable()

```

```{r}
fig_monthly_income <- 
	survey_data %>%
	select(study_arm, hh_id, starts_with("income")) %>%
	gather(-study_arm, -hh_id, key = "income_source", value = "income") %>%
	mutate(
		income_source = 
			ordered(
				income_source,
				levels = c(
					"income",
					"income_cash_ngo", "income_wage_labor",
					"income_skill_labor", "income_own_business", "income_abroad",
					"income_handicrafts_tailoring", "income_farming", 
					"income_humanitarian_asst", "income_selling_wood",  
					"income_home_garden"
				),
				labels = 
					c(
						"total income",
						"NGO", "wage labor",
						"skilled labor", "own business", 
						"remittences", "tailoring \nhandicrafts", "farming",
						"selling aid", "selling wood",
						"home_garden"
					)
			)
	) %>%
	filter(income_source != "home_garden") %>%
	ggplot(aes(x = income_source, y = income, fill = study_arm)) +
	geom_col(position = "dodge") +
	ggpubr::stat_compare_means(
		label = "p.signif", #"p.signif" # symnum.args <- list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), symbols = c("****", "***", "**", "*", "ns"))
		method = "t.test",
		
		# label.y = 18,
		hide.ns = TRUE#,
		# ref.group = ".all."
		# show.legend = TRUE # doesn't show the legend of stas?
	) +
	viridis::scale_fill_viridis(
		discrete = TRUE,
		end = 2/3
	) +
	theme_classic() +
	theme(
		axis.text.x = element_text(angle = 45, hjust = 1)
	) + 
	labs(
		title = "Monthly income",
		x = "Income source",
		y = "Monthly income (BDT)"
	)

fig_monthly_income

ggsave(
	here::here("docs", "fig_monthly_income.png"),
	plot = last_plot(),
	scale = 0.7,
	height = 6,
	width = 10,
	units = "in",
	device = "png"
)

```


```{r}
survey_data %>%
	group_by(study_arm) %>%
	summarise_at(
		vars(income_wage_labor, income_cash_ngo, income_own_business, income), 
		list(mean = mean, sd = sd, median = median), na.rm = TRUE
	)

survey_data %>%
	select(camp_id, study_arm, income) %>%
	arrange(desc(income))
```




MAUC_vars: continuous numeric
breathing vars: continuous numeric
hh_ppl_smoke: continuous numeric

Associate health variables with % of time using biomass AND whether or not ppl in hh smoke

hh_ppl_smoke

```{r health_tab2}
# "target_child_arm_measurements_yn" and "target_child_breathing_yn" 
# don't need to be in the table but the show refusal rates equal across groups

## Vector of variables to summarize
table2Vars <- 
	c(
		nonrespiratory_vars, 
		respiratory_vars, 
		generalhealth_vars, 
		MUAC_vars, 
		breathing_vars
	)

## Vector of categorical variables that need transformation
table2FactorVars <- 
	c(
		nonrespiratory_vars, 
		respiratory_vars, 
		generalhealth_vars
	)

## Create a TableOne object
tab2 <- 
	CreateTableOne(
		data = survey_data, 
		vars = table2Vars, 
		factorVars = table2FactorVars, 
		strata = "study_arm"
	)

tab2

```


```{r health_yn_tab2_yn}
# "target_child_arm_measurements_yn" and "target_child_breathing_yn" 
# don't need to be in the table but the show refusal rates equal across groups

## Vector of variables to summarize
table2_yn_Vars <- 
	c(
		nonrespiratory_vars_yn, 
		respiratory_vars_yn, 
		generalhealth_vars_yn, 
		MUAC_vars, 
		breathing_vars
	)

## Vector of categorical variables that need transformation
table2_yn_FactorVars <- 
	c(
		nonrespiratory_vars_yn, 
		respiratory_vars_yn, 
		generalhealth_vars_yn
	)

## Create a TableOne object
tab2_yn <- 
	CreateTableOne(
		data = survey_data, 
		vars = table2_yn_Vars, 
		factorVars = table2_yn_FactorVars, 
		strata = "study_arm"
	)

tab2_yn

```


## Objective_health: were there fewer respiratory rates that were out of the ordinary? Were there fewer MUAC that were low? 

Need table of categories
```{r objective_health}
survey_data %>%
	group_by(study_arm) %>%
	summarise_at(
		vars(
			hours_inside, #hours_outside, 
			target_child_hours_inside # target_child_hours_outside, 
		), 
		list(mean), 
		na.rm = TRUE
	) 

## Vector of variables to summarize
table3Vars <- c("hours_inside", "target_child_hours_inside")

# ## Vector of categorical variables that need transformation
# table3FactorVars <- c()

## Create a TableOne object
# tab3 <- CreateTableOne(data = survey_data, vars = table3Vars, factorVars = table3FactorVars, strata = "study_arm")
tab3 <- CreateTableOne(data = survey_data, vars = table3Vars, strata = "study_arm")


tab3
```




```{r mental_health_tab4}
## Vector of variables to summarize
table4_good_Vars <- mental_health_good_vars

# ## Vector of categorical variables that need transformation
table4_good_FactorVars <- mental_health_good_vars

## Create a TableOne object
tab4_good <- 
	CreateTableOne(
		data = survey_data, 
		vars = table4_good_Vars, 
		factorVars = table4_good_FactorVars, 
		strata = "study_arm"
	)



## Vector of variables to summarize
table4_bad_Vars <- c(mental_health_bad_vars, "suicidal_thoughts_30")

# ## Vector of categorical variables that need transformation
table4_bad_FactorVars <- c(mental_health_bad_vars, "suicidal_thoughts_30")

## Create a TableOne object
tab4_bad <- 
	CreateTableOne(
		data = survey_data, 
		vars = table4_bad_Vars, 
		factorVars = table4_bad_FactorVars, 
		strata = "study_arm"
	)


# Group by <= 2 days or >=3 days to account for accuracy of response

## Vector of variables to summarize
table4_good_twodays_Vars <- mental_health_good_twodays_vars

# ## Vector of categorical variables that need transformation
table4_good_twodays_FactorVars <- mental_health_good_twodays_vars

## Create a TableOne object
tab4_good_twodays <- 
	CreateTableOne(
		data = survey_data, 
		vars = table4_good_twodays_Vars, 
		factorVars = table4_good_twodays_FactorVars, 
		strata = "study_arm"
	)


## Vector of variables to summarize
table4_bad_twodays_Vars <- c(mental_health_bad_twodays_vars, "suicidal_thoughts_30_yn")

# ## Vector of categorical variables that need transformation
table4_bad_twodays_FactorVars <- c(mental_health_bad_twodays_vars, "suicidal_thoughts_30_yn")

## Create a TableOne object
tab4_bad_twodays <- 
	CreateTableOne(
		data = survey_data, 
		vars = table4_bad_twodays_Vars, 
		factorVars = table4_bad_twodays_FactorVars, 
		strata = "study_arm"
	)

tab4_good
tab4_bad

tab4_good_twodays
tab4_bad_twodays
```

## Suicidal thoughts
```{r}
survey_data %>%
	tabyl(suicidal_thoughts_30_yn) 

survey_data %>%
	# filter(suicidal_thoughts_30_yn == 1) %>%
	tabyl(camp_id, suicidal_thoughts_30_yn) %>%
	# adorn_totals(c("row", "col")) %>%
	adorn_percentages("row") %>%
	adorn_pct_formatting(rounding = "half up", digits = 0) %>%
	adorn_ns() %>%
	adorn_title("combined") %>%
	knitr::kable()


hh_negative_thoughts_to_visit <-
	survey_data %>%
	filter(suicidal_thoughts_30_yn == 1) %>%
	select(hh_id, camp_id, subblock_id, name_respondent) 

# write.csv(hh_negative_thoughts_to_visit, "")
```


# Income
```{r income}
## Vector of variables to summarize
# Use Hmisc::Cs to quote each variable
table5Vars <- 
	Hmisc::Cs(
		income_cash_ngo, income_own_business, income_wage_labor, income_skill_labor, income_selling_wood, income_abroad, income_humanitarian_asst, income_handicrafts_tailoring, income_farming
	)

# ## Vector of categorical variables that need transformation
# table5FactorVars <- table5Vars

## Create a TableOne object
# tab5 <- CreateTableOne(data = survey_data, vars = table5Vars, factorVars = table5FactorVars, strata = "study_arm")
tab5 <- CreateTableOne(data = survey_data, vars = table5Vars, strata = "study_arm")

tab5

# Visualize
survey_data %>%
	ggplot(aes(x = income)) +
	geom_histogram(binwidth = 500) + 
	geom_vline(aes(xintercept = mean(income, na.rm = TRUE), col = 'red'), size = 2, show.legend = TRUE) + 
	geom_vline(aes(xintercept = median(income, na.rm = TRUE), col = 'blue'), size = 2, show.legend = TRUE) +
	scale_colour_manual("Legend", values = c(red = "red", blue = "blue"), labels = c("mean", "median"))

survey_data %>%
	summarise_at(vars(income, spent_total_month, debt), list(mean = mean, median = median), na.rm = TRUE)

survey_data %>%
	summarise_at(
		vars(
			income_cash_ngo, income_own_business, income_wage_labor, income_skill_labor, income_selling_wood, income_abroad, income_humanitarian_asst, income_handicrafts_tailoring, income_farming
		),
		list(mean), 
		na.rm = TRUE
	) %>%
	gather(key = "var")

# Percentage of hh making any money from selling wood
survey_data %>%
	count(income_selling_wood != 0)
# Only 3 hh are making money selling wood

# Of those selling wood, the income from selling wood as a percent of total income
# Moot since this is only 3 percent of hh

# Electricity
survey_data %>%
	select(electricity) %>%
	table()

# Garden
survey_data %>%
	select(income_home_garden) %>%
	table()
```


# PCA to determine weath quintiles

How do I consider that these assets have differnt value?

Determine the percentage of hh that do not have the basics, no productive tools, no animals

asset_vars <- 
c(
"mattress", "blanket", "mosquito_net", "solar_lamp", "portable_lamp",
"umbrella", "table", "chair_bench", "almirah_wardrobe_show_case", 
"electric_fan", "refrigerator",
"shovel", "sickle", "weaving_tool", "fish_net",
"mobile_phone", "smartphone", "radio", 
"television", "DVD_VCD_player", "computer_laptop", 
"bicycle", "motorcycle", "rickshaw_van", "CNG_tempo_electric_bike",
"chicken_duck_pigeon", "goat_sheep", "cow_buffalo"
)

Asked about but did not include in asset assessment because so few people had them: c("fish_net","almirah_wardrobe_show_case_yn", "refrigerator", "television", "DVD_VCD_player", "computer_laptop", "bicycle", "motorcycle", "rickshaw_van", "CNG_tempo_electric_bike")
```{r}


```


# Expenses
```{r expenses}
survey_data %>%
	summarise_at(
		vars(spent_monthly_vars),
		list(mean = mean),
		na.rm = TRUE
	) %>%
	gather(key = "var", value = "mean")

plot_monthly_expenditures <-
	survey_data %>%
	group_by(study_arm, fuel_30_buy_wood) %>%
	summarise_at(
		vars(spent_monthly_vars),
		list(mean),
		na.rm = TRUE
	) %>%
	gather(-study_arm, -fuel_30_buy_wood, key = "category", value = "expenditure") %>%
	mutate(
		category = as.factor(category),
		category =
			factor(
				category,
				levels = c(
					"spent_food", "buy_wood_cost", "spent_tobacco_pan", 
					"spent_clothing_month", "spent_debt_month", "spent_medical_month", 
					"spent_transport", "spent_hygiene", "spent_phone", 
					"spent_shelter_month", "spent_other_month", 
					"spent_celebrations_month",   "spent_education_month", 
					"spent_hh_items"
				),
				# labels = c(
				# 	"food", "wood", "tobacco/pan", 
				# 	"clothing", "debt", "medical", 
				# 	"transport", "hygiene", "phone", 
				# 	"shelter", "other", 
				# 	"celebrations", "education", 
				# 	"household items"
				# )
				labels = c(
					"  food  ", "  wood  ", "pan/\ntobacco", 
					"clothing", " debt ", "medical", 
					"transport", "other", "other", 
					"other", "other", 
					"other", "other", 
					"other"
				)
			),
		fuel_30_buy_wood = 
			factor(fuel_30_buy_wood, levels = c(0, 1), labels = c("Did NOT \n buy firewood \nin past 30 days", "Bought firewood \nin past 30 days "))
	) %>%
	# filter(
	# study_arm == "pre-intervention" & fuel_30_buy_wood == 0,
	# study_arm == "pre-intervention" & fuel_30_buy_wood == 1,
	# study_arm == "intervention" & fuel_30_buy_wood == 0
	# ) %>%
	ggplot(aes(x = category, y = expenditure, fill = category)) +
	geom_col() + 
	viridis::scale_fill_viridis(
		discrete = TRUE
	) +
	theme(
		axis.text.x = element_blank(), # angle = 90
		axis.ticks.x = element_blank(),
		legend.position = "bottom",
		legend.title = element_blank()
	) + 
	guides(fill = guide_legend(nrow = 1, label.position = "bottom")) + # , hjust = -40
	labs(
		title = "Monthly expenditures",
		x = "Expense category",
		y = "Monthly expenditure (BDT)"
	) +
	facet_wrap( ~ study_arm + fuel_30_buy_wood, nrow = 1)

plot_monthly_expenditures

ggsave(
	here::here("docs", "fig_monthly_expenditures.png"),
	plot = last_plot(),
	scale = 0.7,
	height = 6,
	width = 10,
	units = "in",
	device = "png"
)

survey_data %>%
	ggplot(aes(x = spent_total_month_with_6mo_monthly)) +
	geom_histogram() + 
	geom_vline(aes(xintercept = mean(spent_total_month_with_6mo_monthly, na.rm = TRUE), col = 'red'), size = 2, show.legend = TRUE) + 
	geom_vline(aes(xintercept = median(spent_total_month_with_6mo_monthly, na.rm = TRUE), col = 'blue'), size = 2, show.legend = TRUE) +
	scale_colour_manual("Legend", values = c(red = "red", blue = "blue"), labels = c("mean", "median"))
# 
# var_viz_by_histogram <- function(var_quoted) {
#   var = unquote(var_quoted)
#   survey_data %>%
#     ggplot(aes(x = var)) +
#     geom_histogram() +
#     geom_vline(aes(xintercept = mean(var, na.rm = TRUE), col = 'red'), size = 2, show.legend = TRUE) +
#     geom_vline(aes(xintercept = median(var, na.rm = TRUE), col = 'blue'), size = 2, show.legend = TRUE) +
#     scale_colour_manual("Legend", values = c(red = "red", blue = "blue"), labels = c("mean", "median"))
# }
# 
# var_viz_by_histogram(var = "spent_food")
# Quoting problem
# 
# unquote("spent_food")

# How much was spent on food? 
survey_data %>%
	ggplot(aes(x = spent_food)) +
	geom_histogram() + 
	geom_vline(aes(xintercept = mean(spent_food, na.rm = TRUE), col = 'red'), size = 2, show.legend = TRUE) + 
	geom_vline(aes(xintercept = median(spent_food, na.rm = TRUE), col = 'blue'), size = 2, show.legend = TRUE) +
	scale_colour_manual("Legend", values = c(red = "red", blue = "blue"), labels = c("mean", "median"))

# How much was spent on tobacco? 
survey_data %>%
	ggplot(aes(x = spent_tobacco_pan)) +
	geom_histogram() + 
	geom_vline(aes(xintercept = mean(spent_tobacco_pan, na.rm = TRUE), col = 'red'), size = 2, show.legend = TRUE) + 
	geom_vline(aes(xintercept = median(spent_tobacco_pan, na.rm = TRUE), col = 'blue'), size = 2, show.legend = TRUE) +
	scale_colour_manual("Legend", values = c(red = "red", blue = "blue"), labels = c("mean", "median"))
```
After food, the largest expenditure was wood (for pre-intervention hh), then tobacco and pan

```{r}
survey_data %>%
	filter(!is.na(buy_wood_cost)) %>%
	select(fuel_30_buy_wood, buy_wood_cost)

survey_data %>%
	filter(fuel_ever_buy_wood == 1, study_arm == "intervention") %>%
	select(hh_id, study_arm, fuel_ever_buy_wood, fuel_30_buy_wood, buy_wood_cost, fuel_30_collect_wood) # %>%
# tabyl(buy_wood_cost, fuel_ever_buy_wood, study_arm)

survey_data %>%
	select(study_arm, fuel_ever_buy_wood, fuel_30_buy_wood) 
```



# Housing material - no sense in factoring this into wealth since will be the same for almost all
```{r}

```



# Ventilation
```{r}
# How many hh have no windows?
survey_data %>%
	count(window_number == 0)
# Almost 80% of  hh have no windows!

# Of hh that have at least one window, what is the average number of windows?
survey_data %>%
	filter(window_number > 0) %>%
	summarise_at(vars(window_number), list(mean = mean), na.rm = TRUE)

# Of hh that have at least one window, how many have cross-ventilation (with either another window or a door)?
survey_data %>%
	filter(window_number > 0) %>%
	select(window_door_wall) %>%
	table()
```


# Credit
```{r}
# Percent that have access to credit
survey_data %>%
	count(credit_access == 1)

# Percent of hh that have access to credit thorugh specific mechanisms

# Refactor so that dk = 0

survey_data %>%
	summarise_at(
		vars(
			credit_relatives, credit_charities, credit_village_head, credit_lender, credit_bank, credit_cooperative
		),
		list(mean),
		na.rm = TRUE
	)

# Use credit to borrow money for food in past 3 months
survey_data %>%
	count(credit_borrow_money_food == 1)

# Percent that have used mobile money
survey_data %>%
	count(mobile_money == 1)
```



```{r food_dataset}
food_dataset <-
	survey_data %>%
	select(
		study_arm,
		fcn_id, 
		camp_id,
		block_id,
		subblock_id,
		hh_size,
		contains("food"), 
		contains("rice"),
		contains("bread"),
		contains("corn"),
		contains("potatoes"),
		contains("lentils"),
		contains("dairy"),
		contains("veggies"),
		contains("fruit"),
		contains("eggs"),
		contains("fish"),
		contains("poultry"),
		contains("goat_sheep"),
		contains("beef"),
		contains("oil"),
		contains("sugar")
		
	) %>%
	select(
		-c(
			contains("corner"),
			contains("boil")
		)
	)

saveRDS(food_dataset, here::here("data/food_dataset.rds"))
```


# Food consumption patterns
In the past 7 days, how many days did you eat each of the following foods?
```{r food_consumption_tab6}
## Vector of variables to summarize
# Use Hmisc::Cs to quote each variable
table6Vars <- 
	Hmisc::Cs(
		rice_adults_week,
		bread_adults_week,
		corn_adults_week,
		potatoes_adults_week,
		lentils_adults_week, 
		dairy_adults_week,
		veggies_adults_week,
		fruit_adults_week,
		eggs_adults_week,
		fish_adults_week,
		poultry_adults_week,
		goat_sheep_adults_week,
		beef_adults_week,
		oil_adults_week,
		sugar_adults_week,
		food_diversity_num_groups, 
		food_diversity_eight_groups
	)

## Vector of categorical variables that need transformation
# table6FactorVars <- table6Vars

# Create a TableOne object
tab6 <- 
	CreateTableOne(
		data = survey_data, 
		vars = table6Vars, 
		# factorVars = table6FactorVars, 
		strata = "study_arm"
	)

tab6

```

Potatoes and lentils higher in pre-intervention
Veggies and oil higher and fish substantially higher (2.81 vs 3.42) in intervention
Number of food groups is significantly higher in intervention hh (5.65 vs 5.78)

beef is high among some pre-intervention hh because in the previous week WFP held a WFP Day and distributed beef to everyone in the camp. Did they also distribute potatoes on this day?


# Food source

What % of people reply that they receive this food from aid? from the market?...what do we want to see? That people are getting more from the market? ...this could be because they are saving money since they don't have to purchase fuel

Check what is in the WPF guides.

[food_source]	0	Don't eat / don't have
[food_source]	1	Ration card / food aid
[food_source]	2	Purchased # Not sure the difference from "Purchased with wages"
[food_source]	3	Purchased with wages # Not sure the difference from "Purchased"
[food_source]	4	Gift from relative or friend
[food_source]	5	Borrow from relative or friend
[food_source]	6	Own production (own garden or animals)
[food_source]	7	Exchange labour for food
[food_source]	8	Exchange items for food
[food_source]	9	Gather, hunt, fish
[food_source] 66 Other

Why is almost all rice purchased with wages? Not food aid? Some also report that they gather it?

```{r}
## Vector of variables to summarize
# Use Hmisc::Cs to quote each variable
table15Vars <- food_source_all

# table15Vars <- 
# 	Hmisc::Cs(
# 		rice_source,
# 		bread_source,
# 		corn_source,
# 		potatoes_source,
# 		lentils_source, 
# 		dairy_source,
# 		veggies_source,
# 		fruit_source,
# 		fish_source,
# 		poultry_source,
# 		goat_sheep_source,
# 		beef_source,
# 		oil_source,
# 		sugar_source
# 	)

## Vector of categorical variables that need transformation
# table15FactorVars <- table15Vars

# Create a TableOne object
tab15 <- 
	CreateTableOne(
		data = survey_data, 
		vars = table15Vars, 
		# factorVars = table15FactorVars, 
		strata = "study_arm"
	)

tab15
```

veggies_source6, fish_source1, fish_source2 are sig higher in intervention, veggies_source1 (0.01 vs 0.07), fish_source1 sub higher (0.05 vs 0.12), beef_source2 (0.15 vs 0.21), oil_source1 (0.84 vs 0.96), -> intervention are receiving more fish through aid distribution, but purchasing beef (beef_source1 0.15 in pre-intervention compared to 0.01 in intervention due to WFP distribution day), 


# Coping necessity and strategies

# NEED TO FIX THIS 

```{r}
survey_data %>%
	select(food_insufficient_nutrition) %>%
	table()

survey_data %>%
	select(food_didnt_want) %>%
	table()

survey_data %>%
	select(food_cant_afford_2wk) %>%
	table()

# What did you do?
# food_cant_afford_action
survey_data %>%
	select(food_cant_afford_action) %>%
	table()

# Most difficult 
# Rank by the percentage of hh that report the most difficult

# food_cant_afford_difficult
survey_data %>%
	select(food_cant_afford_difficult) %>%
	table()

# Of those that report having to do this action, the weekly frequency

# Least difficult
# Rank by the percentage of hh that report the least difficult

# food_cant_afford_easiest
survey_data %>%
	select(food_cant_afford_easiest) %>%
	table()

# Of those that report having to do this action, the weekly frequency

# fuel
survey_data %>%
	select(fuel_cant_afford_2wk) %>%
	table()

# What did you do?
# food_cant_afford_action
survey_data %>%
	select(fuel_cant_afford_action) %>%
	table()

## Vector of variables to summarize
# Use Hmisc::Cs to quote each variable
table16Vars <- 
	Hmisc::Cs(
		borrow_food, reduce_food, 
		reduce_meals_lack_food, not_eat_lack_food, restrict_food,
		borrow_fuel, reduce_fuel, 
		reduce_meals_lack_fuel, not_eat_lack_fuel
	)

## Vector of categorical variables that need transformation
table16FactorVars <- table16Vars

# Create a TableOne object
tab16 <- 
	CreateTableOne(
		data = survey_data, 
		vars = table16Vars, 
		factorVars = table16FactorVars, 
		strata = "study_arm"
	)

tab16

```

# Fuel sources
Percentage of hh that have used the following fuel sources in the past 30 days

```{r fuel_use}
survey_data %>%
	count(fuel_ever_collect_wood == 1)
# Why are 393 NA? because we added the question late?

## Vector of variables to summarize
# Use Hmisc::Cs to quote each variable
table7Vars <- 
	Hmisc::Cs(
		fuel_ever_scraps,
		fuel_ever_collect_wood,
		fuel_ever_receive_wood,
		fuel_ever_buy_wood,
		fuel_ever_receive_lpg,
		fuel_ever_buy_lpg,
		fuel_ever_receive_crh,
		fuel_ever_buy_crh,
		fuel_ever_other
	)

## Vector of categorical variables that need transformation
table7FactorVars <- table7Vars

# Create a TableOne object
tab7 <- 
	CreateTableOne(
		data = survey_data, 
		vars = table7Vars, 
		factorVars = table7FactorVars, 
		strata = "study_arm"
	)

tab7

## Vector of variables to summarize
# Use Hmisc::Cs to quote each variable
table8Vars <- 
	Hmisc::Cs(
		fuel_30_gather_scraps,
		fuel_30_collect_wood,
		fuel_30_receive_wood,
		fuel_30_buy_wood,
		fuel_30_receive_lpg,
		fuel_30_buy_lpg,
		fuel_30_receive_crh,
		fuel_30_buy_crh,
		fuel_30_other
	)

## Vector of categorical variables that need transformation
table8FactorVars <- table8Vars

# Create a TableOne object
tab8 <- 
	CreateTableOne(
		data = survey_data, 
		vars = table8Vars, 
		factorVars = table8FactorVars, 
		strata = "study_arm"
	)

tab8
```

# Based on IDIs and FGDs, "other is likely plastic

```{r fuel_plastic}
survey_data %>%
	tabyl(burn_plastic_frequency, study_arm)

# Almost 150 of 393 hh report burning househols every day! We need to better understand how many meals and if they are relying on plastic for all of the fuel they need or if it is used in combination with other fuel sources

```

# Who gathers fuel

Not mutally exclusive
```{r who_collects_fuel_tab9}
## Vector of variables to summarize
# Use Hmisc::Cs to quote each variable
table9Vars <- 
	Hmisc::Cs(
		gather_scraps_w, gather_scraps_m, gather_scraps_g, gather_scraps_b,
		collect_wood_w, collect_wood_m, collect_wood_g, collect_wood_b,
		buy_wood_w, buy_wood_m, buy_wood_g, buy_wood_b,
		receive_wood_w, receive_wood_m, receive_wood_g, receive_wood_b,
		receive_lpg_w, receive_lpg_m, receive_lpg_g, receive_lpg_b,
		buy_lpg_w, buy_lpg_m, buy_lpg_g, buy_lpg_b,
		receive_crh_w, receive_crh_m, receive_crh_g, receive_crh_b,
		buy_crh_w, buy_crh_m, buy_crh_g, buy_crh_b
	)

## Vector of categorical variables that need transformation
table9FactorVars <- table9Vars

# Create a TableOne object
tab9 <- 
	CreateTableOne(
		data = survey_data, 
		vars = table9Vars, 
		factorVars = table9FactorVars #, 
		# strata = "study_arm"
	)

tab9

# # Add N for each fuel type
# survey_data %>%
# 	summarise_at(
# 		vars(
# 			gather_scraps_w, gather_scraps_m, gather_scraps_g, gather_scraps_b,
# 			collect_wood_w, collect_wood_m, collect_wood_g, collect_wood_b,
# 			buy_wood_w, buy_wood_m, buy_wood_g, buy_wood_b,
# 			receive_wood_w, receive_wood_m, receive_wood_g, receive_wood_b,
# 			receive_lpg_w, receive_lpg_m, receive_lpg_g, receive_lpg_b,
# 			buy_lpg_w, buy_lpg_m, buy_lpg_g, buy_lpg_b,
# 			receive_crh_w, receive_crh_m, receive_crh_g, receive_crh_b,
# 			buy_crh_w, buy_crh_m, buy_crh_g, buy_crh_b
# 		),
# 		list(mean),
# 		na.rm = TRUE
# 	) %>%
# 	gather(key = "gather_who", value = "pc_hh")
# 
# # Use kable to make this into four columns with women, men, girls, and boys at the top. 

```

Men are primarily responsible for gathering all types of fuel; we should see that more women are getting LPG as some camps (like 8w) require that women procure the LPG. 

# Firewood collection
```{r}
survey_data %>%
	filter(!is.na(collect_wood_forest_start)) %>%
	select(
		collect_wood_forest_start,
		collect_wood_forest_stop,
		buy_wood_when_start
	) 

# # Hm, not sure how to add this to the data frame
# survey_data <-
#   mutate(
#     collect_wood_forest_start_dmy = dmy(survey_data$collect_wood_forest_start),
#     collect_wood_forest_stop_dmy =  dmy(survey_data$collect_wood_forest_stop),
#     collect_wood_duration = difftime(collect_wood_forest_stop_dmy, collect_wood_forest_start_dmy,
#                                      units = c("weeks"))
#   ) %>%
#   select(collect_wood_forest_start, collect_wood_forest_stop, collect_wood_duration)

# Of the hh that have stopped collecting firewood, what is the average duration of firewood collection?  
# How many hh are still collecting firewood?
# survey_data$collect_wood_duration <- 
difftime(
	dmy(survey_data$collect_wood_forest_stop),
	dmy(survey_data$collect_wood_forest_start),
	units = c("weeks")
) %>%
	mean(na.rm = TRUE)
```
49.4 weeks

```{r}

```

## Time spent gathering wood
```{r}

summary(survey_data$collect_wood_walk_hr)

survey_data %>%
	ggplot(aes(x = collect_wood_walk_hr)) +
	geom_bar() +
	# geom_histogram(stat = "count") + 
	geom_vline(aes(xintercept = mean(collect_wood_walk_hr, na.rm = TRUE), col = 'red'), size = 2, show.legend = TRUE) + 
	# geom_vline(aes(xintercept = median(collect_wood_walk_hr, na.rm = TRUE), col = 'blue'), size = 2, show.legend = TRUE) +
	# scale_colour_manual("Legend", values = c(red = "red", blue = "blue"), labels = c("mean", "median")) +
	scale_colour_manual("Legend", values = c(red = "red"), labels = c("mean")) +
	scale_x_continuous(breaks = 0:11, minor_breaks = NULL) +
	labs(
		x = "Round-trip time to walk to the forest and collect wood (hr)", 
		y = "Number of households"
	) +
	theme_classic()

ggsave(
	file_barplot_firewood_collection_hours, 
	plot = last_plot(),
	device = "png"
)
```


## Number of times firewood is gathered per week
collect_wood_times_week
```{r}
survey_data %>%
	filter(collect_wood_times_week >= 6) %>%
	select(
		hh_size, 
		collect_wood_times_week, 
		collect_wood_walk_hr, 
		forest_wood_fee, 
		fuel_30_buy_wood, 
		fuel_30_receive_crh, 
		fuel_30_buy_crh
	) %>%
	arrange(hh_size, collect_wood_times_week)

survey_data %>%
	ggplot(aes(x = collect_wood_times_week)) +
	geom_bar() +
	# geom_histogram(stat = "count") + 
	geom_vline(aes(xintercept = mean(collect_wood_times_week, na.rm = TRUE), col = 'red'), size = 2, show.legend = TRUE) + 
	# geom_vline(aes(xintercept = median(collect_wood_walk_hr, na.rm = TRUE), col = 'blue'), size = 2, show.legend = TRUE) +
	# scale_colour_manual("Legend", values = c(red = "red", blue = "blue"), labels = c("mean", "median")) +
	scale_colour_manual("Legend", values = c(red = "red"), labels = c("mean")) +
	scale_x_continuous(breaks = 0:11, minor_breaks = NULL) +
	labs(
		x = "Number of trips to collect firewood/week", 
		y = "Number of households"
	) +
	theme_classic()

survey_data %>%
	ggplot(aes(x = hh_size, y = collect_wood_times_week, color = collect_wood_walk_hr)) +
	geom_point() + 
	scale_color_viridis_c() + 
	# Need to fix ticks so they are whole numbers
	facet_grid(. ~ fuel_30_buy_wood)

# There are 3 hh that collect 8-9 times per week and they do not have huge hh_size and are not very close to the forest though they also don't buy any fuel.


ggsave(
	file_barplot_firewood_collection_frequency, 
	plot = last_plot(),
	device = "png"
)
```

## Cost to enter the forest for firewood
forest_wood_fee
```{r}
survey_data %>%
	ggplot(aes(x = forest_wood_fee)) +
	geom_histogram() + 
	geom_vline(aes(xintercept = mean(forest_wood_fee, na.rm = TRUE), col = 'red'), size = 2, show.legend = TRUE) + 
	geom_vline(aes(xintercept = median(forest_wood_fee, na.rm = TRUE), col = 'blue'), size = 2, show.legend = TRUE) +
	scale_colour_manual("Legend", values = c(red = "red", blue = "blue"), labels = c("mean", "median"))

survey_data %>%
	ggplot(aes(x = collect_wood_walk_hr, y = forest_wood_fee, color = collect_wood_times_week)) +
	geom_point() + 
	scale_color_viridis_c()

survey_data %>%
	filter(forest_wood_fee > 100) %>%
	select(forest_wood_fee, collect_wood_walk_hr, collect_wood_times_week)
```
4 hh report a cost of 200 BDT to enter the forest, which is high, especially considering the next highest is 120 BDT. Mistake?

## Cost of firewood
buy_wood_cost 
"In the past 30 days, how much money (taka) did you spend on firewood?"
```{r}
survey_data %>%
	ggplot(aes(x = buy_wood_cost)) +
	geom_histogram() + 
	geom_vline(aes(xintercept = mean(buy_wood_cost, na.rm = TRUE), col = 'red'), size = 2, show.legend = TRUE) + 
	geom_vline(aes(xintercept = median(buy_wood_cost, na.rm = TRUE), col = 'blue'), size = 2, show.legend = TRUE) +
	scale_colour_manual("Legend", values = c(red = "red", blue = "blue"), labels = c("mean", "median"))

survey_data %>%
	filter(buy_wood_cost > 3000) %>%
	select(buy_wood_cost, hh_size, fuel_30_collect_wood, fuel_30_buy_lpg, stove_boil_drink, stove_boil_bathe, stove_reason_stay_warm, stove_reason_cook_together, stove_reason_sell_food)

survey_data %>%
	ggplot(aes(x = hh_size, y = buy_wood_cost)) +
	geom_point() + 
	facet_grid(. ~ fuel_30_collect_wood)
```
Since the hh that reported spent most purchasing firewood don't have an obvious reason for this (they don't have huge hh size though are cooking for an un-recorded number of other people). It appears that these hh reporting very high cost of firewood just have bad recall, or there is an error.

## Reason for using wood fuel
1	We don’t have enough of other types of fuel
2	We prefer using wood to cook food
66	Other

Need to take account for hh that both gather wood and buy wood
Make the question: Among hh that use wood (collect or purchase), why do they use wood?
```{r}
survey_data %>%
	select(gather_wood_reason, buy_wood_reason) %>%
	filter(gather_wood_reason == 66)

survey_data %>%
	filter(!is.na(gather_wood_reason) & !is.na(buy_wood_reason)) %>%
	mutate(
		gather_buy_wood_reason_discordant = ifelse(gather_wood_reason != buy_wood_reason, "discordant", 0)
	) %>%
	filter(gather_buy_wood_reason_discordant == "discordant")
# There are only two households that are discordant

survey_data %>%
	select(gather_wood_reason) %>%
	table()
# 16 people reported "other reason" for gathering wood -> what?

survey_data %>%
	select(buy_wood_reason) %>%
	table()

# 4 people reported "other reason" for buying wood -> what?

survey_data %>%
	filter(!is.na(gather_wood_reason) | !is.na(buy_wood_reason)) %>%
	mutate(
		gather_buy_wood_reason = 
			case_when(
				gather_wood_reason == 1 & buy_wood_reason == 1 ~ 1,
				is.na(gather_wood_reason) & buy_wood_reason == 1 ~ 1,
				gather_wood_reason == 1 & is.na(buy_wood_reason) ~ 1,
				gather_wood_reason == 2 & buy_wood_reason == 2 ~ 2,
				is.na(gather_wood_reason) & buy_wood_reason == 2 ~ 2,
				gather_wood_reason == 2 & is.na(buy_wood_reason) ~ 2,
				TRUE ~ 66 # These are any hh that have 
			)
	) %>%
	select(gather_buy_wood_reason) %>% # gather_wood_reason, buy_wood_reason, 
	table()
```

Almost all hh that rely on firewood report the primary reason they use firewood is because they do not have enough of other fuel sources; only 34/(475+34+20) report that the primary reason they use firewood is because they prefer the taste. 


# Forest use

## vegetation_dead when collected for fuel?
1	Yes, the scraps/wood I collect are all dead
2	I collect some scraps/wood that are dead and I gather scraps/leaves/twigs while they are still alive
3	I cut down live plants for the twigs/wood I need
```{r}
survey_data %>%
	select(gather_scraps_dead) %>%
	table()

survey_data %>%
	select(gather_wood_dead) %>%
	table()
```

## Wood for reasons other than cooking
"Have you or your family ever collected firewood for purposes other than your own household's cooking needs (cooking food to sell, etc)?"

```{r}
survey_data %>%
	select(gather_wood) %>%
	table()
```
16 report gathering wood for reasons other than their own household's cooking - how does this compare to the number that cook to sell (1?), the number that cook to stay warm (?) + the number that cook for non-household member (guessing these people didn't include themselves)

## Forest for reasons other than wood
"Have you or your family ever gone to the forest to take anything other than wood (food, household materials, etc)?"
```{r other_forest_use_tab10}
survey_data %>%
	select(forest_collect_not_wood) %>%
	table()


## Vector of variables to summarize
table10Vars <- 
	c(
		"reason_forest_food", "reason_forest_med", "reason_forest_shelter",
		"reason_forest_privacy", "reason_forest_defecation", "reason_forest_leisure",
		"reason_forest_other", "reason_forest_other_specified"
	)

## Vector of categorical variables that need transformation
table10FactorVars <- table10Vars

# Create a TableOne object
tab10 <- 
	CreateTableOne(
		data = survey_data, 
		vars = table10Vars, 
		factorVars = table10FactorVars, 
		strata = "study_arm"
	)

tab10

survey_data %>%
	ggplot(aes(x = cost_forest_not_wood)) +
	geom_histogram() + 
	geom_vline(aes(xintercept = mean(cost_forest_not_wood, na.rm = TRUE), col = 'red'), size = 2, show.legend = TRUE) + 
	geom_vline(aes(xintercept = median(cost_forest_not_wood, na.rm = TRUE), col = 'blue'), size = 2, show.legend = TRUE) +
	scale_colour_manual("Legend", values = c(red = "red", blue = "blue"), labels = c("mean", "median"))

survey_data %>%
	summarise_at(vars(cost_forest_not_wood), list(mean), na.rm = TRUE)

survey_data %>%
	filter(forest_collect_not_wood == 1) %>%
	select(cost_forest_not_wood, starts_with("reason_forest")) %>%
	arrange(desc(cost_forest_not_wood))

```


14% of 36 people replied that they go to the forest for "other" reasons but no other reasons are specified - why?...becuase on Q487 cost_forest_not_wood the relevance is wrong...selected({reason_forest},'66') should have been selected({reason_forest_other},'1')...oops

--> ask about this in the fgd?

Three hh report paying <100 BDT to go into the forest for non-wood. This is ever more than was paid to collect firewood. Interestingly, the one hh that paid 300 BDT was the only hh that went to the forest for privacy (and they recorded privacy as the only reason for going)







# Time to collect fuel
Combine all survey data
- For pre- and post-intervention results, collect both so that we can compare recall reliability and then average before combining with intervention group. 
```{r fuel_collection_time}
survey_data %>%
	group_by(study_arm) %>%
	summarise_at(
		vars(
			collect_wood_walk_hr,
			# receive_wood_walk, # Missing this question
			receive_wood_wait,
			receive_lpg_walk,
			receive_lpg_wait,
			buy_lpg_walk,
			buy_lpg_wait,
			receive_crh_walk,
			receive_crh_wait
		),
		list(mean),
		na.rm = TRUE
	) %>%
	gather(-study_arm, key = "activity", value = "time_hr_or_min")

survey_data %>%
	ggplot(aes(x = collect_wood_walk_hr)) +
	geom_histogram() + 
	geom_vline(aes(xintercept = mean(collect_wood_walk_hr, na.rm = TRUE), col = 'red'), size = 2, show.legend = TRUE) + 
	geom_vline(aes(xintercept = median(collect_wood_walk_hr, na.rm = TRUE), col = 'blue'), size = 2, show.legend = TRUE) +
	scale_colour_manual("Legend", values = c(red = "red", blue = "blue"), labels = c("mean", "median"))

ggsave(
	here::here("docs", "fig_collect_wood_walk_hr.png"),
	plot = last_plot(),
	scale = 0.7,
	height = 6,
	width = 10,
	units = "in",
	device = "png"
)
```





# Stove use
```{r}
# Percent of hh that use their stoves for the following reasons

# will need to separate pre-intervention, intervention, and post-intervention groups --> of course, will need to separate for every analysis...

survey_data %>%
	summarise_at(
		vars(
			traditional_use_yesterday, # Number of times traditional stove was used yesterday
			LPG_use_yesterday, # Number of times LPG stove was used yesterday
			stove_boil_drink, # Pc of hh that boil drinking water
			stove_boil_bathe, # Pc of hh that boil bathing water
			boil_yesterday_times, # Number of times the stove was used for boiling water yesterday
			stove_reason_stay_warm, # Pc of hh that use the stove to stay warm
			stove_reason_cook_together, # Pc of hh that use the stove to stay warm
			stove_reason_sell_food, # Pc of hh that use the stove to cook food to sell
			# cook_sell_yesterday is associated with the question "In the past 7 days, how many days did you cook food to sell?" so 7 is a reasonable answer
			# cook_sell_yesterday, # Of hh that cook food to sell, the number of times they cooked food to sell yesterday (maybe don't include this because cooking to sell was so rare)
			cook_sell_days_week,
			# cook_to_sell, # Of hh that cook food to sell, the percentage of total food cooked that they sell
			cook_to_sell_percent
		),
		list(mean),
		na.rm = TRUE
	) %>%
	gather(key = "stove_type", value = "pc_hh_or_uses_per_day")

# Good, no one was using LPG yesterday


# In the past 7 days, how many days did you cook food to sell 
survey_data %>%
	ggplot(aes(x = cook_sell_days_week)) +
	geom_histogram() + 
	geom_vline(aes(xintercept = mean(cook_sell_days_week, na.rm = TRUE), col = 'red'), size = 2, show.legend = TRUE) + 
	geom_vline(aes(xintercept = median(cook_sell_days_week, na.rm = TRUE), col = 'blue'), size = 2, show.legend = TRUE) +
	scale_colour_manual("Legend", values = c(red = "red", blue = "blue"), labels = c("mean", "median"))

```

### For hh that reported purchasing firewood, is this becuase they were selling wood or were using extra fuel to stay warm, cood for others, or cook to sell?
```{r}
survey_data %>%
	#filter(fuel_30_collect_wood, income_selling_wood > 0, fuel_30_buy_wood, buy_wood_cost > 0) %>%
	select(
		income_selling_wood,
		buy_wood_cost,
		traditional_use_yesterday, # Number of times traditional stove was used yesterday
		LPG_use_yesterday, # Number of times LPG stove was used yesterday
		stove_boil_drink, # Pc of hh that boil drinking water
		stove_boil_bathe, # Pc of hh that boil bathing water
		boil_yesterday_times, # Number of times the stove was used for boiling water yesterday
		stove_reason_stay_warm, # Pc of hh that use the stove to stay warm
		stove_reason_cook_together, # Pc of hh that use the stove to stay warm
		stove_reason_sell_food, # Pc of hh that use the stove to cook food to sell
		# cook_sell_yesterday is associated with the question "In the past 7 days, how many days did you cook food to sell?" so 7 is a reasonable answer
		# cook_sell_yesterday, # Of hh that cook food to sell, the number of times they cooked food to sell yesterday (maybe don't include this because cooking to sell was so rare)
		cook_sell_days_week,
		# cook_to_sell, # Of hh that cook food to sell, the percentage of total food cooked that they sell
		cook_to_sell_percent
	)

```

## Efficiency
```{r cooking_efficiency_tab11}

## Vector of variables to summarize
# Use Hmisc::Cs to quote each variable
table11Vars <- 
	c("soak_rice", "soak_lentils", "cover_pot")

## Vector of categorical variables that need transformation
table11FactorVars <- table11Vars

# Create a TableOne object
tab11 <- 
	CreateTableOne(
		data = survey_data, 
		vars = table11Vars, 
		factorVars = table11FactorVars, 
		strata = "study_arm"
	)

tab11
```


## Who cooks
Percentage of hh that mention women, girls, men, and boys cook
```{r cook_who_tab12}
## Vector of variables to summarize
# Use Hmisc::Cs to quote each variable
table12Vars <- 
	c("cook_who_w", "cook_who_g", "cook_who_m", "cook_who_b")

## Vector of categorical variables that need transformation
table12FactorVars <- table12Vars

# Create a TableOne object
tab12 <- 
	CreateTableOne(
		data = survey_data, 
		vars = table12Vars, 
		factorVars = table12FactorVars, 
		strata = "study_arm"
	)

tab12
```

cook_who_b = 0 (%) why for other groups reportedd as ==1 ? because there was 0 boys so it doesn't show up as a factor?



# LPG use and safety
Average duration between when enrolled in LPG and when receive LPG and training
Separate for UNHCR and IOM areas



```{r}
# The following dates should already be in date format but for some reason they are not so use dmy to make them into dates
lpg_wait_duration <- 
	difftime(dmy(survey_data$first_receive_lpg), dmy(survey_data$first_enrolled_lpg), units = "weeks") 

lpg_use_without_training <-
	difftime(dmy(survey_data$date_safety_training), dmy(survey_data$first_receive_lpg), "weeks") %>%
	mean(na.rm = TRUE)

```

### Prior familiarity with LPG
```{r}
survey_data %>%
	summarise_at(
		vars(lpg_prior_use),
		list(mean),
		na.rm = TRUE
	)
```

### Safety
fire_cause for fire_why
1	Carelessness
2	I was busy with other work
3	While children were playing with the fire
4	Due to the low height of the roof and/or the stove was close to the fence
5	Don't know
66	Other

fire_consequence
1	Entire household burned out
2	Part of the household burned out
3	Mild burn of the children
4	Severe burn of the children
5	Severe burn of the adult 
6	Mild burn of the adult
7	People die
8	Don't know
66	Other

```{r stove_safety_tab13}
## Vector of variables to summarize
table13Vars <- 
	c(
		"stove_training", 
		"lpg_safety_visit", 
		"lpg_gas_leak", 
		"lpg_child_burn", 
		"fire_number"
	)

## Vector of categorical variables that need transformation
table13FactorVars <- table13Vars

# Create a TableOne object
tab13 <- 
	CreateTableOne(
		data = survey_data, 
		vars = table13Vars, 
		factorVars = table13FactorVars, 
		strata = "study_arm"
	)

tab13

survey_data %>%
	summarise_at(
		vars(
			stove_training, 
			lpg_safety_visit, 
			lpg_gas_leak, 
			lpg_child_burn, 
			fire_number
		),
		list(mean),
		na.rm = TRUE
	) %>%
	gather(key = "activity", value = "pc_hh")

survey_data %>%
	select(safety_stove_training) %>%
	table()

survey_data %>%
	summarise_at(
		vars(starts_with("training_")),
		list(mean),
		na.rm = TRUE
	) %>%
	gather(key = "training_type", value = "pc_hh")

survey_data %>%
	select(lpg_no_training_learn) %>%
	table()

survey_data %>%
	select(flooring_below_stove) %>%
	table()

survey_data %>%
	select(space_between_wall_stove) %>%
	table()

survey_data %>%
	select(lpg_afraid) %>%
	table()

survey_data %>%
	filter(!is.na(lpg_afraid)) %>%
	select(lpg_afraid_why)

survey_data %>%
	select(fire_why) %>%
	table()

survey_data %>%
	select(fire_consequence) %>%
	table()
```

## LPG refills and sufficiency

refill_time_lpg_missed
0	No
1	Yes,  I couldn't go on the exact refill date and they wouldn't let me go on a different day
2	Yes, other
3	Don't know
```{r}
survey_data %>%
	select(refill_time_lpg_missed) %>%
	table()
```

times_bf_refill
"How long before the next LPG refill does your household run out of LPG for cooking food. (Answer in meals or days – select the answer that best matches the response)"
1	1-3 days before my refill
2	4-6 days before my refill
3	7-9 days before my refill
4	10+ days before my refill
5	1-5 meals before my refill 
6	6-10 meals before my refill 
7	10-15 meals before my refill 
8	15-20 meals before my refill 
9	20+ meals before my refill
10	1-3 meals per week
11	4-6 meals per week
12	7-9 meals per week
13	10+ meals per week

```{r}
survey_data %>%
	select(fuel_use_non_lpg_freq_cook) %>%
	table()
```

## Use of extra fuel
lpg_use
1	Prepare snacks/ food that I sell
2	Give the extra LPG to others for free
3	Sell the extra LPG to another household
4	Sell the extra LPG to a restaurant
5	Keep on using it myself
6	We never have more than we need to cook for just my family

```{r}
survey_data %>%
	select(lpg_extra_use) %>%
	table()
```

# Receive LPG but use other fuel
##  
"For cooking food or boiling water, do you ever have to use fuel other than the LPG that you receive?""
```{r}
survey_data %>%
	select(fuel_use_non_lpg_ever) %>%
	table()

survey_data %>%
	summarise_at(
		vars(starts_with("fuel_use_non_lpg")),
		list(mean),
		na.rm = TRUE
	) %>%
	gather(key = "alternative_fuel", value = "pc_hh")
```

## Place purchase more LPG
1	I go to an established market
2	Someone transports the LPG close to me (not a market, selling out of a CNG)

## Fuel prior to LPG distribution
```{r}
survey_data %>%
	select(fuel_type_before_lpg) %>%
	table() 

```

## Livestyle changes since LPG distribution
lpg_changes_lifestyle is select_multiple... table percent of hh that answered each?
```{r}
survey_data %>%
	group_by(study_arm) %>%
	summarise_at(
		vars(starts_with("lpg_changes_lifestyle")),
		list(mean), 
		na.rm = TRUE
	) %>%
	gather(key = "lifestyle_change", value = "pc_hh")
```




# Time use
"Think about a day before you obtained LPG at the distribution center and compare it to now, when you do get LPG from the distribution center. Compared to before, do you think that YOU currently spend MORE or LESS time on each of the following activities?"
Same question for children's time

Only asked to intervention and post-intervention hh and ONLY if they report previously 
selected(${fuel_ever_receive_lpg},'1') and (selected(${collect_wood_g},'1') or selected(${collect_wood_b},'1'))
Post-intervention might have better recall because they more recently transition; so assess separately and combine if it seems reasonable to do so.


For the group "time_free_lpg" - the relevance is "selected(${fuel_30_receive_lpg},'1') and (selected(${collect_wood_g},'1') or selected(${collect_wood_b},'1'))" - this means we ONLY asked the time use questions to family's who's CHILDREN collected wood. That's fine for the group "time_child_free_lpg" but not for the adult respondent question! 

[more_less]	1	more 
[more_less]	2	same
[more_less]	3	less


Assess percentage of hh that say they spend more and less time on each type of activity

activity left column, more-less on top row

```{r}
time_child_more_less <-
	survey_data %>%
	filter(study_arm == "intervention") %>%
	select(hh_id, study_arm, starts_with("time_child")) %>% # For now, don't evaluation time that is not time_child
	filter(!is.na(time_child_cooking)) %>% # this question was only answered if girls or boys were reported to collect firewood
	# count() # There were only 38 respondents of 597 hh that answered the intervention survey
	gather(-hh_id, -study_arm, key = "activity", value = "more_less") %>%
	group_by(activity) %>%
	count(more_less) %>%
	mutate(pc = n / sum (n) * 100) %>%
	mutate(pc = ifelse(more_less == "less", pc * (-1), pc)) %>%
	select(-n) %>%
	ungroup() %>%
	mutate(
		activity = 
			ordered(
				activity, 
				levels = 
					c(
						"time_child_harvesting_wood",
						"time_child_gathering_nonwood_items", 
						"time_child_collecting_water", 
						"time_child_cooking", 
						"time_child_cleaning",
						"time_child_school", 
						"time_child_socializing",
						"time_child_sleeping", 
						"time_child_nothing"
					),
				labels = 
					c(
						"Harvesting wood",
						"Gathering non-wood items",
						"Collecting water", 
						"Cooking", 
						"Cleaning",  
						"Going to school", 
						"Socializing", 
						"Sleeping",
						"Nothing"
					)
			),
		more_less = 
			ordered(
				more_less,
				levels = c(1, -1), 
				labels = c("more", "less")
			)
	) # %>%
# spread(more_less, pc)

fig_time_child_more_less <-
	time_child_more_less %>%
	filter(more_less != "same") %>%
	ggplot(aes(x = activity, y = pc, fill = more_less)) +
	geom_col(position = "dodge") + 
	viridis::scale_fill_viridis(
		discrete = TRUE,
		begin = 9/10,
		end = 1/10, 
		name = "Amount of time",
		breaks = c("more", "less"),
		labels = c("More", "Less")
	) + 
	theme_classic() +
	theme(
		axis.text.x = element_text(angle = 45, hjust = 1)
	) +
	labs(
		title = "Reported change in time spent by children \nwho used to collect firewood after receiving LPG",
		x = "Activity",
		y = "Percent of households reporting change \n(n = 38)"
	)

fig_time_child_more_less

ggsave(
	here::here("docs", "fig_time_child_more_less.png"),
	plot = last_plot(),
	scale = 0.7,
	height = 6,
	width = 10,
	units = "in",
	device = "png"
)

```

# Drugery
1	Cooking
2	Washing dishes
3	Washing clothes
4	Collecting water (including time traveling to the water pump and time acquiring water)
5	Harvesting wood from the forest
6	Caring for children (washing, dressing, bathing)
7	Caring for the sick, disabled, or elderly (washing, dressing, bathing)
88	NA/Nothing is difficult

```{r}
survey_data %>%
	select(enumerator, start_date, drudgery_most_diff, drudgery_second_most_diff, drudgery_easiest) %>%
	arrange(enumerator, start_date)

survey_data %>%
	select(drudgery_most_diff, drudgery_second_most_diff) %>%
	table()

survey_data %>%
	select(drudgery_most_diff) %>%
	table()

survey_data %>%
	select(drudgery_second_most_diff) %>%
	table()

survey_data %>%
	select(drudgery_easiest) %>%
	table()
```

Many hh have drudgery_most_diff == drudgery_second_most_diff == drudgery_easiest. Training enumerators that they should not be the same thing was an oversight. 
There are also many NAs, because the question wasn't required- but why did they not just answer? I don't see any skip logic on it. 
Will probably have to throw this question out. = (




















# Harassment

sex_contact = "Has somebody ever brushed up against you or one of your family members in a sexual way on purpose?"

## Test examples
```{r harassment, include=FALSE}
# The percentage of households that experienced specific types of harassment at any time since they entered the camp


survey_data %>%
	summarise_at(any_harassment_hh, mean, na.rm = TRUE)

survey_data %>%
	select(any_harassment_hh) %>%
	View()

# # The percentage of households that experienced choking when engaged in the following fuel collection activities since they entered the camp -> Factor not numeric 0 = no, 1 = yes
# survey_data %>%
#  	mutate_at(c("collect_wood_choke_hh", "buy_wood_choke_hh", "receive_wood_choke_hh", "receive_lpg_choke_hh", "buy_lpg_choke_hh", "receive_crh_choke_hh", "buy_crh_choke_hh"), list(as.numeric)) %>%
# 	summarise_at(c("collect_wood_choke_hh", "buy_wood_choke_hh", "receive_wood_choke_hh", "receive_lpg_choke_hh", "buy_lpg_choke_hh", "receive_crh_choke_hh", "buy_crh_choke_hh"), mean, na.rm = TRUE)
# 
# 
# # Of those who experienced choking the mean number of times they experienced choking  -> Factor not numeric 0 = no, 1 = yes
# survey_data %>%
# 	mutate_at(c("collect_wood_choke_m", "collect_wood_choke_w", "collect_wood_choke_b", "collect_wood_choke_g"), list(as.numeric)) %>%
# 	summarise_at(c("collect_wood_choke_m", "collect_wood_choke_w", "collect_wood_choke_b", "collect_wood_choke_g"), mean, na.rm = TRUE)
```

For whether or not the type of harassment happened during the particular fuel collection activity, convert "Don't know" = 99 to NA.

## Harassment prevalence
The percentage of households that experienced specific types of harassment at any time since they entered the camp

The response to each harassment question was selected from yes_no_dk:
0	No
1	Yes
77	Refused
99 Don't know

```{r harassment_prev, echo=FALSE, fig.height=6, fig.width=10}


# Prevalence of harassment of certain genders; denominator is hh with that gender that EVER collected type X fuel 
# scraps_gather_insult_men_yn == 1 / (scraps_gather_m == 1)

# survey_data %>%
# 	select(harassment_vars_yn) %>% # any_harassment_hh, fuel_collection_who, 
# 	View()

fuel_collection_who_alt_order <- c()
for (person in c("w", "g", "m", "b")){
	for (fuel in c("gather_scraps", "collect_wood", "receive_wood", "buy_wood", "receive_lpg", "buy_lpg", "receive_crh", "buy_crh")){
		fuel_collection_who_alt_order <- c(fuel_collection_who_alt_order, paste(fuel, person, sep = "_"))
	}
}

fuel_collection_who_alt_order_summary <-
	survey_data %>%
	summarise_at(fuel_collection_who_alt_order, sum, na.rm = TRUE) %>%
	gather(key = "fuel_type_gender", value = "number_hh_collecting_fuel")

fuel_collection_who_alt_order_summary %>%
	filter(str_detect(fuel_type_gender, pattern = 'gather_scrap|collect_wood|receive_lpg'))

harassment_prev <-
	survey_data %>%
	select(ends_with("_w_yn"), ends_with("_m_yn"), ends_with("_g_yn"), ends_with("_b_yn")) %>%
	
	# accidentally selected bc they contain g_yn
	# select(-target_child_breathing_yn, diff_concentrating_yn, cant_get_going_yn) %>% 
	
	# select(!contains("insult")) %>%
	# select(!contains("belittle")) %>%
	# select(!contains("scare")) %>%
	# select(!contains("push")) %>%
	# select(!contains("hit")) %>%
	# select(!contains("kick")) %>%
	# select(!contains("choke")) %>%
# select(!contains("weapon")) %>%
# select(!contains("sex_lang")) %>%
# select(!contains("sex_contact")) %>%
# select(!contains("sex_rumor")) %>%
# select(!contains("clothing_pull")) %>%
# select(!contains("sex_corner"))
# select(contains("sex_corner")) %>% # insult 32, belittle 32, scare 32, push 32, hit 32, kick 32, choke 32, wearpon 32, sex_lang 32, sex_contact 32, sex_rumor 32, clothing_pull 32, sex_corner 32
# dim()
summarise_all(sum, na.rm = TRUE) %>%
	gather(key = "harassment_type_gender", value = "number_hh_harassed") %>%
	mutate(
		fuel_type_gender = 
			paste(
				str_extract(harassment_type_gender, pattern = "^[a-z]+_[a-z]+"),
				str_extract(str_extract(harassment_type_gender, pattern = "[a-z]{1}_yn$"), pattern = "^[a-z]{1}"),
				sep = "_"),
		fuel_type = str_extract(harassment_type_gender, pattern = "^[a-z]+_[a-z]+"),
		gender = str_extract(str_extract(harassment_type_gender, pattern = "[a-z]{1}_yn$"), pattern = "^[a-z]{1}"),
		harassment_type = 
			rep(c(
				"insulted", "belittled", "scared", 
				"pushed", "hit", "kicked", "choked", "faced a weapon", 
				"subject to sexual language",  "brushed by sexually", "subject to sexual rumors", 
				"clothing pulled", "cornered in a sexual way"
			), 4 * 8), # 4 gender/age groups and 8 fuel types
		# 419 rows - why?
	) %>%
	left_join(fuel_collection_who_alt_order_summary, by = "fuel_type_gender") %>%
	mutate(
		pc_harassed = number_hh_harassed / number_hh_collecting_fuel
	) %>%
	select(fuel_type, gender, harassment_type, number_hh_harassed, number_hh_collecting_fuel, pc_harassed)

# harassment_prev %>%
# 	kable(digits = 2) %>%
# 	kable_styling(
# 		bootstrap_options = c("striped", "hover", "condensed"),
# 		fixed_thead = TRUE
# 	)

harassment_prev %>%
	filter(str_detect(fuel_type, pattern = 'gather_scrap|collect_wood|receive_lpg')) %>% # Can't have a " " around "|"
	mutate(
		harassment_type =
			ordered(
				harassment_type,
				levels = 
					c(
						"insulted", "belittled", "scared", 
						"pushed", "hit", "kicked", "choked", "faced a weapon", 
						"subject to sexual language",  "brushed by sexually", "subject to sexual rumors", 
						"clothing pulled", "cornered in a sexual way"
					),
				labels = 
					c(
						"insulted", "belittled", "scared", 
						"pushed", "hit/kicked", "hit/kicked", "choked/ \nfaced a \nweapon", "choked/ \nfaced a \nweapon", 
						"subject to \nsexual \nlanguage/ \nrumors", "brushed by \nsexually /\nclothing \npulled", "subject to \nsexual \nlanguage/ \nrumors", 
						"brushed by \nsexually /\nclothing \npulled", "cornered in a \nsexual way"
					)
			),
		harassment_category =
			ordered(
				harassment_type,
				levels =
					c(
						"insulted", "belittled", "scared", 
						"pushed", "hit/kicked", "hit/kicked", "choked/ \nfaced a \nweapon", "choked/ \nfaced a \nweapon", 
						"subject to \nsexual \nlanguage/ \nrumors", "brushed by \nsexually /\nclothing \npulled", "subject to \nsexual \nlanguage/ \nrumors", 
						"brushed by \nsexually /\nclothing \npulled", "cornered in a \nsexual way"
					),
				labels = 
					c(
						"verbal (insulted, belittled, scared)", "verbal (insulted, belittled, scared)", "verbal (insulted, belittled, scared)", 
						"physical (pushed, hit, kicked, choked, faced a \nweapon)", "physical (pushed, hit, kicked, choked, faced a \nweapon)",
						"physical (pushed, hit, kicked, choked, faced a \nweapon)", "physical (pushed, hit, kicked, choked, faced a \nweapon)",
						"physical (pushed, hit, kicked, choked, faced a \nweapon)",
						"sexual (language, rumors, brush past, clothing pulled, cornered)", "sexual (language, rumors, brush past, clothing pulled, cornered)", 
						"sexual (language, rumors, brush past, clothing pulled, cornered)", 
						"sexual (language, rumors, brush past, clothing pulled, cornered)", "sexual (language, rumors, brush past, clothing pulled, cornered)"
					)
			),
		fuel_type =
			ordered(
				fuel_type,
				levels = c("gather_scraps", "collect_wood", "receive_lpg"),
				labels = c("Gather scraps", "Collect wood", "Receive LPG")
			),
		gender = 
			ordered(
				gender,
				levels = c("w", "m", "g", "b"),
				labels = c("Women", "Men", "Girls", "Boys")
			)
	) %>%
	group_by(harassment_category) %>%
	ggplot(aes(x = harassment_type, y = pc_harassed, fill = gender)) + # , group = harassment_category
	geom_col(position = "dodge") +
	# ggpubr::stat_compare_means(
	# 	label = "p.signif", #"p.signif" # symnum.args <- list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), symbols = c("****", "***", "**", "*", "ns"))
	# 	method = "t.test",
	# 
	# 	# label.y = 18,
	# 	hide.ns = TRUE#,
	# 	# ref.group = ".all."
	# 	# show.legend = TRUE # doesn't show the legend of stas?
	# ) +
	viridis::scale_fill_viridis(
		discrete = TRUE,
		end = 7/8,
		name = "Demographic"
	) +
	scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + # Percentage labels rounded to the nearest integer
	theme_classic() +
	theme(
		plot.title = element_text(hjust = 0.5),
		plot.subtitle = element_text(hjust = 0.5),
		# axis.text.x = element_text(angle = 60, hjust = 1),
		strip.background = element_blank(),
		strip.text.x = element_blank()
	) + 
	labs(
		title = "Harassment experienced while collecting fuel",
		subtitle = "Gathering scraps                              Collecting firewood                               Receiving LPG",
		x = "Type of harassment", 
		y = "Percentage of individuals who experienced harassment \nwhile collecting fuel"
	) +
	coord_cartesian(expand = F, clip = "off") +
	facet_wrap(harassment_category ~ fuel_type, ncol = 3, scales = "free_x") # facet_grid doesn't work - puts all the harassment types on the bottom, not sure why; facet_grid can use a space agrument, but facet_wrap cannot; space = "free". Facet_wrap can use ,   strip.position = "right"

ggsave(
	here::here("docs", "sexual_harassment.png"),
	plot = last_plot(),
	scale = 1,
	height = 6,
	width = 10,
	units = "in",
	device = "png"
)
```

## Harassment frequency, by gender
13 Harassment types:
c("insult_hh", "belittle_hh", "scare_hh", "push_hh", "hit_hh", "kick_hh", "choke_hh", "weapon_hh", "sex_lang_hh", "sex_contact_hh", "sex_rumor_hh", "clothing_pull_hh", "sex_corner_hh")

The frequency was selected from frequency_times:
0	Never
1	Once
2	Twice
3	Three times
4	More than three times

```{r}
# # How many hh reported more than 3 or more times for any group?
# survey_data %>%
#   select(harassment_vars_by_group) %>%
#   table()

# sum(survey_data[, harassment_vars_by_group] == 4, na.rm = TRUE)
```

There are 19 cells in which they report experiencing the event more than 3 times
# Why did we do frequency_times instead of just asking for an integer?!



```{r harassment_tab14}
# ## Vector of variables to summarize
# table14Vars <- harassment_vars_by_group_yn
# 
# ## Vector of categorical variables that need transformation
# table14FactorVars <- table14Vars
# 
# # Create a TableOne object
# tab14 <- 
# 	CreateTableOne(
# 		data = survey_data, 
# 		vars = table14Vars, 
# 		factorVars = table14FactorVars #, 
# 		# strata = "study_arm"
# 	)
# 
# tab14
# 
# # saveRDS(tab14, "harassment_overview.rds")
# 
# harassment_freq_by_group <- 
# 	survey_data %>%
# 	summarise_at(harassment_vars_by_group, mean, na.rm = TRUE) %>%
# 	matrix(ncol = 7 * 4, byrow = TRUE) %>%
# 	magrittr::set_colnames(
# 		c(
# 			"collect wood_m", "collect wood_w", "collect wood_b", "collect wood_g",
# 			"receive wood_m", "receive wood_w", "receive wood_b", "receive wood_g",
# 			"buy wood_m", "buy wood_w", "buy wood_b", "buy wood_g",
# 			"receive LPG_m", "receive LPG_w", "receive LPG_b", "receive LPG_g",
# 			"buy LPG_m", "buy LPG_w", "buy LPG_b", "buy LPG_g",
# 			"receive CRH_m", "receive CRH_w", "receive CRH_b", "receive CRH_g",
# 			"buy CRH_m", "buy CRH_w", "buy CRH_b", "buy CRH_g"
# 		)
# 	) %>%
# 	as.data.frame() %>%
# 	mutate_all(list(as.numeric)) %>%
# 	mutate(harassment_type = c("insult", "belittle", "scare", "push", "hit", "kick", "choke", "weapon", "use sexual language", "sexual contact", "spread sexual rumors", "pull clothing in a sexual way", "corner in a sexual way")) %>%
# 	select(harassment_type, everything())
# 
# harassment_freq_by_group %>%
# 	kable(digits = 2) %>%
# 	kable_styling(
# 		bootstrap_options = c("striped", "hover", "condensed"), 
# 		fixed_thead = TRUE
# 	)
```



```{r harassment_IDI_selection}
## Vector of variables to summarize

harassment_physical_sexual_vars <-
	survey_data %>%
	select(ends_with("_w"), ends_with("_m"), ends_with("_g"), ends_with("_b")) %>%
	select(
		-c(
			cook_who_w, gather_scraps_w, collect_wood_w, buy_wood_w, receive_wood_w, receive_lpg_w, buy_lpg_w, receive_crh_w, buy_crh_w,
			cook_who_m, gather_scraps_m, collect_wood_m, buy_wood_m, receive_wood_m, receive_lpg_m, buy_lpg_m, receive_crh_m, buy_crh_m,
			cook_who_g, gather_scraps_g, collect_wood_g, buy_wood_g, receive_wood_g, receive_lpg_g, buy_lpg_g, receive_crh_g, buy_crh_g,
			cook_who_b, gather_scraps_b, collect_wood_b, buy_wood_b, receive_wood_b, receive_lpg_b, buy_lpg_b, receive_crh_b, buy_crh_b
		)
	) %>%
	names()

harassment_physical_sexual <- 
	survey_data %>%
	filter(consent == "OK") %>%
	select(hh_id, ends_with("_w"), ends_with("_m"), ends_with("_g"), ends_with("_b")) %>%
	select(
		-c(
			cook_who_w, gather_scraps_w, collect_wood_w, buy_wood_w, receive_wood_w, receive_lpg_w, buy_lpg_w, receive_crh_w, buy_crh_w,
			cook_who_m, gather_scraps_m, collect_wood_m, buy_wood_m, receive_wood_m, receive_lpg_m, buy_lpg_m, receive_crh_m, buy_crh_m,
			cook_who_g, gather_scraps_g, collect_wood_g, buy_wood_g, receive_wood_g, receive_lpg_g, buy_lpg_g, receive_crh_g, buy_crh_g,
			cook_who_b, gather_scraps_b, collect_wood_b, buy_wood_b, receive_wood_b, receive_lpg_b, buy_lpg_b, receive_crh_b, buy_crh_b
		)
	) %>%
	# replace all instances of "Never" with NA
	# Turned everything back into integers without labels
	naniar::replace_with_na_at(.vars = harassment_physical_sexual_vars, condition = ~.x == "Never") %>% # Replace "Never" (which was entered if a hh reported X happened but it didn't happen to the particular group w, m, g, b) with NA
	# when I use replace_with_na_all it influences the hh_id column and screws it up.
	select(-c(contains("insult"), contains("belittle"), contains("scare"), contains("push"))) %>%
	filter_at(vars(-hh_id), any_vars(!is.na(.))) %>%
	janitor::remove_empty(which = "cols")

# 14 women report being hit or worse  or sexual anything
harassment_physical_sexual_w <-
	harassment_physical_sexual %>%
	select(hh_id, ends_with("_w")) %>%
	filter_at(vars(-hh_id), any_vars(!is.na(.))) %>%
	janitor::remove_empty(which = "cols")



# 110 respondent reported men have been hit or worse or experience anything sexual
harassment_physical_sexual_m <-
	harassment_physical_sexual %>%
	select(hh_id, ends_with("_m")) %>%
	filter_at(vars(-hh_id), any_vars(!is.na(.))) %>%
	janitor::remove_empty(which = "cols")

# 2 respondent reported adolesent girls have been hit or worse or experience anything sexual
harassment_physical_sexual_g <-
	harassment_physical_sexual %>%
	select(hh_id, ends_with("_g")) %>%
	filter_at(vars(-hh_id), any_vars(!is.na(.))) %>%
	janitor::remove_empty(which = "cols")

# 21 respondent reported adolescent boys have been hit or worse or experience anything sexual
harassment_physical_sexual_b <-
	harassment_physical_sexual %>%
	select(hh_id, ends_with("_b")) %>%
	filter_at(vars(-hh_id), any_vars(!is.na(.))) %>%
	janitor::remove_empty(which = "cols")

# tidyr::replace_na(): Missing values turns into a value (NA –> -99)
# naniar::replace_with_na(): Value becomes a missing value (-99 –> NA)

harassment_physical_sexual_g_list <-
	harassment_physical_sexual_g %>%
	sample_n(size = 2)  %>%
	select(hh_id)
# There are only two girls
# 10G115604G26_3478, 10G115614G26_3517
```

## Identify more adolescent girls that faced harassment by including "push" - this only adds one girl (10D109224D11_2750) so then also add also allow for verbal abuse of "scare" -> this results in  10 girls
```{r}
harassment_physical_sexual_g_extra_list <-
	survey_data %>%
	filter(consent == "OK") %>%
	select(hh_id, ends_with("_w"), ends_with("_m"), ends_with("_g"), ends_with("_b")) %>%
	select(
		-c(
			cook_who_w, gather_scraps_w, collect_wood_w, buy_wood_w, receive_wood_w, receive_lpg_w, buy_lpg_w, receive_crh_w, buy_crh_w,
			cook_who_m, gather_scraps_m, collect_wood_m, buy_wood_m, receive_wood_m, receive_lpg_m, buy_lpg_m, receive_crh_m, buy_crh_m,
			cook_who_g, gather_scraps_g, collect_wood_g, buy_wood_g, receive_wood_g, receive_lpg_g, buy_lpg_g, receive_crh_g, buy_crh_g,
			cook_who_b, gather_scraps_b, collect_wood_b, buy_wood_b, receive_wood_b, receive_lpg_b, buy_lpg_b, receive_crh_b, buy_crh_b
		)
	) %>%
	# replace all instances of "Never" with NA
	# Turned everything back into integers without labels
	naniar::replace_with_na_at(.vars = harassment_physical_sexual_vars, condition = ~.x == "Never") %>% # Replace "Never" (which was entered if a hh reported X happened but it didn't happen to the particular group w, m, g, b) with NA
	# when I use replace_with_na_all it influences the hh_id column and screws it up.
	select(-c(contains("insult"), contains("belittle"))) %>%
	# filter(hh_id %notin% c("10D109224D11_2750", "10G115604G26_3478", "10G115614G26_3517")) %>%
	filter(hh_id %notin% (harassment_physical_sexual_g_list %>% pull(hh_id))) %>%
	filter_at(vars(-hh_id), any_vars(!is.na(.))) %>%
	janitor::remove_empty(which = "cols") %>%
	
	select(hh_id, ends_with("_g")) %>%
	filter_at(vars(-hh_id), any_vars(!is.na(.))) %>%
	janitor::remove_empty(which = "cols") %>%
	
	sample_n(size = 8)  %>%
	select(hh_id)
```

There were only three adolescent girls who's mother reported that they were hit or worse. These were hh  10G115604G26_3478, 10G115614G26_3517. This girl was reported to be pushed 10D109224D11_2750. The two of seven ramdonly selected girls reported being scared are 8wB122150_1733, 3G186539Dd8_1975

```{r}

harassment_physical_sexual_b_list <-
	harassment_physical_sexual_b %>%
	filter(hh_id %notin% (harassment_physical_sexual_g_list %>% pull(hh_id))) %>%
	filter(hh_id %notin% (harassment_physical_sexual_g_extra_list %>% pull(hh_id))) %>%
	sample_n(size = 10) %>%
	select(hh_id)
# 3E185415DD22_1424, 8wBI15102369_1104, 10G115604G26_3478, 9G123670G29_6347, 10D109334D11_2814


harassment_physical_sexual_w_list <-
	harassment_physical_sexual_w %>%
	filter(hh_id %notin% (harassment_physical_sexual_g_list %>% pull(hh_id))) %>%
	filter(hh_id %notin% (harassment_physical_sexual_g_extra_list %>% pull(hh_id))) %>%
	filter(hh_id %notin% (harassment_physical_sexual_b_list %>% pull(hh_id))) %>%
	sample_n(size = 10) %>%
	select(hh_id)
#hh: 8wA117722A19_2130, 8wA115397_1528, 8wDI21101459, 8wBA20117719_, 9G600019G1_5663

harassment_physical_sexual_m_list <-
	harassment_physical_sexual_m %>%
	filter(hh_id %notin% (harassment_physical_sexual_g_list %>% pull(hh_id))) %>%
	filter(hh_id %notin% (harassment_physical_sexual_g_extra_list %>% pull(hh_id))) %>%
	filter(hh_id %notin% (harassment_physical_sexual_b_list %>% pull(hh_id))) %>%
	filter(hh_id %notin% (harassment_physical_sexual_w_list %>% pull(hh_id))) %>%
	sample_n(size = 10) %>%
	select(hh_id)
# 8wB102745i14_2610, 10G110695G26_3480, 8wA117770A30_, 8wB115467A16_2421, 10D109334D11_2814
```


```{r}
harassment_physical_sexual_list <-
	bind_rows(
		harassment_physical_sexual_w_list,
		harassment_physical_sexual_m_list,
		harassment_physical_sexual_g_list,
		harassment_physical_sexual_g_extra_list,
		harassment_physical_sexual_b_list
	) %>%
	pull(hh_id)

harassment_physical_sexual_list_hh_detail <-
	survey_data %>%
	filter(hh_id %in% harassment_physical_sexual_list) %>%
	mutate(
		hh_id = 
			factor(hh_id, levels = harassment_physical_sexual_list)
	) %>%
	select(SubmissionDate, hh_id, camp_id, block_id, subblock_id, name_respondent, name_hh_head, name_mahji, fcn_id, hh_id, target_child_name) %>%
	arrange(hh_id) %>%
	mutate(
		target_respondent = c(rep("woman", 10), rep("man", 10), rep("girl", 10), rep("boy", 10))
	) %>%
	select(SubmissionDate,target_respondent, hh_id, everything())

write.csv(harassment_physical_sexual_list_hh_detail, "C:/Users/lenovo/Google Drive (lakwong@stanford.edu)/Rohingya/Rohingya research - Fuel/HH selection/harassment_physical_sexual_list_hh_detail.csv")

```

