---
title: "Rohingya Endline Data Cleaning" 
author: "Laura Kwong"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
`%notin%` =  Negate(`%in%`)
```

```{r message=FALSE, warning=FALSE}
# Libraries
library(tidyverse)
library(readxl)
library(lubridate)
library(hms)

# Parameters

# List input files and read them

# v86, v89, v90, v91, v92, v93, v94

data_today <- read_csv(here::here("data-raw/rohingya_fuel_v94_endline_Rohingya.csv")) # 7 Oct 2020 and onwards

# list of all enrolled hh

# Rohingya_hh_data_post_intervention <- read_xlsx(Rohingya_hh_data_path, sheet = "post-intervention")
# Rohingya_hh_data_intervention_follow_up <- read_xlsx(Rohingya_hh_data_path, sheet = "intervention follow-up")
# Rohingya_hh_data <- bind_rows(Rohingya_hh_data_post_intervention, Rohingya_hh_data_intervention_follow_up) %>% mutate(fcn_id = as.numeric(fcn_id))
Rohingya_hh_data <- read_xlsx(here::here("data/RohingyaFuelMaster_hh_data.xlsx")) # list of all hh
Rohingya_hh_data_host <- read_xlsx(here::here("data/RohingyaFuelMaster_hh_data_host.xlsx")) # list of all host hh


# Output files
# Rohingya_hh_survey_master_v86 <- here::here("data/RohingyaFuelMaster_hh_survey_master_v86_data.rds")
# Rohingya_hh_survey_master_v89 <- here::here("data/RohingyaFuelMaster_hh_survey_master_v89_data.rds")
# Rohingya_hh_survey_master_v90 <- here::here("data/RohingyaFuelMaster_hh_survey_master_v90_data.rds")
# Rohingya_hh_survey_master_v91 <- here::here("data/RohingyaFuelMaster_hh_survey_master_v91_data.rds")

Rohingya_hh_survey_master <- read_csv(here::here("data/RohingyaFuelMaster_hh_survey_master_data.rds"))
Rohingya_hh_survey_master_deidentified <- read_csv(here::here("data/RohingyaFuelMaster_hh_survey_master_deidentified_data.rds"))

Rohingya_individual_survey_master <- read_csv(here::here("data/RohingyaFuelMaster_individual_survey_master_data.rds"))

data_review <- read_xlsx(here::here("Data_review_revisions/Rohingya fuel data review and revisions_endline.xlsx"))  %>% arrange(desc(start_date), enumerator_name, fcn_id)
```


# Combine data into a master file




Data review steps

0. Bithe downloads all data from ODK and puts file in raw data folder with name rohingya_fuel_rawdata_today.csv

1. Load master file

2. Run changes that were determine on previous days of review

3. Run error-checking/outlier code

4. Create dataframe with all errors. Select errors for only today. Append these onto the top of the existing review and feedback xls  (rowbind then sort by date desc()). 

5. After Bithe sends responses, add changes to code that is run in step 2. 




## View data

```{r}
# View(data_today %>% select(enumerator, fcn_id, everything()))
# View(Rohingya_hh_data)
```

## Clean prior days

```{r survey_data}

survey_data <-
	data_today %>%
	select(
		-starts_with("generated_note"),
		-starts_with("reserved_name")
	) %>%
	# mutate(master_row = X) %>%
	mutate(
		enumerator = as.factor(enumerator),
		enumerator_name =
			recode_factor(
				enumerator,
				"1" = "Tunajjina Alam",
				"2"	= "Rayhanul Jannat",
				"3"	= "Shamima Akter",
				"4" =	"Morsida Akter",
				"5" =	"Way May Marma",
				"6" = "Morselina Akter",
				"7"	= "Farhana Suma",
				"8" =	"Nishat Farjana",
				"9" =	"Arefa Khanam",
				"10" =	"Daliya Akter",
				"11" =	"Md. Jamilur Rahman",
				"12" =	"Md. Razu Ahmed",
				"13" = "Mohammad Alamgir",
				"14" =	"Nazrin Akter",
				"15" = "dummy",
				"16" = "Fatema Akter",
				"17" = "Tanij Akter"
			)
	) %>%
	
	# mutate(start_date = dmy(as.character(start_date))) %>%
	# mutate(
	#   SubmissionDate = parse_date_time(as.character(SubmissionDate), orders = "mdy HMS", tz = "Asia/Dhaka"),
	#   starttime = parse_date_time(as.character(starttime), orders = "mdy HMS", tz = "Asia/Dhaka"),
	#   endtime = parse_date_time(as.character(endtime), orders = "mdy HMS", tz = "Asia/Dhaka"),
	#   start_date = mdy(as.character(start_date)) # Not working for most values, not sure why
	# ) %>%
	select(-enumerator) %>%  
	mutate_at(
		vars(
			fcn_id,
			income_cash_ngo, income_abroad, income_farming, income_own_business, 
			income_wage_labor, income_skill_labor, income_handicrafts_tailoring, 
			income_humanitarian_asst, income_selling_wood,     
			life_failure, fearful, restless_sleep, less_talkative, lonely, 
			unfriendly_people, crying_spells, sick, feeling_disliked, 
			cant_get_going, suicidal_thoughts_30
		), 
		funs(as.numeric)
	) %>% 
	ungroup() %>%
	select(SubmissionDate, starttime, endtime, deviceid, start_date, enumerator_name, everything())
```

```{r}
# saveRDS(survey_data, Rohingya_hh_survey_master_v86_path)
# saveRDS(survey_data, Rohingya_hh_survey_master_v89_path)
# saveRDS(survey_data, Rohingya_hh_survey_master_v90_path)
# saveRDS(survey_data, Rohingya_hh_survey_master_v91_path)



saveRDS(survey_data, Rohingya_hh_survey_master_path)


survey_data_deidentified <-
	survey_data %>%
	select(-contains("name"), -c(camp_id, block_id, subblock_id, upazila_id, union_id, ward_id, village_id, hh_id, hh_id_host, UNHCR_id))


# survey_data %>%
# 	select(contains("_id")) %>%
# 	names()

saveRDS(survey_data_deidentified, Rohingya_hh_survey_master_deidentified_path)
```

```{r individual_survey_data}
# survey_data$`SET-OF-survey-hh_demographics-hh_members` # uuid:d0973c86-21b3-4d48-b770-a0efe0ba4309/hh_members
# survey_data$`SET-OF-survey-health-symptoms` # uuid:d0973c86-21b3-4d48-b770-a0efe0ba4309/symptoms
# survey_data$`SET-OF-survey-location` # uuid:d0973c86-21b3-4d48-b770-a0efe0ba4309/location

# data_today_hh # PARENT_KEY + "hh_members"
# data_today_symptoms # PARENT_KEY + "symptoms"
# data_today_location # PARENT_KEY + "location"

individual_data <-
	data_today %>%
	mutate(
		enumerator = as.factor(enumerator),
		enumerator_name =
			recode_factor(
				enumerator,
				"1" = "Tunajjina Alam",
				"2"	= "Rayhanul Jannat",
				"3"	= "Shamima Akter",
				"4" =	"Morsida Akter",
				"5" =	"Way May Marma",
				"6" = "Morselina Akter",
				"7"	= "Farhana Suma",
				"8" =	"Nishat Farjana",
				"9" =	"Arefa Khanam",
				"10" =	"Daliya Akter",
				"11" =	"Md. Jamilur Rahman",
				"12" =	"Md. Razu Ahmed",
				"13" = "Mohammad Alamgir",
				"14" =	"Nazrin Akter",
				"15" = "dummy",
				"16" = "Fatema Akter",
				"17" = "Tanij Akter"
			)
	) %>%
	mutate(
		`SET-OF-survey-hh_demographics-hh_members_short` = str_extract(`SET-OF-survey-hh_demographics-hh_members`, "^[^/]+"),
		`SET-OF-survey-health-symptoms_short` = str_extract(`SET-OF-survey-health-symptoms`, "^[^/]+"),
		`SET-OF-survey-location_short` = str_extract(`SET-OF-survey-location`, "^[^/]+")
	) %>%
	select(start_date, enumerator_name, fcn_id, `SET-OF-survey-hh_demographics-hh_members_short`, `SET-OF-survey-health-symptoms_short`, `SET-OF-survey-location_short`) %>% 
	left_join(
		data_today_hh %>%	rename("KEY_hh_member" = "KEY"), by = c(`SET-OF-survey-hh_demographics-hh_members_short` = "PARENT_KEY")
	) %>%
	left_join(
		data_today_symptoms %>% rename("KEY_symptoms" = "KEY"), by = c(`SET-OF-survey-health-symptoms_short` = "PARENT_KEY", "name" = "name_roster")
	) %>% 
	left_join(
		data_today_location %>% rename("KEY_location" = "KEY"), by = c(`SET-OF-survey-location_short` = "PARENT_KEY", "name" = "location_name_roster")
	) %>%
	select(start_date, enumerator_name, fcn_id, name, hhh_relation, dob, age_yrs, sex, pregnant, disability, edu_yrs, edu_camp_yrs, edu_informal_yrs, symptoms_7, hours_outside, location_outside_house_1, everything())
```

```{r}
View(individual_data)

individual_data %>%
	filter(`symptoms_7/11` == 1)


saveRDS(individual_data, Rohingya_individual_survey_master_path)

# Only 5 records show up, all from 7 Oct....why?
```




############ PROBLEMS #######################

fuel_ever_receive_lpg == 0 but should have been ==  1 for 
101239
101762
274944
122567
101574
101723

--> these hh need to be redone




## Error checking

Discussions amongst the team came up with many possible inconsistancies that the following code flags and reports. 
The resulting records should show up in the survey_data_questions excel sheet. 

```{r flag_errors, echo=FALSE}
survey_errors <- 
	survey_data %>%
	separate(
		starttime,
		into  = c("date_start", "time_start"),
		sep = ' '
	) %>%
	separate(
		endtime,
		into  = c("date_end", "time_end"),
		sep = ' '
	) %>%
	mutate(
		# hh_id = fcn_id,
		# hh_id.error = ifelse(length(hh_id) < 8, NA_character_, "hh_id wrong"), # <8 or <15
		# start_date = ymd(start_date), # This isn't working
		
		# use https://cran.r-project.org/web/packages/lubridate/vignettes/lubridate.html
		# tz just labels the tz, doesn't actually change the time zone,
		# to change the time zone you need to use "with_tz"
		# https://en.wikipedia.org/wiki/List_of_tz_database_time_zones
		# apparently this method didn't work for Chris so he used as_hms()
		# time_start = mdy_hm(starttime),
		# time_end = mdy_hm(endtime),
		# time_start = as.hms(time_start, tz = "Asia/Dhaka"),
		# time_end = as.hms(time_end, tz = "Asia/Dhaka"),
		
		
		# should be able to auto-determine survey length
		#  time_start_hms = as.hms(time_start),
		# time_end_hms = as.hms(time_end),
		# min_to_complete = round(difftime(time_end_hms, time_start_hms, units = "min"), 0),
		# survey_short = ifelse(min_to_complete < 30, "Why so short?", 0), 
		# survey_long = ifelse(min_to_complete > 70, "Why so long?", 0),
		
		
		hh_id.error = ifelse(is.na(hh_id) | length(hh_id) < 10, "What is the hh_id?", NA_character_),
		camp_id.error = ifelse(is.na(camp_id), "What is the camp_id?", NA_character_),
		block_id.error = ifelse(is.na(block_id), "What is the block_id?", NA_character_),
		subblock_id.error = ifelse(is.na(subblock_id), "What is the subblock_id?", NA_character_),
		fcn_id.error = ifelse(is.na(fcn_id), "What is the fcn_id?", NA_character_),
		# Rand_nu.error = ifelse(is.na(Rand_nu), "What is the camp_id?", NA_character_),
		
		hh_size.error_high = ifelse(hh_size >9, "hh_size really >9?", NA_character_),
		
		# total_income_30.error_low = ifelse(total_income < 1000, "Income very low?", NA_character_),
		total_income_30.error_low = NA_character_,
		# total_income_30.error_high = ifelse(total_income > 10000, "Income high?", NA_character_),
		# total_income_30.error_high = NA_character_,
		income_cash_ngo.error_high = ifelse(income_cash_ngo > 8000, "NGO income >8000?", NA_character_),
		income_own_business.error_high = ifelse(income_own_business > 8000, "Business income >8000?", NA_character_),
		income_wage_labor.error_high = ifelse(income_wage_labor > 5000, "Wage labor income >5000?", NA_character_),
		income_humanitarian_asst.error_high = ifelse(income_humanitarian_asst > 3000, "Sold aid for >3000?", NA_character_),
		clothing.error = ifelse(clothing > 6000, "Spent >6000 on clothing?", NA_character_),
		shelter.error = ifelse(shelter > 5000, "Spent >5000 on shelter?", NA_character_),
		debt.error = ifelse(debt >5000, "Debt really >5000?", NA_character_),
		
		# spent_total_month.error_high = ifelse(spent_total_month > 8000, "expenses above 8000?", NA_character_),
		total_expenditures_30.error_high = NA_character_,
		# spent_total_month.error_expenses = ifelse(spent_total_month > (total_income + 3000) , "spent more than made?", NA_character_),
		# total_expenditures_30.error_expenses = NA_character_,
		
		# floor_material.error = ifelse(floor_material == 6, "Was the floor really cement?", NA_character_), # Team always response that "floor_mater ==  6" (cement) is correctly entered so will stop checking for this error as of 17 Oct. 
		roof_material.error = ifelse(roof_material == 4, "Roof is mud?", NA_character_),
		floor_material.other = ifelse(floor_material == 66, "What was the other material used for the floor?", NA_character_),
		roof_material.other = ifelse(roof_material == 66, "What was the other material used for the roof?", NA_character_),
		wall_material.other = ifelse(wall_material == 66, "What was the other material used for the walls?", NA_character_),
		
		rice_adults_week.error = ifelse(rice_adults_week != 7, "Did not eat rice 7 days/week?", NA_character_), 
		bread_adults_week.high_error = ifelse(bread_adults_week > 2, "Bread consumed >2 time?", NA_character_),
		potatoes_adults_week.high_error = ifelse(potatoes_adults_week >5, "Ate potatoes >5 days/week?", NA_character_),
		fish_adults_week.high_error = ifelse(fish_adults_week == 7, "Ate fish every day?", NA_character_),
		# food_wrong_meat = ifelse((goat_sheep_adults_week | beef_adults_week | poultry_adults_week) > 3, "Ate lots of meat?", 0),
		food_source.other = ifelse(food_source == 66, "What was the other food source?", NA_character_),
		
		food_cant_afford_action.other = ifelse(food_cant_afford_action == 66, "What other thing did they do when they couldn't afford food?", NA_character_),
		fuel_cant_afford_action.other = ifelse(fuel_cant_afford_action == 66, "What other thing did they do when they couldn't afford fuel?", NA_character_),
		
		traditional_use_yesterday.error = ifelse(traditional_use_yesterday > 4, "Used traditional stove >4 times/day?", NA_character_),
		boil_yesterday_times.error = ifelse(boil_yesterday_times > traditional_use_yesterday + LPG_use_yesterday, "Boiled more than used stove?", NA_character_),
		forest_wood_fee.error = ifelse(forest_wood_fee > 50, "Forest fee >50?", NA_character_),
		
		flooring_below_stove.error = ifelse(flooring_below_stove == 66, "What was the flooring below the stove?", NA_character_),
		lpg_repair_costs.high_error = ifelse(lpg_repair_costs > 1000, "LPG repair cost >1000?", NA_character_),
		lpg_afraid.other = ifelse(lpg_afraid == 66, "Why were they afraid of LPG?", NA_character_),
		lpg_stove_repair.other = ifelse(lpg_stove_repair == 66, "What was the other part of the LPG stove that needed repair?", NA_character_),
		lpg_cylinder_repair.other = ifelse(lpg_cylinder_repair == 66, "What was the other part of the LPG stove that needed repair?", NA_character_),
		
		
		receive_lpg_walk.error_high = ifelse(receive_lpg_walk > 2, "Time to walk to LPG distribution center >2 hr?", NA_character_),
		receive_lpg_wait.error_high = ifelse(receive_lpg_wait > 6, "Waiting at LPG center >6 hr?", NA_character_),
		
		fuel_ever_receive_lpg.error = ifelse(fuel_ever_receive_lpg == 0, "The hh didn't receive LPG ever?", NA_character_),
		fuel_30_receive_lpg.error = ifelse(fuel_30_receive_lpg == 0, "The hh didn't receive LPG in past 30 days?", NA_character_),
		
		medical.high = ifelse(medical > 5000, "Were the medical expenditures >5000?", NA_character_),
		# medical.error = ifelse(medical == debt, "What was the medical expenditure?", NA_character_), # only for v91 and v92 which accidentally had the question for medical expenditures as "debt"
		
		time_cooking.error = ifelse(time_cooking != 3 & fuel_30_receive_lpg == 1, "Respondent did not report spending less time cooking even though using LPG?", NA_character_),
		time_harvesting_wood.error = ifelse(time_harvesting_wood != 3 & fuel_30_receive_lpg == 1, "Respondent did not report spending less time harvesting wood even though using LPG?", NA_character_),    
		
		drudgery_most_diff.error = ifelse(drudgery_most_diff == drudgery_easiest & drudgery_easiest != 88, "Same activity most and least difficult?", NA_character_),
		drudgery_easiest.error = ifelse(drudgery_second_most_diff == drudgery_easiest & drudgery_easiest != 88, "Same activity second most and least difficult?", NA_character_),
		drudgery_second_most_diff.error = ifelse(drudgery_most_diff == drudgery_second_most_diff & drudgery_most_diff != 88, "Same activity most and second most difficult?", NA_character_),
		
		livlihood_training.other = ifelse(livlihood_training == 66, "What was the other livelihood training?", NA_character_),
		
		
		happy.error = 
			ifelse(
				#unexpected set of feelings q are all 0 -> prior to 190930 this question was too restrictive (expected ALL would be 0 to see a problem)
				(happy == 0 |
				 	enjoyed_life == 0) &
					(life_failure == 0 |
					 	crying_spells == 0), 
				"Is it correct that respondent not happy but not cry?", 
				NA_character_
			), 
		crying_spells.error = 
			ifelse(
				#unexpected set of feelings q all 7-> prior to 190930 this question was too restrictive (expected ALL would be 7 to see a problem)
				(happy == 7 |
				 	enjoyed_life == 7) &
					(life_failure == 7 |
					 	crying_spells == 7),
				"Is it correct that respondent happy but said cry every day ?", 
				NA_character_
			),
		life_failure.error = 
			ifelse(
				#Feelings all 7
				(happy == 7 | enjoyed_life == 7) & 
					(life_failure == 7 | fearful == 7 |
					 	crying_spells == 7 | suicidal_thoughts_30 == 7),
				"Is it correc that respondent report mixed thoughts of happy and failure?", 
				NA_character_
			),
		
		suicidal_thoughts_30.followup = ifelse(suicidal_thoughts_30 == 1, "Were mental health resources provided?", NA_character_)
		
	) %>%
	select(
		fcn_id, 
		hh_id.error, camp_id.error, block_id.error, subblock_id.error, fcn_id.error, 
		hh_size.error_high, 
		# hh_id, hh_id.error, 
		total_income_30.error_low, 
		income_cash_ngo.error_high, income_own_business.error_high, income_wage_labor.error_high, income_humanitarian_asst.error_high,
		clothing.error, shelter.error, debt.error, 
		total_expenditures_30.error_high,
		# floor_material.error, 
		roof_material.error, 
		floor_material.other, roof_material.other, wall_material.other, 
		rice_adults_week.error, bread_adults_week.high_error, potatoes_adults_week.high_error, fish_adults_week.high_error,
		food_cant_afford_action.other, fuel_cant_afford_action.other, 
		traditional_use_yesterday.error, boil_yesterday_times.error, forest_wood_fee.error,
		flooring_below_stove.error, lpg_repair_costs.high_error,
		lpg_stove_repair.other, lpg_cylinder_repair.other, 
		receive_lpg_walk.error_high, receive_lpg_wait.error_high, 
		fuel_ever_receive_lpg.error, fuel_30_receive_lpg.error, 
		medical.high, # medical.error,
		time_cooking.error, time_harvesting_wood.error,
		drudgery_most_diff.error, drudgery_easiest.error, drudgery_second_most_diff.error, 
		livlihood_training.other,
		happy.error, crying_spells.error, life_failure.error,
		suicidal_thoughts_30.followup
	) %>% 
	
	gather(-fcn_id, key = "error_var", value = "issue") %>% # 
	# filter(!is.na(issue)) %>%
	left_join(survey_data %>% select(fcn_id, enumerator_name, start_date, target_respondent_current, target_child_current), by = "fcn_id") %>%
	mutate(fcn_id_repeat = fcn_id) %>%
	select(start_date, enumerator_name, fcn_id, target_respondent_current, target_child_current, issue, fcn_id_repeat, error_var) %>% 
	
	#hh_id
	separate(col = error_var, into = c("var", "extra"), sep = "\\.", extra = "merge") %>%
	select(-extra) %>%
	arrange(desc(start_date), enumerator_name, desc(fcn_id)) %>% # desc(master_row)
	mutate(row = row_number()) 


initial_value_fun <- function(row, fcn_id, var){
	survey_data %>%
		mutate(
			total_income = NA_character_,
			spent_total_month = NA_character_
		) %>%
		filter(fcn_id == survey_errors$fcn_id[row]) %>%
		select(survey_errors$var[row]) %>%
		pull()
}

initial_vals <-
	pmap(list(survey_errors[["row"]], survey_errors[["fcn_id"]], survey_errors[["var"]]), initial_value_fun) %>% # use [[ to get a list whereas $ returns a column 
	unlist() %>%
	enframe() %>% # from tibble package, makes a tibble the the nested list
	unnest(cols = c()) %>%
	transmute(initial_value = as.character(value))

# existing_dates <- data_review %>% select(start_date) %>% distinct()

survey_errors_initial <-
	bind_cols(survey_errors %>% select(-row), initial_vals) %>%
	filter(!is.na(issue)) %>%
	# filter(start_date %in% c("Oct 1, 2020")) %>%
	# filter(start_date %notin% existing_dates) %>%
	add_column(correct_value = "", remarks = "", correction_coded = "NA", date_correction_made = "NA", notes = "")

# c("Sep 30, 2020", "Sep 29, 2020", "Sep 28, 2020", "Sep 27, 2020", "Sep 26, 2020") %notin% c("Sep 27, 2020", "Sep 26, 2020")
# c(survey_errors %>% select(start_date) %>% unique()) %in% c(data_review %>% select(start_date) %>% distinct())
# class(c(data_review %>% select(start_date) %>% distinct()))
# class(survey_errors %>% select(start_date) )

# data_review <- read_xlsx(data_review_path) %>% arrange(desc(start_date), enumerator_name, fcn_id)


data_review <-
	bind_rows(data_review, survey_errors_initial) %>% # %>% filter(start_date == "Sep 28, 2020")
	arrange(desc(remarks)) %>%
	distinct(fcn_id, var, .keep_all = TRUE) %>% # preserves first row
	arrange(desc(mdy(start_date)), enumerator_name, fcn_id)

View(data_review)

```


```{r}
openxlsx::write.xlsx(data_review, data_review_path)
```


```{r}

# data_review_path_2 <- here::here("Data_review_revisions/Rohingya fuel data review and revisions_endline_older.xlsx")
# data_review_2 <- read_xlsx(data_review_path_2)
# 
# data_review <- 
# 	data_review %>%
# 	select(-c(correct_value, remarks, correction_coded, date_correction_made)) %>%
# 	left_join(data_review_2 %>% select(fcn_id, var, correct_value, remarks, correction_coded, date_correction_made), by = c("fcn_id", "var"))

```




##########################################################################################




################################ The below is not done yet ################################


# Enumerator level issues

Check the following
1. average, min, and max survey_duration_min
2. number of surveys completed
3. all enumerators have responses but one enumerator has none - how do I do this? Must group_by(enumerator) then mutate_at(all relevant vars) and take the average (na.rm = FALSE). 




```{r}
View(survey_data)
survey_data %>% names()

survey_data %>% select(starttime, endtime, survey_duration_min, SubmissionDate, start_date)

```


```{r enumerator_performance, echo=FALSE, error=FALSE, eval=FALSE}
enumerator_performance <- 
	survey_errors %>% 
	# filter(consent != "", enumerator != 14) %>% # 14 = "Nazrin Akter"
	group_by(enumerator) %>% 
	select(
		enumerator, survey_duration_min, income
	) %>% 
	summarise_at(
		vars(
			min_to_complete, income
		), 
		funs(
			mean = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE),
			mean_na = mean(., na.rm = FALSE), sd_na = sd(., na.rm = FALSE)
		)
	) %>% 
	ungroup()

enumerator_performance

surveys_per_enumerator <-  
	survey_today %>% 
	group_by(enumerator) %>% 
	# filter(consent == "OK") %>% 
	tally() %>% 
	ungroup()

surveys_per_enumerator
```

