---
title: "RF105A: Analysis"
author: "Christopher LeBoa"
date: "2025-01-15"
output: html_document
---

# Rohingya Fuel Analysis

This file is a part of the Rohungya fuel project. Which quantifies the impact of human and environmental impacts to switching to LPG in the Rohingya refugee camps in Bangladesh.

## Load packages and datasets 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())
#install.packages("here")
#install.packages("zoo")
# install.packages("broom.mixed") Why is this failing? 
# install.packages("tableone")
# install.packages("stargazer")
# install.packages("kableExtra")
# install.packages("estimatr")
# install.packages("lme4")
# install.packages("binom")

source(here::here("0_config.R")) #Configuration file 
source(here::here("3_data_cleaning/1.5_define_vector_columns.R")) #Cleans data 
#source(here::here("5_analysis/Dif_in_dif_fxn.R")) #Conducts difference in difference analysis 
#Using dif in dif directly in this file with Lm robust now 

library(gridExtra)

# Parameters
file_in_hansen <- here::here("2_data_raw/deforestation/hansen_deforestation_21.csv")
file_survey_data_base <- here::here("4_data/RohingyaFuel_survey_data_triple.rds")
file_survey_data_all <- here::here("4_data/RohingyaFuelMaster_survey_data_tidy.rds")
#===============================================================================

# Load input files
data_hansen <- read_csv(file_in_hansen)
survey_data <- read_rds(file_survey_data_base)
model_data <- survey_data %>% filter(timepoint %in% c("baseline", "endline"))

file_stove_on_day <- here::here("4_data/RohingyaFuel_stove_on_day_250401.csv")
df_events_stove_on_per_day <- read_csv(file_stove_on_day)


```

# Household demographics and comparison to loss to follow up
## HH Table 1
This is not printed in the paper but was useful for calculating household demographic data that is described in the paper.
```{r}
rm(list = ls())
source(here::here("0_config.R")) # a config file that needs to be run to load neccesary packages 
source(here::here("3_data_cleaning/1.5_define_vector_columns.R")) # a file that defines which columns are 
## Chris
# source(here::here("1_config.R"))


# Parameters
file_survey_data_all <- here::here("4_data/RohingyaFuelMaster_survey_data_tidy.rds")
file_survey_data_base <- here::here("4_data/RohingyaFuel_survey_data_triple.rds")
file_survey_data_baseline <- here::here("4_data/RohingyaFuelMaster_survey_data_intervention_baseline.rds")


file_out_1 <- here::here("4_data/study_arm_camp_id_errors_220724.csv")
file_out_2 <- here::here("4_data/camp_block_id_errors_220724.csv")
camp_block_id_path <- here::here("4_data/camp_block_id.csv")
camp_block_sublock_id_path <- here::here("4_data/camp_block_sublock_id.csv")
camp_block_subblock_id_100_largest_path <- here::here("4_data/camp_block_subblock_id_100_largest.csv")


# Load input files

survey_data_all <- 
  read_rds(file_survey_data_all) %>%
  mutate(electricity = ifelse(electricity == 2, 1, 0)) ## Redefine the electricity variable 
survey_data <- 
  read_rds(file_survey_data_base)  %>%
  mutate(electricity = ifelse(electricity == 2, 1, 0))


survey_data_baseline <-  # select only baseline hh for table one 
  survey_data %>%
  filter(timepoint == "baseline")


survey_data %>%
  filter(timepoint == "baseline") %>%
  count(study_arm_overall)
# For each baseline, midline, endline there are 305 comparison hh and 486 intervention hh
# 791 hh with triplicate measures

survey_data_hh <-
  survey_data_all %>%
  mutate(
    study_arm_overall = 
      ordered(
        study_arm_overall,
        labels = c("comparison group", "intervention group")
      )
  ) %>%
  tabyl(timepoint, study_arm_overall)

survey_data_hh %>%
  kable(
    caption = "Number of households surveyed at each timepoint",
    booktabs = TRUE,
    digits = 1,
    align = c("l", "c", "C"),
    format = "latex"
  ) %>%
  kable_styling(latex_options = c("scale_down")) 



################################################################################
# Where are the hh located?
################################################################################
survey_data_all %>%
  tabyl(timepoint, camp_id, study_arm_overall)

survey_data %>%
  tabyl(timepoint, camp_id, study_arm_overall)

# study_arm_overall == intervention: camp_id %in% ("8w", "9", "10)
# study_arm_overall == comparison: camp_id %in% ("8E", "18", "3", "4", "5") # 3,4,5 are UNCHR; others are IOM


# There are a number of hh that appear to have the wrong study_arm assigned. 
# E.g. there are hh labeled as intervention that are in camps 3, 4, 5, 8E, which are all comparison camps

study_arm_error_all <-
  survey_data_all %>%
  mutate(
    anomolous = 
      case_when(
        timepoint == "endline" & study_arm_overall == "intervention" & camp_id == "3" ~ 1,
        timepoint == "endline" & study_arm_overall == "intervention" & camp_id == "4" ~ 1,
        timepoint == "endline" & study_arm_overall == "intervention" & camp_id == "5" ~ 1,
        timepoint == "endline" & study_arm_overall == "intervention" & camp_id == "8E" ~ 1,
        timepoint == "endline" & study_arm_overall == "comparison" & camp_id == "8W" ~ 1,
        timepoint == "endline" & study_arm_overall == "comparison" & camp_id == "9" ~ 1,
        timepoint == "endline" & study_arm_overall == "comparison" & camp_id == "10" ~ 1,
        TRUE ~ 0
      )
  ) %>%
  select(study_arm_overall, timepoint, camp_id, block_id, subblock_id, fcn_id, name_mahji, name_respondent, name_hh_head, target_child_name, anomolous) %>%
  filter(anomolous == 1) %>%
  select(-anomolous)

# write.csv(study_arm_error_all, file_out_1)

################################################################################
# Where are the hh located?
################################################################################
# Data Cleaning 

# Check for errors by examining all the data
camp_block_id_all <-
  survey_data_all %>%
  # tabyl(camp_id)
  # tabyl(camp_id, lpg_depots) # lpg_depots = "What LPG distribution center do you go to?
  tabyl(camp_id, block_id)
# unite(block_sub_block_id, c("block_id", "subblock_id")) %>%
# tabyl(camp_id, block_sub_block_id)

camp_block_id_all_errors <-
  survey_data_all %>%
  mutate(
    anomolous = 
      case_when(
        camp_id == "MOJIMULLAH" ~ 1,
        camp_id == "L18" ~ 1,
        camp_id == "G" ~ 1,
        camp_id == "10" & block_id == "e" ~ 1,
        camp_id == "4" & block_id == "b" ~ 1,
        camp_id == "8W" & block_id == "c" ~ 1,
        camp_id == "8W" & block_id == "g" ~ 1,
        camp_id == "9" & block_id == "b" ~ 1,
        camp_id == "9" & block_id == "c" ~ 1,
        camp_id == "9" & block_id == "i" ~ 1,
        camp_id == "9" & block_id == "c" ~ 1,
        TRUE ~ 0
      )
  ) %>%
  select(study_arm_overall, timepoint, camp_id, block_id, subblock_id, fcn_id, name_mahji, name_respondent, name_hh_head, target_child_name, anomolous) %>%
  filter(anomolous == 1) %>%
  select(-anomolous)



### Now only the paired data

camp_org <-
  survey_data %>%
  tabyl(timepoint, camp_id, org)

survey_data_all %>%
  tabyl(timepoint, camp_id, org)



camp_block_id <-
  survey_data %>%
  # tabyl(camp_id)
  # tabyl(camp_id, lpg_depots) # lpg_depots = "What LPG distribution center do you go to?
  tabyl(camp_id, block_id)
# unite(block_sub_block_id, c("block_id", "subblock_id")) %>%
# tabyl(camp_id, block_sub_block_id)

# write.csv(camp_block_id, camp_block_id_path)


camp_block_subblock_id <-
  survey_data %>%
  group_by(camp_id, block_id, subblock_id) %>% 
  count() %>%
  ungroup() %>%
  arrange(camp_id, block_id, subblock_id) 

camp_block_subblock_id_100_largest <-
  camp_block_subblock_id %>%
  arrange(desc(n)) %>%
  slice(1:100) %>%
  arrange(camp_id, block_id, subblock_id)



###############################################################################
# # Create dataset of households missing endline data to check for differential missingness 
###############################################################################
missing_from_endline_data  <- survey_data_all %>% filter(!hh_id %in% survey_data$hh_id)


###############################################################################
# # Create Table 1 datasets 
###############################################################################


survey_data_tab1 <-
  survey_data %>%
  filter(timepoint == "baseline") %>%
  select(
    c(
      "study_arm_overall",
      "hh_size", "hh_size_2mo_u5", "hh_size_u2mo",
      "hh_ppl_smoke",
      "electricity",
      "electric_fan_yn",
      "smartphone_yn", "mobile_phone_yn", # "radio_yn",   
      "portable_lamp_yn", "solar_lamp_yn", 
      
      "mattress_yn", "blanket_yn", "mosquito_net_yn",
      "umbrella_yn",
      "chair_bench_yn", "table_yn", # "almirah_wardrobe_show_case_yn",
      "shovel_yn", "sickle_yn", "weaving_tool_yn",
      "chicken_duck_pigeon_yn",
      "income",
      "spent_total_month",
      "debt",
      "target_child_sex",
      "target_child_months"
    )
  ) %>%
  # Convert to USD
  mutate(
    dropped_yn = "Participated in 3 surveys",
    income_USD = income / BDT_USD_exchange_rate_baseline,
    spent_total_month_USD = spent_total_month/ BDT_USD_exchange_rate_baseline,
    debt_USD = debt / BDT_USD_exchange_rate_baseline
  ) %>%
  select(-c(income, spent_total_month, debt)) %>%
  select(
    dropped_yn, study_arm_overall, target_child_sex, target_child_months,
    hh_size, hh_size_2mo_u5, hh_size_u2mo, hh_ppl_smoke,
    income_USD, spent_total_month_USD, debt_USD,
    everything()
  )



survey_data_tab1_IOM <- 
  survey_data %>%
  filter(camp_id %in% c("8E", "8W", "9", "10", "18"))	%>% 
  filter(timepoint == "baseline") %>%
  select(
    c(
      "study_arm_overall",
      "hh_size", "hh_size_2mo_u5", "hh_size_u2mo",
      "hh_ppl_smoke",
      "electricity",
      "electric_fan_yn",
      "smartphone_yn", "mobile_phone_yn", # "radio_yn",   
      "portable_lamp_yn", "solar_lamp_yn", 
      
      "mattress_yn", "blanket_yn", "mosquito_net_yn",
      "umbrella_yn",
      "chair_bench_yn", "table_yn", # "almirah_wardrobe_show_case_yn",
      "shovel_yn", "sickle_yn", "weaving_tool_yn",
      "chicken_duck_pigeon_yn",
      "income",
      "spent_total_month",
      "debt",
      "target_child_sex",
      "target_child_months"
    )
  ) %>%
  # Convert to USD
  mutate(
    dropped_yn = "Participated in 3 surveys",
    income_USD = income / BDT_USD_exchange_rate_baseline,
    spent_total_month_USD = spent_total_month/ BDT_USD_exchange_rate_baseline,
    debt_USD = debt / BDT_USD_exchange_rate_baseline
  ) %>%
  select(-c(income, spent_total_month, debt)) %>%
  select(
    dropped_yn, study_arm_overall, target_child_sex, target_child_months,
    hh_size, hh_size_2mo_u5, hh_size_u2mo, hh_ppl_smoke,
    income_USD, spent_total_month_USD, debt_USD,
    everything()
  )

## The following hh were missing from endline data collection -- we want to create separate table object to view their assets 
# and compare wealth to see if they are fundementally different than those included in study

missing_data_tab1 <-
  missing_from_endline_data %>%
  filter(timepoint == "baseline") %>%
  select(
    c(
      "study_arm_overall",
      "hh_size", "hh_size_2mo_u5", "hh_size_u2mo",
      "hh_ppl_smoke",
      "electricity",
      "electric_fan_yn",
      "smartphone_yn", "mobile_phone_yn", # "radio_yn",   
      "portable_lamp_yn", "solar_lamp_yn", 
      
      "mattress_yn", "blanket_yn", "mosquito_net_yn",
      "umbrella_yn",
      "chair_bench_yn", "table_yn", # "almirah_wardrobe_show_case_yn",
      "shovel_yn", "sickle_yn", "weaving_tool_yn",
      "chicken_duck_pigeon_yn",
      "income",
      "spent_total_month",
      "debt",
      "target_child_sex",
      "target_child_months"
    )
  ) %>%
  # Convert to USD
  mutate(
    dropped_yn = "Lost to attrition",
    income_USD = income/ BDT_USD_exchange_rate_baseline,
    spent_total_month_USD = spent_total_month/ BDT_USD_exchange_rate_baseline,
    debt_USD = debt / BDT_USD_exchange_rate_baseline
  ) %>%
  select(-c(income, spent_total_month, debt)) %>%
  select(
    dropped_yn, study_arm_overall, 
    hh_size, hh_size_2mo_u5, hh_size_u2mo, hh_ppl_smoke,
    income_USD, spent_total_month_USD, debt_USD,
    everything()
  )


###############################################################################
# # Define variables that will be used in the tables 
###############################################################################


### Define the vars for the table and specify which are factors
table1Vars <-
  c(
    "dropped_yn",
    "Study arm",
    "Target child is female", 
    "Age of target child (mo)",
    "Number of household members", 
    "Number of hh members 2-59 months",
    "Number of household members 0 to < 2 months",
    "Number of household members who smoke",
    "Monthly income [USD]",
    "Monthly expenditure [USD]",
    "Total debt [USD]",
    "House has solar electricity",
    "Has 1+ electric fan", 
    "Has 1+ smartphone", 
    "Has 1+ mobile phone",
    # "Has 1+ radio", # Note that no family had a radio so the table has radio_yn = 0
    "Has 1+ portable lamp",
    "Has 1+ solar lamp",
    "Has 1+ mattress", 
    "Has 1+ blanket",
    "Has 1+ mosquito net",
    "Has 1+ umbrella", 
    "Has 1+ chair/bench", 
    "Has 1+ table", 
    # "Has 1+ wardrobe", 
    "Has 1+ shovel", 
    "Has 1+ sickle", 
    "Has 1+ weaving tool", 
    "Has 1+ poultry"
    # "Has home garden",

  )


table1FactorVars <- 
  c(
    "House has solar electricity",
    "Has 1+ electric fan", 
    "Has 1+ smartphone", 
    "Has 1+ mobile phone",
    "Has 1+ radio",
    "Has 1+ portable lamp",
    "Has 1+ solar lamp",
    "Has 1+ mattress", 
    "Has 1+ blanket",
    "Has 1+ mosquito net",
    "Has 1+ umbrella", 
    "Has 1+ chair/bench", 
    "Has 1+ table", 
    # "Has 1+ wardrobe", # remove because only 3 total people have a wardrobe
    "Has 1+ shovel", 
    "Has 1+ sickle", 
    "Has 1+ weaving tool", 
    "Has 1+ poultry",
    "Target child is female"
  )


# Make full dataset
survey_all_tab1 <- 
  survey_data_tab1 %>% 
  bind_rows(missing_data_tab1) %>%
  mutate(dropped_yn = ordered(dropped_yn, levels = c("Participated in 3 surveys", "Lost to attrition")))

# Name datasets
names(survey_all_tab1) <- table1Vars

names(survey_data_tab1) <- table1Vars

names(survey_data_tab1_IOM) <- table1Vars

names(missing_data_tab1) <-  table1Vars

survey_all_tab1$`Monthly income [USD]`


###############################################################################
# # Create Table 1 Objects
###############################################################################


# Get average stats for all hh
tab1_baseline_no_study_arm <- 
  CreateTableOne(
    data = survey_data_tab1, 
    vars = table1Vars, factorVars = table1FactorVars
  )

tab1_baseline_no_study_arm


## Table 1 that was used for paper 

# Compare arms among hh used for analysis (participated in all three timepoints)
tab1_baseline <- 
  CreateTableOne(
    data = survey_data_tab1, 
    vars = table1Vars, factorVars = table1FactorVars, strata = "Study arm"
  )

tab1_baseline

# Compare only the hh that were in the IOM camps
tab1_baseline_IOM <- 
  CreateTableOne(
    data = survey_data_tab1_IOM, 
    vars = table1Vars, factorVars = table1FactorVars, strata = "Study arm"
  )

tab1_baseline_IOM

###############################################################################
# # Create Supplement table 2 
###############################################################################

## Supplemental table 2 code.... Comparing hh that were included in study compared to those dropped from study.
# Compare hh that dropped compared to those that did not
#Used to calculate the data that were missing by endline 
tab1_missing <-  
  CreateTableOne(data = missing_data_tab1, 
                 vars = table1Vars, factorVars = table1FactorVars, strata = "Study arm"
  )

tab1_comparison_dropped <-  
  CreateTableOne(data = survey_all_tab1 %>% filter(`Study arm` == "comparison"), 
                 vars = table1Vars, factorVars = table1FactorVars, strata = "dropped_yn"
  )

tab1_comparison_dropped

tab1_intervention_dropped <-  
  CreateTableOne(data = survey_all_tab1 %>% filter(`Study arm` == "intervention"), 
                 vars = table1Vars, factorVars = table1FactorVars, strata = "dropped_yn"
  )

tab1_intervention_dropped




###############################################################################
# # Save Table 1 datasets as CSVs
###############################################################################

tab1_baseline_no_study_arm_csv <- print(tab1_baseline_no_study_arm)
write.csv(tab1_baseline_no_study_arm_csv, "tab1_baseline_no_study_arm.csv")

tab1_baseline_csv <- print(tab1_baseline)
write.csv(tab1_baseline_csv, "tab1_baseline.csv")

tab1_comparison_dropped_csv <- print(tab1_comparison_dropped)
write.csv(tab1_comparison_dropped_csv, "tab1_comparison_dropped.csv")

tab1_intervention_dropped_csv <- print(tab1_intervention_dropped)
write.csv(tab1_intervention_dropped_csv, "tab1_intervention_dropped.csv")
```

# Deforestation Analysis and Figure 1
We collected our annual deforestation measurements by conducting an analysis on Google Earth Engine. The code for that analysis is at this link https://code.earthengine.google.com/2a498b4aeda511b70e5a0c353adad077
With the outputs of that analysis we created the following figure showing the deforestation in the camps over time.
```{r}
# Figure 1: Deforestation over time
plot_defor <- 
  data_hansen %>%
  mutate(
    forest_loss_km = round(forest_loss_m / 10^6, 1), 
    color_grp = case_when(
      year < 2017 ~ "pre-refugee", 
      year == 2017 | year == 2018 ~ "pre-LPG", 
      year >= 2019 ~ "after LPG"),
      color_grp = factor(color_grp, levels = c("pre-refugee", "pre-LPG", "after LPG"))
    ) %>% 
  ggplot(aes(x = year, y = forest_loss_km, fill = color_grp)) +
  geom_hline(aes(yintercept = 4.76), color = "darkgreen", linetype = "dashed") + 
  geom_hline(aes(yintercept = 8.83), color = "red", linetype = "solid") + 
  geom_hline(aes(yintercept = 5.4), color = "orange", linetype = "dotdash") + 
  geom_bar(stat = 'identity') +
  geom_text(aes(label = forest_loss_km), vjust = -0.5) + 
  annotate("text", x = 2002, y = 5, label = "pre-influx pre-2017") + 
  annotate("text", x = 2002, y = 9.2, label = "pre-LPG 2017-18") + 
  annotate("text", x = 2002, y = 5.7, label = "after LPG 2019-23") + 
  scale_fill_manual(values = c("pre-refugee" = "darkgreen", "pre-LPG" = "red", "after LPG" = "orange")) +
  theme_bw() + 
  labs(
    x = "Year", 
    y = "Forest Loss in Cox's Bazar Peninsula (in sq. km)",
    fill = "Period"
  ) +
  theme(legend.position = "top")

ggsave("/Users/christopherleboa/Downloads/fig1_defor.pdf", width = 10, height = 8)

# Find averages 
data_hansen %>%
	mutate(forest_loss_km = round(forest_loss_m / 10^6, 1)) %>% 
	mutate(
		group = 
				 	case_when(
				 		year < 2005 ~ 1, 
				 		year >=2005 & year < 2010 ~ 2,
				 		year >= 2010 & year < 2015 ~ 3, 
				 		year < 2017 & year > 2014 ~ 4, 
				 		year == 2017 ~ 2017,
				 		year == 2018 ~ 2018,
				 		year == 2019 ~ 2019,
				 		year >= 2019 ~ 5, 
				 		TRUE ~ NA_real_
				 	)) %>% 
	group_by(group) %>% 
	summarise(
		n = n(),
		mean = mean(forest_loss_km), 
		sd = sd(forest_loss_km)
		) %>% 
	mutate(
		margin = qt(0.975,df=n-1)*sd/sqrt(n), 
		low = mean - margin, 
		high = mean + margin
	)
```

# Self-reported fuel use

## Fuel usage by type Data Cleaning 
This section cleans the fuel use data and preps for figure 2 (next chunk)
```{r}
fuel_used_ever_bl <- 
	survey_data %>% 
	filter(timepoint == "baseline") %>%
	select(
		fcn_id,
		study_arm_overall,
		timepoint,
		fuel_ever_gather_scraps,
		fuel_ever_collect_wood,
		fuel_ever_receive_wood,
		fuel_ever_buy_wood,
		fuel_ever_receive_lpg,
		fuel_ever_buy_lpg,
		fuel_ever_receive_crh,
		fuel_ever_buy_crh,
		fuel_ever_other
	) %>%
	pivot_longer( 
		cols = c(
			fuel_ever_gather_scraps,
			fuel_ever_collect_wood,
			fuel_ever_receive_wood,
			fuel_ever_buy_wood,
			fuel_ever_receive_lpg,
			fuel_ever_buy_lpg,
			fuel_ever_receive_crh,
			fuel_ever_buy_crh,
			fuel_ever_other
		),
		names_to = "fuel"
	) %>%
	mutate(value = ifelse(is.na(value), 0, value)) %>%
	mutate(fuel = str_remove(fuel, "^.{10}")) %>%
	mutate(
		study_arm_overall = 
			ordered(
				study_arm_overall,
				levels = c("comparison", "intervention"),
				labels = c("Comparison group", "Intervention group")
			)
	) %>%
	mutate(
		fuel = 
			ordered(
				fuel,
				levels = c("gather_scraps", "collect_wood", "buy_wood", "receive_wood", "buy_crh", "receive_crh", "buy_lpg", "receive_lpg", "other"),
				labels = c("Scraps, gathered", "Wood, collected", "Wood, purchased", "Wood, received", "Compressed rice husks, purchased", "Compressed rice husks, received", "LPG, purchased", "LPG, received", "Plastic, collected") # We know from the qualitative interviews that Other == Plastic
			)
	)

fuel_used_ever_bl %>% 
  group_by(fuel, study_arm_overall) %>% 
  summarize(sum(value, na.rm = TRUE))

fuel_used_ever <- 
	survey_data %>% 
	filter(timepoint == "endline") %>%
	select(
		fcn_id,
		study_arm_overall,
		timepoint,
		fuel_ever_gather_scraps,
		fuel_ever_collect_wood,
		fuel_ever_receive_wood,
		fuel_ever_buy_wood,
		fuel_ever_receive_lpg,
		fuel_ever_buy_lpg,
		fuel_ever_receive_crh,
		fuel_ever_buy_crh,
		fuel_ever_other
	) %>%
	pivot_longer( 
		cols = c(
			fuel_ever_gather_scraps,
			fuel_ever_collect_wood,
			fuel_ever_receive_wood,
			fuel_ever_buy_wood,
			fuel_ever_receive_lpg,
			fuel_ever_buy_lpg,
			fuel_ever_receive_crh,
			fuel_ever_buy_crh,
			fuel_ever_other
		),
		names_to = "fuel"
	) %>%
	mutate(value = ifelse(is.na(value), 0, value)) %>%
	mutate(fuel = str_remove(fuel, "^.{10}")) %>%
	mutate(
		study_arm_overall = 
			ordered(
				study_arm_overall,
				levels = c("comparison", "intervention"),
				labels = c("Comparison group", "Intervention group")
			)
	) %>%
	mutate(
		fuel = 
			ordered(
				fuel,
				levels = c("gather_scraps", "collect_wood", "buy_wood", "receive_wood", "buy_crh", "receive_crh", "buy_lpg", "receive_lpg", "other"),
				labels = c("Scraps, gathered", "Wood, collected", "Wood, purchased", "Wood, received", "Compressed rice husks, purchased", "Compressed rice husks, received", "LPG, purchased", "LPG, received", "Plastic, collected") # We know from the qualitative interviews that Other == Plastic
			)
	) 

fuel_used_30_days <- 
	survey_data %>% 
	select(
		fcn_id,
		study_arm_overall,
		timepoint,
		fuel_30_gather_scraps,
		fuel_30_collect_wood,
		fuel_30_receive_wood,
		fuel_30_buy_wood,
		fuel_30_receive_lpg,
		fuel_30_buy_lpg,
		fuel_30_receive_crh,
		fuel_30_buy_crh,
		fuel_30_other, 
		fuel_use_non_lpg_freq_cook
	) %>%
	pivot_longer( 
		cols = c(
			fuel_30_gather_scraps,
			fuel_30_collect_wood,
			fuel_30_receive_wood,
			fuel_30_buy_wood,
			fuel_30_receive_lpg,
			fuel_30_buy_lpg,
			fuel_30_receive_crh,
			fuel_30_buy_crh,
			fuel_30_other
		),
		names_to = "fuel"
	) %>%
	mutate(value = ifelse(is.na(value), 0, value)) %>%
	mutate(fuel = str_remove(fuel, "^.{8}")) %>%
	mutate(
		study_arm_overall = 
			ordered(
				study_arm_overall,
				levels = c("comparison", "intervention"),
				labels = c("Comparison group", "Intervention group")
			), 
		 run_out = if_else(fuel_use_non_lpg_freq_cook > 0, 1, 0)
	) %>%
	mutate(
		fuel = 
			ordered(
				fuel,
				levels = c("gather_scraps", "collect_wood", "buy_wood", "receive_wood", "buy_crh", "receive_crh", "buy_lpg", "receive_lpg", "other"),
				labels = c("Scraps, gathered", "Wood, collected", "Wood, purchased", "Wood, received", "Compressed rice husks, purchased", "Compressed rice husks, received", "LPG, purchased", "LPG, received", "Plastic, collected") # We know from the qualitative interviews that Other == Plastic
			)
	)

## Get the cost of firewood in USD/Month 
survey_data %>% 
  filter(buy_wood_cost > 0) %>% 
  group_by(timepoint) %>% 
  summarise(mean(buy_wood_cost))

1032/84.88
```

## Figure 2 of self reported fuel use type by timepoint 
This figure represents the Fuel use reported by households at each time point

```{r}
#Create figure dataset 
fig_fuel_used_30_days_fig <- 
fuel_used_30_days %>%
  group_by(fuel, study_arm_overall, timepoint) %>%
  mutate(fuel = factor(fuel, levels = c(
    "LPG, received", "Scraps, gathered", "Wood, purchased",
    "LPG, purchased", "Compressed rice husks, purchased",
    "Compressed rice husks, received", "Plastic, collected"
  ))) %>%
  drop_na(fuel) %>% 
  summarise(
    prop = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    n = n(),
    upperE = prop + 1.96 * (sqrt(prop * (1 - prop) / n)),
    lowerE = prop - 1.96 * (sqrt(prop * (1 - prop) / n))
  ) %>%
  ungroup() %>%
  mutate(
    fuel_method = 
      case_when(
        str_detect(fuel, "purchased") == TRUE~ "purchased", 
        str_detect(fuel, "received") == TRUE~ "received", 
        TRUE ~ "collected"
        ), 
    fuel_type = 
      case_when(
        str_detect(fuel, "LPG") == TRUE~ "LPG", 
        str_detect(fuel, "rice") == TRUE~ "Compressed rice husks", 
        str_detect(fuel, "Wood") == TRUE~ "Wood", 
        str_detect(fuel, "Scraps") == TRUE~ "Wood", 
        TRUE ~ "Plastic"
        ),
  fuel_method = factor(fuel_method, levels = c("purchased", "received", "collected")),
  fuel_type = factor(fuel_type, levels = c("LPG", "Wood","Compressed rice husks", "Plastic"))
  ) %>% 
  ungroup()

survey_data %>% 
	select(
		fcn_id,
		study_arm_overall,
		timepoint,
		fuel_30_gather_scraps,
		fuel_30_collect_wood,
		fuel_30_receive_wood,
		fuel_30_buy_wood,
		fuel_30_receive_lpg,
		fuel_30_buy_lpg,
		fuel_30_receive_crh,
		fuel_30_buy_crh,
		fuel_30_other, 
		fuel_use_non_lpg_freq_cook, 
	) %>%
	  mutate(
	    wood = if_else(fuel_30_gather_scraps == 1 | fuel_30_buy_wood == 1 | fuel_30_collect_wood == 1 | fuel_30_receive_wood == 1, 1, 0),
	    lpg = if_else(fuel_30_buy_lpg == 1 | fuel_30_receive_lpg == 1, 1, 0),
	    crh = if_else(fuel_30_receive_crh == 1 | fuel_30_buy_crh == 1, 1, 0),
	    other = if_else(fuel_30_other == 1, 1, 0)) %>% 
	group_by(timepoint) %>%
	summarise(
		prop_wood = mean(wood, na.rm = TRUE), 
		n = n(),
		n_wood = sum(wood, na.rm = TRUE),
		prop_lpg = mean(lpg, na.rm = TRUE), 
		prop_crh = mean(crh, na.rm = TRUE), 
		prop_other = mean(other, na.rm = TRUE)
	)
  
  
#fig_fuel_used_30_days_fig

#Create figure 2 
fig_fuel_used_30_days_fig %>% 
  ggplot() +
  geom_point(aes(x = timepoint, y = prop, color = fuel_type)) +
  geom_line(aes(x = timepoint, y = prop, color = fuel_type, linetype = fuel_method, group = fuel)) +
  geom_errorbar(aes(x = timepoint, ymin = lowerE, ymax = upperE, color = fuel_type), width = 0.2) +
  scale_y_continuous(labels = scales::percent_format(), breaks = seq(0, 1, by = 0.1)) +
  labs(
    title = "Types of Cooking Fuel Used in the Past 30 Days,\n By Study Arm and Timepoint",
    color = "",
    linetype = "",
    x = "Timepoint",
    y = "Proportion of Households (%)"
  ) +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.box = "vertical") +
  guides(
    color = guide_legend(nrow = 1),
    linetype = guide_legend(nrow = 1)
  ) +
  facet_wrap(vars(study_arm_overall))

ggsave("/Users/christopherleboa/Downloads/fig2.pdf", width = 6, height = 6)
```

## Fuel Use Summary Table 
The information above was requested as a summary table.We have included it as a table in the supplement (SI2). The code below creates that table and saves it as a word document.
```{r}
table_fuel_use <- fig_fuel_used_30_days_fig %>%
  select(fuel_type, fuel_method, study_arm_overall, timepoint, prop, lowerE, upperE) %>%
  mutate(
    value = sprintf("%.3f (%.3f, %.3f)", prop, lowerE, upperE)
  ) %>%
  select(fuel_type, study_arm_overall, fuel_method, timepoint, value) %>%
  pivot_wider(
    names_from = timepoint,
    values_from = value
  #  values_fn = ~ first(.x)
  ) %>% arrange(fuel_type, fuel_method, study_arm_overall)

library(gt)

df_gt <- table_fuel_use %>%
  mutate(
    study_arm_overall = str_replace_all(study_arm_overall, "_", " "),
    fuel_method = str_replace_all(fuel_method, "_", " "),
    fuel_method = str_replace_all(fuel_method, "_", " ")
  )

pub_table <- df_gt %>%
  gt() %>%
  cols_move_to_start(study_arm_overall) %>%
  tab_header(
    title = "Fuel Use Over Time",
    subtitle = "Proportion (95% CI)"
  ) %>%
  cols_label(
    study_arm_overall = "Study arm (overall)",
    fuel_type = "Fuel type",
    fuel_method = "Fuel method",
    baseline = "Baseline",
    midline  = "Midline",
    endline  = "Endline"
  ) %>%
  tab_spanner(
    label = "Timepoint",
    columns = c(baseline, midline, endline)
  ) %>%
  opt_table_outline() %>%
  opt_all_caps()

gtsave(pub_table, "/Users/christopherleboa/Library/CloudStorage/GoogleDrive-cleboa@berkeley.edu/.shortcut-targets-by-id/1g4FGyxS0paoGycT8REXc9ZEXkWLVDMJr/Rohingya_analysis/supplement_fig_2_fuel_type_table.docx") 
```

## Run Out of LPG Analysis
The following code provides information on the households that report running out of LPG in the last month 
```{r}
#The overall fuel useage by timepoint 
  fuel_used_30_days %>% 
  group_by(fuel, study_arm_overall, timepoint) %>%
  summarise(
    mean.mpg = mean(value),          
    sd.mpg = sd(value, na.rm = TRUE),
    n.mpg = n()) %>%
  mutate(
    se.mpg = sd.mpg / sqrt(n.mpg),
    lower.ci.mpg = mean.mpg - qt(1 - (0.05 / 2), n.mpg - 1) * se.mpg,
   upper.ci.mpg = mean.mpg + qt(1 - (0.05 / 2), n.mpg - 1) * se.mpg)

#Fuel Use when Run Out of LPG given 
  fuel_used_30_days %>% 
  group_by(fuel, timepoint, run_out) %>%
    filter(run_out == 1) %>%
  summarise(
    mean = mean(value),          
    sd = sd(value, na.rm = TRUE),
    n = n()) %>%
  mutate(
    se = sd / sqrt(n),
    lower.ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
   upper.ci = mean + qt(1 - (0.05 / 2), n - 1) * se) 

#Fuel Use when Run Out of LPG given disaggregated by study arm (used for RF105B analysis)
fuel_used_30_days %>% 
  group_by(fuel, timepoint, study_arm_overall, run_out) %>%
  summarise(
    mean_use = mean(value, na.rm = TRUE),
    sd_use   = sd(value, na.rm = TRUE),
    n_use    = n(),
    se_use   = sd_use / sqrt(n_use),
    t_crit   = qt(0.975, df = n_use - 1),
    ci_lower = mean_use - t_crit * se_use,
    ci_upper = mean_use + t_crit * se_use,
    .groups = "drop"
  ) 

```

##Self reported stove stacking 
This takes the data of those that use fuel other than LPG in the last 30 days and 
```{r}

#Create dataset of fuel used other than lpg
fuel_used_30_days_wood_lpg_other <-
  survey_data %>%
  select(study_arm_overall, timepoint, fcn_id, contains("fuel_30")) %>%
  group_by(study_arm_overall, timepoint) %>%
  mutate(
    wood = 
      case_when( 
        fuel_30_buy_wood == 1 ~ 1, 
        fuel_30_collect_wood == 1 ~ 1, 
        fuel_30_receive_wood == 1 ~ 1,
        TRUE ~ 0
      ),
    biomass = 
      case_when(
        fuel_30_gather_scraps == 1 ~ 1, 
        fuel_30_buy_wood == 1 ~ 1, 
        fuel_30_collect_wood == 1 ~ 1, 
        fuel_30_receive_wood == 1 ~ 1, 
        fuel_30_buy_crh == 1 ~ 1,
        fuel_30_receive_crh == 1 ~ 1, 
        TRUE ~ 0
      ), 
    lpg = 
      case_when(
        fuel_30_buy_lpg == 1 ~ 1, 
        fuel_30_receive_lpg == 1 ~ 1, 
        TRUE ~ 0
      ),
    other = 
      case_when( 
        fuel_30_other == 1 ~ 1,
        TRUE ~ 0
      ),
  ) %>%
  mutate(n = 1)

# Creates summary of the number of households by timepoint that used wood, lpg, or other fuel in the last 30 days and the confidence intervals around those estimates.This gets the percentage of hh that use things other than LPG and LPG among those that use more than LPG in a month 
fuel_used_30_days_wood_lpg <- 
  fuel_used_30_days_wood_lpg_other %>% 
  pivot_longer(cols = c(wood, lpg), names_to = "fuel_simple", values_to = "value") %>% 
  group_by( timepoint, fuel_simple) %>% 
  summarise(
    prop = mean(value),
    sd = sd(value),
    binom.confint(x = sum(value, na.rm = TRUE), n = sum(n), methods = "wilson")
  ) %>%
  ungroup() 

## Reasons for stove stacking
survey_data %>% 
  group_by(timepoint, study_arm_overall) %>% 
  count(buy_wood_reason)
  
#Intervention results 
271/(271+31+4)
31/(271+31+4)
4/(271+31+4)

#Comparison results 
96/(96+11+20)
11/(96+11+20)
20/(96+11+20)

```

## Percentage of households that could not afford fuel in prior 2 weeks 
```{r }
#Overall results 
	survey_data %>% 
		group_by(study_arm_overall, timepoint) %>% 
		summarize(
			hh = n(),
			num_not_afford = sum(fuel_cant_afford_2wk, na.rm = TRUE), 
			p = (sum(fuel_cant_afford_2wk, na.rm = TRUE)) / n(),
			margin = qnorm(0.975)*sqrt(p*(1-p)/hh), 
			low = p - margin, 
			high = p + margin)

#endline results only 
survey_data %>% 
  filter(timepoint=="endline") %>% 
  group_by(timepoint, study_arm_overall) %>% 
  summarize(
    hh = n(),
    p = (sum(fuel_cant_afford_2wk, na.rm = TRUE)) / n(),
    margin = qnorm(0.975)*sqrt(p*(1-p)/hh), 
    low = p - margin, 
    high = p + margin)


########################################################################
#Calculating the number of days before refill the hh ran out of LPG
#######################################################################

# Creates dataset with number of hh that ran out of LPG as new column 
freq_cook <- 
  survey_data %>% 
  filter(!fuel_use_non_lpg_freq_cook > 200 | is.na(fuel_use_non_lpg_freq_cook)) %>% 
  group_by(study_arm_overall, timepoint) %>% 
  mutate(
    run_out = if_else(fuel_use_non_lpg_freq_cook > 0, 1, 0)
  ) 


#Presents overall results of # of hh that ran out of lpg 
freq_cook %>% 
  ungroup() %>% 
  group_by(timepoint) %>% 
  summarize(
    mean = mean(fuel_use_non_lpg_freq_cook,  na.rm = TRUE),    
    sd = sd(fuel_use_non_lpg_freq_cook, na.rm = TRUE),
    n = n(), 
    n_out = sum(run_out, na.rm = TRUE),
    pct_out = sum(run_out, na.rm = TRUE)/n
  ) %>%
  mutate(
    se = sd/ sqrt(n),
    lower.ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
    upper.ci = mean + qt(1 - (0.05 / 2), n - 1) * se, 
    lower.ci.prop = pct_out - 1.96 * sqrt((pct_out/(1-pct_out)/n)), 
    upper.ci.prop = pct_out + 1.96 * sqrt((pct_out/(1-pct_out)/n)),
  ) 

#Breaks down results of # of hh that ran out by study arm
freq_cook %>% 
  ungroup() %>% 
  group_by(timepoint, study_arm_overall) %>% 
  summarize(
    mean = mean(fuel_use_non_lpg_freq_cook,  na.rm = TRUE),    
    sd = sd(fuel_use_non_lpg_freq_cook, na.rm = TRUE),
    n = n(),
    num_out = sum(run_out, na.rm = TRUE),
    pct_out = sum(run_out, na.rm = TRUE)/n
  ) %>%
  mutate(
    
    se = sd/ sqrt(n),
    lower.ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
    upper.ci = mean + qt(1 - (0.05 / 2), n - 1) * se, 
    lower.ci.prop = pct_out - 1.96 * sqrt((pct_out/(1-pct_out)/n)), 
    upper.ci.prop = pct_out + 1.96 * sqrt((pct_out/(1-pct_out)/n)),
  ) 
```
## Effect estimate of fuel change 
This information is included in table Supplement 1.2.1
```{r}
# Looking at impact of fuel changes using difference in difference model 
library(estimatr)

model_fuel <- survey_data %>% 
  filter(timepoint != "midline")

model_fuel$fuel_30_gather_scraps

outcomes <- c(
 "fuel_30_gather_scraps", "fuel_30_collect_wood", "fuel_30_receive_wood", "fuel_30_buy_wood","fuel_30_receive_lpg", "fuel_30_buy_lpg", "fuel_30_receive_crh", "fuel_30_buy_crh", "fuel_30_other"
)

models <- lapply(outcomes, function(outcome) {
  formula <- as.formula(
    paste(outcome, "~ timepoint_num * study_arm_overall_num")
  )
  
  lm_robust(
    formula,
    data = model_fuel,
    clusters = fcn_id
  )
})
names(models) <- outcomes

# Extract DiD coefficient and CI
did_results <- do.call(rbind, lapply(names(models), function(outcome) {
  m <- models[[outcome]]
  
  coef_val <- coef(m)["timepoint_num:study_arm_overall_num"]
  ci <- confint(m)["timepoint_num:study_arm_overall_num", ]
  
  data.frame(
    outcome = outcome,
    did_coef = coef_val,
    ci_lower = ci[1],
    ci_upper = ci[2]
  )
}))

did_results
```



## Burning of plastics 
```{r}
########################################################################
## Percent of households that report fuel shortages use Plastics  
#######################################################################

# Of hh that report running out of fuel 
freq_cook %>%
  filter(fuel_cant_afford_2wk == 1) %>% 
  group_by(timepoint, study_arm_overall) %>%
  mutate(
    burn_plastic_yn = if_else(burn_plastic_frequency > 0, 1, 0), #Burn plastic at all 
    burn_plastic_gt2 = if_else(burn_plastic_frequency > 1, 1, 0), #Burns plastic at least 2x per week 
  ) %>%
  summarize(
    n_total = n(),
    n = sum(burn_plastic_yn, na.rm = TRUE),
    n2x = sum(burn_plastic_gt2, na.rm = TRUE),
    prop_plastic_any = mean(burn_plastic_yn, na.rm = TRUE),
    prop_plastic_gt2x = mean(burn_plastic_gt2, na.rm = TRUE)
  ) 

#Of hh that do not report fuel insecurity 
freq_cook %>%
  #filter(fuel_cant_afford_2wk == 0) %>% 
  group_by(timepoint, study_arm_overall) %>%
  mutate(
    burn_plastic_yn = if_else(burn_plastic_frequency > 0, 1, 0), #Burn plastic at all 
    burn_plastic_gt2 = if_else(burn_plastic_frequency > 1, 1, 0), #Burns plastic at least 2x per week 
  ) %>%
  summarize(
    n_total = n(),
    n = sum(burn_plastic_yn, na.rm = TRUE),
    n2x = sum(burn_plastic_gt2, na.rm = TRUE),
    prop_plastic_any = mean(burn_plastic_yn, na.rm = TRUE),
    prop_plastic_gt2x = mean(burn_plastic_gt2, na.rm = TRUE)
  ) 

fuel_used_30_days %>% 
  group_by(fuel, timepoint, study_arm_overall) %>% 
  summarise(
    mean = mean(value),          
    sd = sd(value, na.rm = TRUE),
    n_total = sum(value, na.rm = TRUE),
    n = n())


```
## The types of fuel households choose when they run out of LPG
```{r}
  fuel_used_30_days %>% 
  mutate(run_out = if_else(fuel_use_non_lpg_freq_cook > 0, 1, 0)) %>%
  filter(run_out == 1) %>%
  group_by(fuel, timepoint) %>%
  summarise(
    mean = mean(value),          
    sd = sd(value, na.rm = TRUE),
    n_ftype = sum(value, na.rm = TRUE),
    n = n()) %>%
  mutate(
    se = sd / sqrt(n),
    lower.ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
   upper.ci = mean + qt(1 - (0.05 / 2), n - 1) * se) 
```


## Fuel Can't Afford Coping Mechanisms 
```{r pressure, echo=FALSE}
# Fuel cant afford 
survey_data %>%
  filter(
    fuel_cant_afford_2wk == 1,
    !is.na(fuel_cant_afford_action),
    study_arm_overall == "intervention",
    timepoint == "baseline"
  ) %>%
  count(fuel_cant_afford_action) %>%
#  group_by(fuel_cant_afford_action) %>%
  mutate(
    p = n / sum(n),
     sum(n),
    margin = ifelse(n > 1, qnorm(0.975) * sqrt(p * (1 - p) / n), NA),
    low = ifelse(!is.na(margin), p - margin, NA),
    high = ifelse(!is.na(margin), p + margin, NA)
  ) %>%
  arrange(desc(p))

# Looking at impact of fuel changes
model_data_dif <- 
  model_data %>% 
  mutate(
     # Convert factor to character first, then apply replace_na and convert to numeric if needed
    fuel_cant_afford_action = as.numeric(replace_na(as.character(fuel_cant_afford_action), "0")),
    borrow_fuel = if_else(fuel_cant_afford_action == 1, 1, 0), 
    reduce_meals = if_else(fuel_cant_afford_action == 3, 1, 0), 
    borrow_money = if_else(fuel_cant_afford_action == 8, 1, 0), 
    work_extra = if_else(fuel_cant_afford_action == 11, 1, 0), 
    purchase_credit = if_else(fuel_cant_afford_action == 7, 1, 0), 
    sold_food = if_else(fuel_cant_afford_action == 13, 1, 0), 
    burn_plastic = if_else(burn_plastic_frequency > 0, 1, 0)
  )

model_data_dif$work_extra


# Looking at impact of fuel changes using difference in difference model 
library(estimatr)

outcomes <- c(
  "borrow_fuel",
  "reduce_meals",
  "borrow_money",
  "purchase_credit",
  "work_extra",
  "sold_food", 
  "burn_plastic"
)

models <- lapply(outcomes, function(outcome) {
  formula <- as.formula(
    paste(outcome, "~ timepoint_num * study_arm_overall_num")
  )
  
  lm_robust(
    formula,
    data = model_data_dif,
    clusters = fcn_id
  )
})
names(models) <- outcomes

# Extract DiD coefficient and CI
did_results <- do.call(rbind, lapply(names(models), function(outcome) {
  m <- models[[outcome]]
  
  coef_val <- coef(m)["timepoint_num:study_arm_overall_num"]
  ci <- confint(m)["timepoint_num:study_arm_overall_num", ]
  
  data.frame(
    outcome = outcome,
    did_coef = coef_val,
    ci_lower = ci[1],
    ci_upper = ci[2]
  )
}))

did_results

```

# Stove Use Analysis 
We analyze the stove use in an earlier data cleaning script. Here we create the data for figure 4 and the analysis of stove use over time after receiving LPG.


##Summary statistics for stove use
```{r}
#Number of total days included == the number of rows in the dataset 
  #7577
total_days <- 6893+544+140

#Exclusive LPG days 
6884/total_days
#exclusive biomass days 
552/total_days
#mixed days 
153/total_days

df_events_stove_on_per_day <- 
  df_events_stove_on_per_day %>% 
  filter(processor_name == "firefinder_100_80_5_20")

### The number of events by type of exclusive use day
df_events_stove_on_per_day %>% 
  summarise(
    b_use = sum(exclusive_biomass), lpg_use = sum(exclusive_lpg), mix_use = sum(mixed_use)
  )
  
### Use time and number of uses for each type of exclusive use day 
output1 <- df_events_stove_on_per_day %>%
  filter(exclusive_lpg == TRUE) %>%
  #dplyr::group_by(processor_name) %>% 
  dplyr::summarise(across(starts_with(c("cooking_events", "stove_on")),
                          .fns = list(
                            mean = ~mean(.x, na.rm = TRUE), 
                            sd = ~sd(.x, na.rm = TRUE), 
                            se = ~sd(.x, na.rm = TRUE)/sqrt(length(.x)),
                            n = ~n(),
                            ci_l = ~mean(.x, na.rm = TRUE) - (1.96 * sd(.x, na.rm = TRUE)/sqrt(n())),
                            ci_u = ~mean(.x, na.rm = TRUE) + (1.96 * sd(.x, na.rm = TRUE)/sqrt(n())))))

output2 <- df_events_stove_on_per_day %>%
  filter(exclusive_biomass == TRUE) %>%
 # dplyr::group_by(processor_name) %>% 
  dplyr::summarise(across(starts_with(c("cooking_events", "stove_on")),
                          .fns = list(
                            mean = ~mean(.x, na.rm = TRUE), 
                            sd = ~sd(.x, na.rm = TRUE), 
                            se = ~sd(.x, na.rm = TRUE)/sqrt(length(.x)),
                            n = ~n(),
                            ci_l = ~mean(.x, na.rm = TRUE) - (1.96 * sd(.x, na.rm = TRUE)/sqrt(n())),
                            ci_u = ~mean(.x, na.rm = TRUE) + (1.96 * sd(.x, na.rm = TRUE)/sqrt(n())))))

output3 <- df_events_stove_on_per_day %>%
  filter(mixed_use == TRUE) %>%
 # dplyr::group_by(processor_name) %>% 
  dplyr::summarise(across(starts_with(c("cooking_events", "stove_on")),
                          .fns = list(
                            mean = ~mean(.x, na.rm = TRUE), 
                            sd = ~sd(.x, na.rm = TRUE), 
                            se = ~sd(.x, na.rm = TRUE)/sqrt(length(.x)),
                            n = ~n(),
                            ci_l = ~mean(.x, na.rm = TRUE) - (1.96 * sd(.x, na.rm = TRUE)/sqrt(n())),
                            ci_u = ~mean(.x, na.rm = TRUE) + (1.96 * sd(.x, na.rm = TRUE)/sqrt(n())))))

bind_rows(output1, output2, output3)

```

##Data cleaning for stove use over time after receiving LPG

In other papers there are reports of decreasing intervention updake over time. We want to analyze that here be looking at stove use over time 
```{r}
#Create a variable for number of days since self reported first receiving lpg 
df_days_receive <- 
  df_events_stove_on_per_day %>% 
  mutate(
    days_after_first_receiving = date - first_receive_lpg_ymd,
         before_after = if_else(days_after_first_receiving< 0, "Days Before Intervention", "Days After Receiving"), 
         before_after = factor(before_after, levels = c( "Days Before Intervention", "Days After Receiving"))
    
    ) %>% 
  filter(before_after == "Days After Receiving")

df_stove_exclusive_use_by_month <-
	df_events_stove_on_per_day %>%
	group_by(fcn_id, months_after_first_receiving, lpg_enrolled_and_receiving) %>%
	summarise(mean = mean(exclusive_lpg == TRUE, na.rm = TRUE)) %>%
	arrange(months_after_first_receiving)

```

## Energy Use Calculations
```{r}
# Figure 4 energy conversions 
## In this figure we convert stove usage to MJ of use for each stove type and total 
## This means multiplying the Time use by the efficiency of each stove and creating a total column for each 

# Stove efficiencies: % Thermal efficiency 
lpg_efficiency <- .50 #These are standards for doing stove efficiency calculations for carbon credits 
biomass_efficiency <-.15

#Sensitivity analysis for paper supplement
lpg_efficiency_2 <- .67 #This is taken from UNHCR stove specifications from safe+2
biomass_efficiency_2 <-.128
#This paper says 14% for three stone file https://pubs-acs-org.libproxy.berkeley.edu/doi/10.1021/es301693f
#we used the value for trditional stove from here https://baec.portal.gov.bd/sites/default/files/files/baec.portal.gov.bd/page/1f00cd0e_737d_4e2e_ab9f_08183800b7a2/NSA-Vol%2024-Article%201.pdf
#This article also has traditional wood fires as between 17 and 12% efficient 

#Energy Reached the pot (MJ) == (Power (KW) * Time (min)) * Thermal efficiency (%)

#Convert KWH to MJ
# 1 KWH = 3.6 MJ
conv_mJ <- 3.6

power_wood <- 6.824/conv_mJ  #KW Power of wood stove mixed start from Islam, Khanam, Rouf, and Rahaman 2012
power_lpg <- 3.4/conv_mJ #KW  Power of LPG stove taken from UNHCR specification\

#The df days receive dataset has two separate processors in it. I will keep only data with the processor `firefinder_100_80_5_20`


## Data on Energy use 
data_fig3 <-  
df_days_receive %>% 
  group_by(hh_id, days_after_first_receiving) %>%
  filter(processor_name == "firefinder_100_80_5_20") %>% 
  mutate(
    stove_on_min_sum_biomass = if_else(is.na(stove_on_min_sum_biomass), 0, stove_on_min_sum_biomass), 
    stove_on_min_sum_lpg = if_else(is.na(stove_on_min_sum_lpg), 0, stove_on_min_sum_lpg)) %>% 
  summarise(
    biomass = sum(stove_on_min_sum_biomass),
    lpg = sum(stove_on_min_sum_lpg), 
    both = if_else(mixed_use == TRUE, biomass + lpg, NA),
    biomass = (biomass/60* power_wood), 
    lpg = (lpg/60 * power_lpg), 
    both = if_else(mixed_use == TRUE, biomass + lpg, NA)
  ) %>% 
  pivot_longer(cols = c(biomass, lpg, both), names_to = "Energy", values_to = "Energy Use (MJ)") %>%
  filter(`Energy Use (MJ)`>0) %>% 
   mutate(Energy = recode(Energy, both = "mixed use")) 


# Data on energy reaching the pot 
data_fig3.2 <- 
df_days_receive %>% 
  group_by(hh_id, days_after_first_receiving) %>%
  filter(processor_name == "firefinder_100_80_5_20") %>% 
  mutate(
    stove_on_min_sum_biomass = if_else(is.na(stove_on_min_sum_biomass), 0, stove_on_min_sum_biomass), 
    stove_on_min_sum_lpg = if_else(is.na(stove_on_min_sum_lpg), 0, stove_on_min_sum_lpg)) %>% 
  summarise(
    biomass = sum(stove_on_min_sum_biomass),
    lpg = sum(stove_on_min_sum_lpg), 
    both = if_else(mixed_use == TRUE, biomass + lpg, NA),
    biomass = (biomass/60* power_wood) * biomass_efficiency, 
    lpg = (lpg/60 * power_lpg) * lpg_efficiency, 
    both = if_else(mixed_use == TRUE, biomass + lpg, NA)
  ) %>% 
  pivot_longer(cols = c(biomass, lpg, both), names_to = "Energy", values_to = "Energy Use (MJ)") %>%
  filter(`Energy Use (MJ)`>0) %>% 
   mutate(Energy = recode(Energy, both = "mixed use")) #Request for changing both to mixed use 


summary_stats <- data_fig3 %>%
  group_by(Energy) %>%
  summarise(
    mean_energy = mean(`Energy Use (MJ)`, na.rm = TRUE),
    sd_energy = sd(`Energy Use (MJ)`, na.rm = TRUE),
    n = n(),
    se_energy = sd_energy / sqrt(n), # Standard Error
    ci_lower = mean_energy - qt(0.975, df = n - 1) * se_energy, # 95% CI lower
    ci_upper = mean_energy + qt(0.975, df = n - 1) * se_energy  # 95% CI upper
  )

summary_stats_3.2 <- data_fig3.2 %>%
  group_by(Energy) %>%
  summarise(
    mean_energy = mean(`Energy Use (MJ)`, na.rm = TRUE),
    sd_energy = sd(`Energy Use (MJ)`, na.rm = TRUE),
    n = n(),
    se_energy = sd_energy / sqrt(n), # Standard Error
    ci_lower = mean_energy - qt(0.975, df = n - 1) * se_energy, # 95% CI lower
    ci_upper = mean_energy + qt(0.975, df = n - 1) * se_energy  # 95% CI upper
  )

summary_stats

summary_stats_3.2
```


#Percentage of each energy used on mixed use days
(In response to reviewer comments about)
```{r}
data_fig3 %>% 
  pivot_wider(names_from = Energy, values_from = `Energy Use (MJ)`) %>%
  group_by(hh_id, days_after_first_receiving) %>% 
  filter(!is.na(lpg) & !is.na(biomass)) %>% 
  mutate(percent_lpg_energy = lpg/`mixed use`) %>% 
  ungroup() %>% 
  summarise(
    mean_percent = mean(percent_lpg_energy, na.rm = TRUE), 
    sd_percent = sd(percent_lpg_energy, na.rm = TRUE))


data_fig3.2 %>% 
  pivot_wider(names_from = Energy, values_from = `Energy Use (MJ)`) %>%
  group_by(hh_id, days_after_first_receiving) %>% 
  filter(!is.na(lpg) & !is.na(biomass)) %>% 
  mutate(percent_lpg_energy = lpg/`mixed use`) %>% 
  ungroup() %>% 
  summarise(
    mean_percent = mean(percent_lpg_energy, na.rm = TRUE), 
    sd_percent = sd(percent_lpg_energy, na.rm = TRUE))

```

##Stove Use Monitoring 

Figure 3 
```{r}

# Top Row of Plot

fig2.3 <- 
  df_days_receive %>% 
  filter(fcn_id != "280680") %>% 
   mutate(
     biomass = if_else(!is.na(stove_on_min_sum_biomass), 1,0), 
     lpg = if_else(!is.na(stove_on_min_sum_lpg), 1, 0)
   ) %>% 
  pivot_longer(cols = c(biomass, lpg), names_to = "stove_monitored", values_to = "stove_count" ) %>% 
  group_by(days_after_first_receiving, months_after_first_receiving, before_after, stove_monitored) %>%
  summarise(`Number Stoves Monitored`= sum(stove_count)) %>% 
 # pivot_longer(cols = c(biomass, lpg), names_to = "Stove", values_to = "Average Percent Use") %>% 
  ggplot(aes(x = months_after_first_receiving, y = `Number Stoves Monitored`)) +
  geom_jitter(aes(color = stove_monitored), alpha = .4) + 
  #facet_grid(cols = vars(before_after), scales = "free_x") + 
  scale_x_continuous(minor_breaks = seq(0,40,12), breaks = seq(0,40,12))  +
  scale_color_manual(values = c("red3","steelblue")) + 
  theme_bw() + 
  theme(legend.position = "top") + 
  labs(y = "Number of \n stoves monitored", color = "Fuel Type", title = "",x = "")
# Second Row of the plot

#For top two rows of the graph use the mean of hh that had at least least 1 minutes of use in a day  
fig2.1 <- 
  df_days_receive %>% 
  filter(fcn_id != "280680") %>% 
  group_by(days_after_first_receiving, before_after, months_after_first_receiving) %>%
  summarise(biomass = mean(stove_on_min_sum_biomass, na.rm = TRUE), lpg = mean(stove_on_min_sum_lpg, na.rm = TRUE)) %>% 
  pivot_longer(cols = c(biomass, lpg), names_to = "Stove", values_to = "Average minutes of use") %>%
 # mutate("Average Minutes of Use" = replace_na("Average Minutes of Use", 0)) %>% 
 # filter(`Average minutes of use`>0) %>% 
  ggplot(aes(x = months_after_first_receiving, y = `Average minutes of use`)) +
  geom_point(aes(color = Stove), alpha = .4) + 
  scale_color_manual(values = c("red3","steelblue")) + 
  #facet_grid(cols = vars(before_after), scales = "free_x") + 
  theme_bw() + 
   scale_x_continuous(minor_breaks = seq(0,40,12), breaks = seq(0,40,12)) +
  theme(legend.position = "none") + 
  labs(title = "", x = "", y = "Av. minutes \nstove use per day", color = "Fuel Type")


#Third Row of the plot 

#This group of code was used to get the max number of stoves data collected from in a month 
fig_df_stove_exclusive_use_label_group <-
  df_stove_exclusive_use_by_month %>%
  filter(lpg_enrolled_and_receiving == "receiving LPG through distribution program") %>%
  group_by(months_after_first_receiving) %>%
  summarise(
    n = n())


fig_df_stove_exclusive_use <-
  df_stove_exclusive_use_by_month %>%
  #filter(fcn_id %notin% c(df_have_geocene_but_no_survey_data_fcn_id)) %>%
  filter(lpg_enrolled_and_receiving == "receiving LPG through distribution program") %>%
  ggplot(aes(x = months_after_first_receiving, y = mean, color = as.factor(months_after_first_receiving))) +
  geom_jitter(alpha = 0.4, color = "steelblue") + 
  stat_summary(aes(group = months_after_first_receiving), geom = "linerange", fun.data = "mean_cl_boot", colour = "black") +
  stat_summary(aes(group = months_after_first_receiving), geom = "point", fun.data = "mean_cl_boot", colour = "black", shape = 17, size = 2) +
  # scale_color_brewer(palette = "Paired") +
  # scale_color_manual(values = mycolors) +
  #scale_color_manual(values = getPalette(color_count)) +
  
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(minor_breaks = seq(0,40,12), breaks = seq(0,40,12)) +
  # geom_text(
  #   inherit.aes = FALSE,
  #   aes(
  #     x = - .5, 
  #     y = 1.05, 
  #     label = "n ="
  #   )
  # ) +
  # geom_text(
  #   data = fig_df_stove_exclusive_use_label_group,
  #   inherit.aes = FALSE,
  #   aes(
  #     x = months_after_first_receiving, 
  #     y = 1.05, 
  #     label = n
  #     # label = paste("n = ", n)
  #   )
  # ) +
  theme_bw() + 
  theme(
    legend.position = "none"
  ) + 
  labs(
    title = "",
    x = "Months after first receiving LPG through free distribution program",
    y = "Days per month household \ncooked exclusively with LPG (%)"
  ) +
  coord_cartesian(clip = "off")

fig_df_stove_exclusive_use

# Plot each on top of one another in larger figure using the geomExtra package
gC <- ggplotGrob(fig2.3)
gA <- ggplotGrob(fig2.1)
gB <- ggplotGrob(fig_df_stove_exclusive_use)


maxWidth = grid::unit.pmax(gA$widths[2:5], gB$widths[2:5], gC$widths[2:5])
gA$widths[2:5] <- as.list(maxWidth)
gB$widths[2:5] <- as.list(maxWidth)
gC$widths[2:5] <- as.list(maxWidth)


fig3 <-
grid.arrange(
  gC,
  gA,
  gB,
  heights=c(1.3, 1, 1.3),
  nrow = 3,
  layout_matrix = rbind(c(1), c(2), c(3))
)

print(fig3)

ggsave("fig3_250329.png", plot = fig3, width = 9.5, height = 9, dpi = 300)





fig3.1 <-
  data_fig3 %>% 
  ggplot(aes(x = Energy, y = `Energy Use (MJ)`)) +
  geom_boxplot(aes(color = Energy), alpha = 0.5) + 
  #facet_grid(cols = vars(before_after), scales = "free_x") + 
    # Mean with error bars using stat_summary
  # stat_summary(
  #   aes(color = Energy),
  #   fun = mean,
  #   geom = "point",
  #   size = 3
  # ) +
  # Error bars for the mean
  # stat_summary(
  #   aes(color = Energy),
  #   fun.data = mean_cl_normal,  # Calculates mean and CI
  #   geom = "errorbar",
  #   width = 0.2,
  # ) +
  theme_bw()+
  theme(legend.position = "none") + 
  scale_y_continuous(limits=c(0,20)) +
  scale_colour_manual(values = c( "red3","steelblue", "purple")) +
  labs(y = "Daily energy consumed (MJ/hh/day)", x = "cooking method")

fig3.2 <- 
data_fig3.2 %>% 
  ggplot(aes(x = Energy, y = `Energy Use (MJ)`)) +
  geom_boxplot(aes(color = Energy), alpha = 0.5) + 
  #facet_grid(cols = vars(before_after), scales = "free_x") + 
  #   stat_summary(
  #   aes(color = Energy),
  #   fun = mean,
  #   geom = "point",
  #   size = 3
  # ) +
  # Error bars for the mean
  # stat_summary(
  #   aes(color = Energy),
  #   fun.data = mean_cl_normal,  # Calculates mean and CI
  #   geom = "errorbar",
  #   width = 0.2,
  # ) +
  theme_bw()+
  theme(legend.position = "none") + 
  scale_y_continuous(limits=c(0,20)) +
  scale_colour_manual(values = c( "red3","steelblue", "purple")) +
  labs(y = "Daily energy that reached the pot (MJ/hh/day)", x= "cooking method")

# Plot each on top of one another in larger figure using the geomExtra package
gA <- ggplotGrob(fig3.1)
gB <- ggplotGrob(fig3.2)


maxWidth = grid::unit.pmax(gA$widths[2:5], gB$widths[2:5])
gA$widths[2:5] <- as.list(maxWidth)
gB$widths[2:5] <- as.list(maxWidth)

max(df_events_stove_on_per_day$days_after_first_receiving)

#Fnd Number of hh included in the stove use analysis 
table(df_events_stove_on_per_day$hh_id)

### Print out figure 4 
fig4 <- 
  grid.arrange(
  ncol = 2,
  gA,
  gB
)

# Combine figures 3 and 4 
final_combined_plot <- ggarrange(
  fig3, fig4,
  ncol = 1,  # stack vertically
  heights = c(3, 2),  # adjust as needed
  labels = c("A", "B"),  # optional labels
  align = "v"
)

# Save combined figure
ggsave(
  filename = "/Users/christopherleboa/Downloads/fig3_and_4_combined_no_lpg.pdf",
  plot = final_combined_plot,
  width = 8,
  height = 11,
  units = "in",
  dpi = 300
)


```



```{r}

#Create per capita/day assessments of stove use
hh_size_est <- survey_data %>% 
  select(fcn_id, hh_size) %>% 
  mutate(fcn_id = as.numeric(fcn_id)) %>%
  left_join(df_events_stove_on_per_day, by = "fcn_id") %>%
  mutate(
    cooking_events_with_lpg = cooking_events_with_lpg / hh_size,
    cooking_events_with_biomass = cooking_events_with_biomass / hh_size,
    stove_on_min_sum_lpg = stove_on_min_sum_lpg / hh_size,
    stove_on_min_sum_biomass = stove_on_min_sum_biomass / hh_size
  )

summary_stats <- function(df) {
  df %>%
    group_by(processor_name) %>% 
    summarise(across(
      starts_with(c("cooking_events", "stove_on")),
      .fns = list(
        mean = ~mean(.x, na.rm = TRUE),
        sd = ~sd(.x, na.rm = TRUE),
        se = ~sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x))),
        n = ~sum(!is.na(.x)),
        ci_l = ~mean(.x, na.rm = TRUE) - 1.96 * sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x))),
        ci_u = ~mean(.x, na.rm = TRUE) + 1.96 * sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))
      ),
      .names = "{.col}_{.fn}"
    ))
}

output1_hh <- hh_size_est %>% filter(exclusive_lpg == 1) %>% summary_stats()
output2_hh <- hh_size_est %>% filter(exclusive_biomass == 1) %>% summary_stats()
output3_hh <- hh_size_est %>% filter(mixed_use == 1) %>% summary_stats()

bind_rows(output1_hh, output2_hh, output3_hh)


### Energy use per capita by fuel type 
## Data on Energy use 
data_fig3 <-  
hh_size_est %>% 
  #filter(exclusive_lpg == 1) %>% #Not best practice but I commented out this for each of the different groupings 
  #filter(exclusive_biomass == 1) %>%
  filter(mixed_use == 1) %>% 
  group_by(hh_id, days_after_first_receiving) %>%
  mutate(
    stove_on_min_sum_biomass = if_else(is.na(stove_on_min_sum_biomass), 0, stove_on_min_sum_biomass), 
    stove_on_min_sum_lpg = if_else(is.na(stove_on_min_sum_lpg), 0, stove_on_min_sum_lpg)) %>% 
  summarise(
    biomass = sum(stove_on_min_sum_biomass),
    lpg = sum(stove_on_min_sum_lpg), 
    both = biomass + lpg, 
    biomass = (biomass/60* power_wood)/hh_size, 
    lpg = (lpg/60 * power_lpg)/hh_size, 
    both = biomass + lpg
  ) %>% 
  pivot_longer(cols = c(biomass, lpg, both), names_to = "Energy", values_to = "Energy Use (MJ)") %>%
  filter(`Energy Use (MJ)`>0) %>% 
   mutate(Energy = recode(Energy, both = "mixed use")) 
   


# Data on energy reaching the pot 
data_fig3.2 <- 
hh_size_est %>% 
  #filter(exclusive_lpg == 1) %>%
  #filter(exclusive_biomass == 1) %>%
  filter(mixed_use == 1) %>% 
  group_by(hh_id, days_after_first_receiving) %>%
  
  mutate(
    stove_on_min_sum_biomass = if_else(is.na(stove_on_min_sum_biomass), 0, stove_on_min_sum_biomass), 
    stove_on_min_sum_lpg = if_else(is.na(stove_on_min_sum_lpg), 0, stove_on_min_sum_lpg)) %>% 
  summarise(
    biomass = sum(stove_on_min_sum_biomass),
    lpg = sum(stove_on_min_sum_lpg), 
    both = biomass + lpg, 
    biomass = (biomass/60* power_wood)/hh_size * biomass_efficiency, 
    lpg = (lpg/60 * power_lpg)/hh_size * lpg_efficiency, 
    both = biomass + lpg
  ) %>% 
  pivot_longer(cols = c(biomass, lpg, both), names_to = "Energy", values_to = "Energy Use (MJ)") %>%
  filter(`Energy Use (MJ)`>0) %>% 
   mutate(Energy = recode(Energy, both = "mixed use")) #Request for changing both to mixed use 


summary_stats_hh <- data_fig3 %>%
  group_by(Energy) %>%
  summarise(
    mean_energy = mean(`Energy Use (MJ)`, na.rm = TRUE),
    sd_energy = sd(`Energy Use (MJ)`, na.rm = TRUE),
    n = n(),
    se_energy = sd_energy / sqrt(n), # Standard Error
    ci_lower = mean_energy - qt(0.975, df = n - 1) * se_energy, # 95% CI lower
    ci_upper = mean_energy + qt(0.975, df = n - 1) * se_energy  # 95% CI upper
  )

summary_stats_3.2_hh <- data_fig3.2 %>%
  group_by(Energy) %>%
  summarise(
    mean_energy = mean(`Energy Use (MJ)`, na.rm = TRUE),
    sd_energy = sd(`Energy Use (MJ)`, na.rm = TRUE),
    n = n(),
    se_energy = sd_energy / sqrt(n), # Standard Error
    ci_lower = mean_energy - qt(0.975, df = n - 1) * se_energy, # 95% CI lower
    ci_upper = mean_energy + qt(0.975, df = n - 1) * se_energy  # 95% CI upper
  )

summary_stats_hh
summary_stats_3.2_hh

```


## Cooking event per day 
This analysis is not included in the article but we are leaving in the public code to show the breakdown of cooking events and minutes cooking by fuel type and household fuel use type per day instead of aggregated 
```{r}
df_stove_on_day_long <- 
  df_events_stove_on_per_day %>%
  pivot_longer(cols = c("exclusive_biomass", "exclusive_lpg", "mixed_use"), names_to = "hh_fuel_use_type", values_to = "hh_type_yn") %>% 
  mutate(hh_fuel_use_type = str_replace(hh_fuel_use_type,"_", " ")) %>% 
  filter(hh_type_yn == "TRUE") 

cooking_event_hh_day <- 
  df_stove_on_day_long %>% 
  pivot_longer(
    cols = starts_with("cooking_events_with_"),
    names_to = c("fuel_type"),
   names_pattern = "cooking_events_with_(.*)",
    values_to = c("event_count")
  )  

stove_on_min_hh <- 
  df_stove_on_day_long %>% 
  pivot_longer(
    cols = starts_with("stove_on_min_"),
    names_to = c("fuel_type"),
   names_pattern = "stove_on_min_(.*)",
    values_to = c("minutes_cooking")
  )  %>% 
  filter(fuel_type != "pc_lpg", fuel_type != "pc_biomass")


#Create figures of data calculated above

cooking_event_hh_day %>% 
  ggplot(aes(x = event_count)) + 
  geom_histogram(aes(fill = fuel_type)) + 
    theme_bw() + 
  theme(legend.position = "none") +
  scale_fill_manual(values = c("red", "purple")) +
  labs(x = "Household Cooking Events (daily)", y = "Number of Daily Measurements") + 

  facet_grid(vars(hh_fuel_use_type)) 

stove_on_min_hh %>% 
  ggplot(aes(x = minutes_cooking)) + 
  geom_histogram(aes(fill = fuel_type)) + 
 theme_bw() +
  theme(legend.position = "none") +
    scale_fill_manual(values = c("red", "purple")) +
  labs(x = "Household Minutes Cooking (daily)", y = "Number of Daily Measurements") + 

  facet_grid(vars(hh_fuel_use_type))
```

## Willingness to Pay
```{r}
###############################################################################
#### Willingness-to-pay #####
###############################################################################

# lpg_willingness_to_pay
# buy_lpg_cost

survey_data %>%
  mutate(income_high_low = ifelse(income <= 3000, "income <= 3000 BDT", "income > 3000 BDT")) %>%
  group_by(income_high_low) %>%
  summarise(mean = mean(lpg_willingness_to_pay, na.rm = TRUE), median = median(lpg_willingness_to_pay, na.rm = TRUE))

survey_data %>%
  select(total_expenditures_30) %>%
  summary()

survey_data %>%
  select(income) %>%
  summary()

fig_lpg_willingness_to_pay <-
  survey_data %>%
  filter(timepoint ==  "endline") %>% #2021 dollars
  ggplot() +
  geom_boxplot(aes(y = lpg_willingness_to_pay / BDT_USD_exchange_rate_endline)) + 
  geom_hline(yintercept = 12.24, lty = 3, color = "blue") + 
  geom_hline(yintercept = 12.24 / 2, lty = 2, color = "blue") + 
  # Cost of cylinder in 2021 was $12.24 (https://docs.google.com/spreadsheets/d/19J8pPY7irwiH68Eh0UCEUe7m0tfD4N87/edit#gid=486556930)
  # Bangladesh LPG price as of 12 April 2021: https://www.dhakatribune.com/bangladesh/power-energy/2021/04/12/govt-lpg-price-reset-at-tk591-private-one-at-tk975
  theme_bw() + 
  labs(
    title = "Willingnes to Pay for 12 kg tank of LPG (2021 currency)",
    y  = "Willingness to pay (USD)"
  )

fig_lpg_willingness_to_pay_high_low_income <-
  survey_data %>%
  mutate(income_high_low = ifelse(income <= 3000, "income <= 3000 BDT", "income > 3000 BDT")) %>%
  filter(timepoint ==  "endline") %>% #2021 dollars
  ggplot() +
  geom_boxplot(aes(y = lpg_willingness_to_pay / BDT_USD_exchange_rate_endline)) + 
  geom_hline(yintercept = 12.24, lty = 3, color = "blue") + 
  # Cost of cylinder in 2021 was $12.24 (https://docs.google.com/spreadsheets/d/19J8pPY7irwiH68Eh0UCEUe7m0tfD4N87/edit#gid=486556930)
  # Bangladesh LPG price as of 12 April 2021: https://www.dhakatribune.com/bangladesh/power-energy/2021/04/12/govt-lpg-price-reset-at-tk591-private-one-at-tk975
  theme_bw() + 
  labs(
    title = "Willingnes to Pay for 12 kg tank of LPG (2021 currency)",
    y  = "Willingness to pay (USD)"
  ) +
  facet_grid( ~ income_high_low)

fig_lpg_willingness_to_pay_high_low_income

#average amount willing to pay for fuel
survey_data %>% 
  group_by(timepoint) %>% 
  summarise(
    median_wtp = median(lpg_willingness_to_pay, na.rm = TRUE),
      mean_wtp = mean(lpg_willingness_to_pay, na.rm = TRUE), 
    pc_income = mean(lpg_willingness_to_pay, na.rm = TRUE)/mean(income, na.rm = TRUE) * 100
  )

505/BDT_USD_exchange_rate_endline #Convert to USD

# Cost of cylinder in 2021 was $12.24 (https://docs.google.com/spreadsheets/d/19J8pPY7irwiH68Eh0UCEUe7m0tfD4N87/edit#gid=486556930)
# how many were willing to pay 50% of the cost?
# 12.24/2 * BDT_USD_exchange_rate_endline = 571.91 BDT

survey_data %>% 
  group_by(timepoint, study_arm) %>%
  count() 
# 931 respondents

survey_data %>%
  group_by(timepoint) %>%
  filter(lpg_willingness_to_pay > 571) %>%
  count()
# 388

# 388 / 931 = 41.67%

ggsave(
  here::here("6_figures", "fig_lpg_willingness_to_pay_high_low_income.tiff"),
  plot = last_plot(),
  scale = 1,
  height = 6,
  width = 10,
  units = "in",
  device = "tiff"
)
```




# Wages by Type 
The following code breaks down the income by group and also provides analysis comparing households between IOM and UNHCR camps.
We use the income data in the end of results and discussion section when describing 
```{r}
survey_data_study_arm_group <- 
  survey_data %>%
  filter(timepoint == "baseline") %>% 
  mutate(
    study_arm_group = case_when(
      camp_id %in% c("8W", "9", "10") ~ "Intervention IOM", 
      camp_id %in% c("8E", "18") ~ "Comparison IOM",
      camp_id %in% c("3","4","5") ~ "Comparison UNHCR", 
      .default = NA
    )) 


## Table if incomes by study arm group 
survey_data_study_arm_group %>% 
 # group_by(study_arm_overall) %>% 
  summarise_at(
    vars(income_wage_labor, income_cash_ngo, income_humanitarian_asst, income_selling_wood, income_skill_labor, income_own_business,income_abroad, income_farming), 
    list(
      mean = mean, 
      sd = sd,
      median = median),
      na.rm = TRUE
  ) 

survey_data_income_type <- 
survey_data_study_arm_group %>% 
  mutate(income_wage_labor_yn = if_else(income_wage_labor>0, 1, 0),
         income_cash_ngo_yn = if_else(income_cash_ngo>0, 1, 0),
         income_farming_yn = if_else(income_farming>0,1,0)) %>% 
  count(income_wage_labor_yn, income_cash_ngo_yn, income_farming_yn)

#Income by type 

#Farming
(108+11+152+3)/(494+437)

#Wage
(532+152+8+3)/(494+437)

#NGO
(86+11+8+3)/(494+437)
```



