---
title: "RF105B"
author: "Christopher LeBoa"
date: "2025-01-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


source(here::here("0_config.R"))
source(here::here("3_data_cleaning/1.5_define_vector_columns.R"))
source(here::here("5_analysis/Dif_in_dif_fxn.R")) 

#install.packages("geomtextpath")

library(tidyquant)
library(grid)
library(geomtextpath)
library(tidyverse)

#Survey file 
file_survey_data_base <- here::here("4_data/RohingyaFuel_survey_data_triple.rds")
file_survey_data_all <- here::here("4_data/RohingyaFuelMaster_survey_data_tidy.rds")

#PM Data file 
lpg_receive_date <- read_csv(here::here("2_data_raw/list_first_enrolled_lpg.csv"))
file_in_pm_data_clean_rds <- here::here("4_data/pm_data_clean.rds")


# Load input files
survey_data <- read_rds(file_survey_data_base)


#view(survey_data)
```

## Tables 1 and 2 Household demographics and loss to follow up 
The following code describes the household characteristics at baseline as well as prints out the differences of hh included and not included in the analysis (Tables 1 and 2 in the manuscript).

```{r}
rm(list = ls())
source(here::here("0_config.R")) # a config file that needs to be run to load neccesary packages 
source(here::here("3_data_cleaning/1.5_define_vector_columns.R")) # a file that defines which columns are 
## Chris
# source(here::here("1_config.R"))


# Parameters
file_survey_data_all <- here::here("4_data/RohingyaFuelMaster_survey_data_tidy.rds")
file_survey_data_base <- here::here("4_data/RohingyaFuel_survey_data_triple.rds")
file_survey_data_baseline <- here::here("4_data/RohingyaFuelMaster_survey_data_intervention_baseline.rds")


file_out_1 <- here::here("4_data/study_arm_camp_id_errors_220724.csv")
file_out_2 <- here::here("4_data/camp_block_id_errors_220724.csv")
camp_block_id_path <- here::here("4_data/camp_block_id.csv")
camp_block_sublock_id_path <- here::here("4_data/camp_block_sublock_id.csv")
camp_block_subblock_id_100_largest_path <- here::here("4_data/camp_block_subblock_id_100_largest.csv")


# Load input files

survey_data_all <- 
  read_rds(file_survey_data_all) %>%
  mutate(electricity = ifelse(electricity == 2, 1, 0)) ## Redefine the electricity variable 
survey_data <- 
  read_rds(file_survey_data_base)  %>%
  mutate(electricity = ifelse(electricity == 2, 1, 0))


survey_data_baseline <-  # select only baseline hh for table one 
  survey_data %>%
  filter(timepoint == "baseline")


survey_data %>%
  filter(timepoint == "baseline") %>%
  count(study_arm_overall)
# For each baseline, midline, endline there are 305 comparison hh and 486 intervention hh
# 791 hh with triplicate measures

survey_data_hh <-
  survey_data_all %>%
  mutate(
    study_arm_overall = 
      ordered(
        study_arm_overall,
        labels = c("comparison group", "intervention group")
      )
  ) %>%
  tabyl(timepoint, study_arm_overall)

survey_data_hh %>%
  kable(
    caption = "Number of households surveyed at each timepoint",
    booktabs = TRUE,
    digits = 1,
    align = c("l", "c", "C"),
    format = "latex"
  ) %>%
  kable_styling(latex_options = c("scale_down")) 



################################################################################
# Where are the hh located?
################################################################################
survey_data_all %>%
  tabyl(timepoint, camp_id, study_arm_overall)

survey_data %>%
  tabyl(timepoint, camp_id, study_arm_overall)

# study_arm_overall == intervention: camp_id %in% ("8w", "9", "10)
# study_arm_overall == comparison: camp_id %in% ("8E", "18", "3", "4", "5") # 3,4,5 are UNCHR; others are IOM


# There are a number of hh that appear to have the wrong study_arm assigned. 
# E.g. there are hh labeled as intervention that are in camps 3, 4, 5, 8E, which are all comparison camps

study_arm_error_all <-
  survey_data_all %>%
  mutate(
    anomolous = 
      case_when(
        timepoint == "endline" & study_arm_overall == "intervention" & camp_id == "3" ~ 1,
        timepoint == "endline" & study_arm_overall == "intervention" & camp_id == "4" ~ 1,
        timepoint == "endline" & study_arm_overall == "intervention" & camp_id == "5" ~ 1,
        timepoint == "endline" & study_arm_overall == "intervention" & camp_id == "8E" ~ 1,
        timepoint == "endline" & study_arm_overall == "comparison" & camp_id == "8W" ~ 1,
        timepoint == "endline" & study_arm_overall == "comparison" & camp_id == "9" ~ 1,
        timepoint == "endline" & study_arm_overall == "comparison" & camp_id == "10" ~ 1,
        TRUE ~ 0
      )
  ) %>%
  select(study_arm_overall, timepoint, camp_id, block_id, subblock_id, fcn_id, name_mahji, name_respondent, name_hh_head, target_child_name, anomolous) %>%
  filter(anomolous == 1) %>%
  select(-anomolous)

# write.csv(study_arm_error_all, file_out_1)

################################################################################
# Where are the hh located?
################################################################################
# Data Cleaning 

# Check for errors by examining all the data
camp_block_id_all <-
  survey_data_all %>%
  # tabyl(camp_id)
  # tabyl(camp_id, lpg_depots) # lpg_depots = "What LPG distribution center do you go to?
  tabyl(camp_id, block_id)
# unite(block_sub_block_id, c("block_id", "subblock_id")) %>%
# tabyl(camp_id, block_sub_block_id)

camp_block_id_all_errors <-
  survey_data_all %>%
  mutate(
    anomolous = 
      case_when(
        camp_id == "MOJIMULLAH" ~ 1,
        camp_id == "L18" ~ 1,
        camp_id == "G" ~ 1,
        camp_id == "10" & block_id == "e" ~ 1,
        camp_id == "4" & block_id == "b" ~ 1,
        camp_id == "8W" & block_id == "c" ~ 1,
        camp_id == "8W" & block_id == "g" ~ 1,
        camp_id == "9" & block_id == "b" ~ 1,
        camp_id == "9" & block_id == "c" ~ 1,
        camp_id == "9" & block_id == "i" ~ 1,
        camp_id == "9" & block_id == "c" ~ 1,
        TRUE ~ 0
      )
  ) %>%
  select(study_arm_overall, timepoint, camp_id, block_id, subblock_id, fcn_id, name_mahji, name_respondent, name_hh_head, target_child_name, anomolous) %>%
  filter(anomolous == 1) %>%
  select(-anomolous)



### Now only the paired data

camp_org <-
  survey_data %>%
  tabyl(timepoint, camp_id, org)

survey_data_all %>%
  tabyl(timepoint, camp_id, org)



camp_block_id <-
  survey_data %>%
  # tabyl(camp_id)
  # tabyl(camp_id, lpg_depots) # lpg_depots = "What LPG distribution center do you go to?
  tabyl(camp_id, block_id)
# unite(block_sub_block_id, c("block_id", "subblock_id")) %>%
# tabyl(camp_id, block_sub_block_id)

# write.csv(camp_block_id, camp_block_id_path)


camp_block_subblock_id <-
  survey_data %>%
  group_by(camp_id, block_id, subblock_id) %>% 
  count() %>%
  ungroup() %>%
  arrange(camp_id, block_id, subblock_id) 

camp_block_subblock_id_100_largest <-
  camp_block_subblock_id %>%
  arrange(desc(n)) %>%
  slice(1:100) %>%
  arrange(camp_id, block_id, subblock_id)



###############################################################################
# # Create dataset of households missing endline data to check for differential missingness 
###############################################################################
missing_from_endline_data  <- survey_data_all %>% filter(!hh_id %in% survey_data$hh_id)

###############################################################################
# # Create Table 2 datasets 
###############################################################################


survey_data_tab1 <-
  survey_data %>%
  filter(timepoint == "baseline") %>%
  select(
    c(
      "study_arm_overall",
      "hh_size", "hh_size_2mo_u5", "hh_size_u2mo",
      "hh_ppl_smoke",
      "electricity",
      "electric_fan_yn",
      "smartphone_yn", "mobile_phone_yn", # "radio_yn",   
      "portable_lamp_yn", "solar_lamp_yn", 
      
      "mattress_yn", "blanket_yn", "mosquito_net_yn",
      "umbrella_yn",
      "chair_bench_yn", "table_yn", # "almirah_wardrobe_show_case_yn",
      "shovel_yn", "sickle_yn", "weaving_tool_yn",
      "chicken_duck_pigeon_yn",
      "income",
      "spent_total_month",
      "debt",
      "target_child_sex",
      "target_child_months"
    )
  ) %>%
  # Convert to USD
  mutate(
    dropped_yn = "Participated in 3 surveys",
    income_USD = income / BDT_USD_exchange_rate_baseline,
    spent_total_month_USD = spent_total_month/ BDT_USD_exchange_rate_baseline,
    debt_USD = debt / BDT_USD_exchange_rate_baseline
  ) %>%
  select(-c(income, spent_total_month, debt)) %>%
  select(
    dropped_yn, study_arm_overall, target_child_sex, target_child_months,
    hh_size, hh_size_2mo_u5, hh_size_u2mo, hh_ppl_smoke,
    income_USD, spent_total_month_USD, debt_USD,
    everything()
  )



survey_data_tab1_IOM <- 
  survey_data %>%
  filter(camp_id %in% c("8E", "8W", "9", "10", "18"))	%>% 
  filter(timepoint == "baseline") %>%
  select(
    c(
      "study_arm_overall",
      "hh_size", "hh_size_2mo_u5", "hh_size_u2mo",
      "hh_ppl_smoke",
      "electricity",
      "electric_fan_yn",
      "smartphone_yn", "mobile_phone_yn", # "radio_yn",   
      "portable_lamp_yn", "solar_lamp_yn", 
      
      "mattress_yn", "blanket_yn", "mosquito_net_yn",
      "umbrella_yn",
      "chair_bench_yn", "table_yn", # "almirah_wardrobe_show_case_yn",
      "shovel_yn", "sickle_yn", "weaving_tool_yn",
      "chicken_duck_pigeon_yn",
      "income",
      "spent_total_month",
      "debt",
      "target_child_sex",
      "target_child_months"
    )
  ) %>%
  # Convert to USD
  mutate(
    dropped_yn = "Participated in 3 surveys",
    income_USD = income / BDT_USD_exchange_rate_baseline,
    spent_total_month_USD = spent_total_month/ BDT_USD_exchange_rate_baseline,
    debt_USD = debt / BDT_USD_exchange_rate_baseline
  ) %>%
  select(-c(income, spent_total_month, debt)) %>%
  select(
    dropped_yn, study_arm_overall, target_child_sex, target_child_months,
    hh_size, hh_size_2mo_u5, hh_size_u2mo, hh_ppl_smoke,
    income_USD, spent_total_month_USD, debt_USD,
    everything()
  )

## The following hh were missing from endline data collection -- we want to create separate table object to view their assets 
# and compare wealth to see if they are fundementally different than those included in study

missing_data_tab1 <-
  missing_from_endline_data %>%
  filter(timepoint == "baseline") %>%
  select(
    c(
      "study_arm_overall",
      "hh_size", "hh_size_2mo_u5", "hh_size_u2mo",
      "hh_ppl_smoke",
      "electricity",
      "electric_fan_yn",
      "smartphone_yn", "mobile_phone_yn", # "radio_yn",   
      "portable_lamp_yn", "solar_lamp_yn", 
      
      "mattress_yn", "blanket_yn", "mosquito_net_yn",
      "umbrella_yn",
      "chair_bench_yn", "table_yn", # "almirah_wardrobe_show_case_yn",
      "shovel_yn", "sickle_yn", "weaving_tool_yn",
      "chicken_duck_pigeon_yn",
      "income",
      "spent_total_month",
      "debt",
      "target_child_sex",
      "target_child_months"
    )
  ) %>%
  # Convert to USD
  mutate(
    dropped_yn = "Lost to attrition",
    income_USD = income/ BDT_USD_exchange_rate_baseline,
    spent_total_month_USD = spent_total_month/ BDT_USD_exchange_rate_baseline,
    debt_USD = debt / BDT_USD_exchange_rate_baseline
  ) %>%
  select(-c(income, spent_total_month, debt)) %>%
  select(
    dropped_yn, study_arm_overall, 
    hh_size, hh_size_2mo_u5, hh_size_u2mo, hh_ppl_smoke,
    income_USD, spent_total_month_USD, debt_USD,
    everything()
  )


###############################################################################
# # Define variables that will be used in the tables 
###############################################################################


### Define the vars for the table and specify which are factors
table1Vars <-
  c(
    "dropped_yn",
    "Study arm",
    "Target child is female", 
    "Age of target child (mo)",
    "Number of household members", 
    "Number of hh members 2-59 months",
    "Number of household members 0 to < 2 months",
    "Number of household members who smoke",
    "Monthly income [USD]",
    "Monthly expenditure [USD]",
    "Total debt [USD]",
    "House has solar electricity",
    "Has 1+ electric fan", 
    "Has 1+ smartphone", 
    "Has 1+ mobile phone",
    # "Has 1+ radio", # Note that no family had a radio so the table has radio_yn = 0
    "Has 1+ portable lamp",
    "Has 1+ solar lamp",
    "Has 1+ mattress", 
    "Has 1+ blanket",
    "Has 1+ mosquito net",
    "Has 1+ umbrella", 
    "Has 1+ chair/bench", 
    "Has 1+ table", 
    # "Has 1+ wardrobe", 
    "Has 1+ shovel", 
    "Has 1+ sickle", 
    "Has 1+ weaving tool", 
    "Has 1+ poultry"
    # "Has home garden",

  )


table1FactorVars <- 
  c(
    "House has solar electricity",
    "Has 1+ electric fan", 
    "Has 1+ smartphone", 
    "Has 1+ mobile phone",
    "Has 1+ radio",
    "Has 1+ portable lamp",
    "Has 1+ solar lamp",
    "Has 1+ mattress", 
    "Has 1+ blanket",
    "Has 1+ mosquito net",
    "Has 1+ umbrella", 
    "Has 1+ chair/bench", 
    "Has 1+ table", 
    # "Has 1+ wardrobe", # remove because only 3 total people have a wardrobe
    "Has 1+ shovel", 
    "Has 1+ sickle", 
    "Has 1+ weaving tool", 
    "Has 1+ poultry",
    "Target child is female"
  )


# Make full dataset
survey_all_tab1 <- 
  survey_data_tab1 %>% 
  bind_rows(missing_data_tab1) %>%
  mutate(dropped_yn = ordered(dropped_yn, levels = c("Participated in 3 surveys", "Lost to attrition")))

# Name datasets
names(survey_all_tab1) <- table1Vars

names(survey_data_tab1) <- table1Vars

names(survey_data_tab1_IOM) <- table1Vars

names(missing_data_tab1) <-  table1Vars

survey_all_tab1$`Monthly income [USD]`


###############################################################################
# # Create Table 1 Objects
###############################################################################


# Get average stats for all hh
tab1_baseline_no_study_arm <- 
  CreateTableOne(
    data = survey_data_tab1, 
    vars = table1Vars, factorVars = table1FactorVars
  )

tab1_baseline_no_study_arm


## Table 2 that was used for paper 

# Compare arms among hh used for analysis (participated in all three timepoints)
tab1_baseline <- 
  CreateTableOne(
    data = survey_data_tab1, 
    vars = table1Vars, factorVars = table1FactorVars, strata = "Study arm"
  )

tab1_baseline

# Compare only the hh that were in the IOM camps
tab1_baseline_IOM <- 
  CreateTableOne(
    data = survey_data_tab1_IOM, 
    vars = table1Vars, factorVars = table1FactorVars, strata = "Study arm"
  )

tab1_baseline_IOM

###############################################################################
# # Create table 1
###############################################################################

##table 1 code.... Comparing hh that were included in study compared to those dropped from study.
# Compare hh that dropped compared to those that did not
#Used to calculate the data that were missing by endline 
tab1_missing <-  
  CreateTableOne(data = missing_data_tab1, 
                 vars = table1Vars, factorVars = table1FactorVars, strata = "Study arm"
  )

tab1_comparison_dropped <-  
  CreateTableOne(data = survey_all_tab1 %>% filter(`Study arm` == "comparison"), 
                 vars = table1Vars, factorVars = table1FactorVars, strata = "dropped_yn"
  )

tab1_comparison_dropped

tab1_intervention_dropped <-  
  CreateTableOne(data = survey_all_tab1 %>% filter(`Study arm` == "intervention"), 
                 vars = table1Vars, factorVars = table1FactorVars, strata = "dropped_yn"
  )

tab1_intervention_dropped




###############################################################################
# # Save Table 1 datasets as CSVs
###############################################################################

tab1_baseline_no_study_arm_csv <- print(tab1_baseline_no_study_arm)
write.csv(tab1_baseline_no_study_arm_csv, "tab1_baseline_no_study_arm.csv")

tab1_baseline_csv <- print(tab1_baseline)
write.csv(tab1_baseline_csv, "tab1_baseline.csv")

tab1_comparison_dropped_csv <- print(tab1_comparison_dropped)
write.csv(tab1_comparison_dropped_csv, "tab1_comparison_dropped.csv")

tab1_intervention_dropped_csv <- print(tab1_intervention_dropped)
write.csv(tab1_intervention_dropped_csv, "tab1_intervention_dropped.csv")
```

## Who Collected Fuel 
```{r}
# for fuel_collection_who, the denominator is hh that EVER collected type X fuel
fuel_collection_who_baseline <- c()
for (fuel in c("gather_scraps", "collect_wood", "receive_wood", "buy_wood", "receive_lpg", "buy_lpg", "receive_crh", "buy_crh")){
  for (person in c("w", "g", "m", "b")){
    fuel_collection_who_baseline <- c(fuel_collection_who_baseline, paste(fuel, person, sep = "_"))
  }
}


## Intervention arm at baseline



fuel_procurement_who_baseline_intervention <-
  survey_data %>% 
  filter(timepoint == "baseline") %>%
  filter(study_arm_overall == "intervention") %>%
  select(
    fcn_id,
    study_arm_overall, timepoint, all_of(fuel_collection_who_baseline)
  ) %>%
  pivot_longer( 
    cols = c(
      all_of(fuel_collection_who_baseline)
    ),
    names_to = "vars",
    values_to = "collected_yn"
  ) %>%
  mutate(collected_yn = ifelse(collected_yn == 0, NA, collected_yn)) %>%
  separate(vars, into = c("procurement", "fuel", "demographic"), sep = "_") %>%
  unite("fuel_type", c("procurement", "fuel"), sep = "_") %>%
  mutate(counter = 1) %>%
  select(-study_arm_overall, -timepoint) %>%
  group_by(fuel_type, demographic) %>%
  summarise(
    n = sum(collected_yn, na.rm = TRUE),
    pc = n / sum(counter) * 100
  ) 



print(fuel_procurement_who_baseline_intervention)  
```

## Expenditures Plot 

```{r expenditures plot}

fcn_id_purchased_fuel_30_endline <-
  survey_data %>%
  filter(
    (fuel_30_buy_wood == 1 | fuel_30_buy_lpg == 1 | fuel_30_buy_crh == 1) & timepoint == "endline"
  ) %>%
  pull(fcn_id) %>% unique() # had to use pull to get a vector instead of select, which kept a tibble

fcn_id_lpg_sufficiency_endline <-
  survey_data %>%
  filter(
    (lpg_sufficiency == "LPG sufficent") & timepoint == "endline"
  ) %>%
  pull(fcn_id) %>% unique() # had to use pull to get a vector instead of select, which kept a tibble


monthly_expenditures_base <- 
  survey_data %>%
  select(timepoint, study_arm_overall, fcn_id, fuel_30_buy_wood, fuel_30_buy_lpg, fuel_30_buy_crh, spent_total_month, all_of(spent_monthly_vars)) %>%
  select(-c(fuel_30_buy_wood, fuel_30_buy_lpg, fuel_30_buy_crh)) %>% #
  mutate(
    # fuel_30_purchased_fuel = ifelse(fuel_30_buy_wood == 1 | fuel_30_buy_lpg == 1 | fuel_30_buy_crh == 1, 1, 0),
    # labels all the hh that purchased fuel at endline, regardless of whether the purchased at baseline or not (arm is still captured in study_group_overall color)
    fuel_30_purchased_fuel_endline = ifelse(fcn_id %in% fcn_id_purchased_fuel_30_endline, 1, 0),
    lpg_sufficiency_endline = ifelse(fcn_id %in% fcn_id_lpg_sufficiency_endline, "lpg_sufficient_endline", "lpg_insufficient_endline")
  ) %>%
  gather(-timepoint, -study_arm_overall, -fcn_id, -fuel_30_purchased_fuel_endline, -lpg_sufficiency_endline, key = "category", value = "expenditure") %>% # fuel_30_purchased_fuel
  # filter(category %notin% 
  # 			 	c(
  # 			 		"spent_total_month_with_6mo_monthly",
  # 			 		"buy_lpg_cost", 
  # 			 		"spent_tobacco_pan", 
  # 			 		"spent_clothing_month", 
  # 			 		"spent_medical_month", 
  # 			 		"spent_debt_month",
  # 			 		
  # 			 		"spent_transport", "spent_shelter_month", 
  # 			 		"spent_celebrations_month",   "spent_education_month", 
# 			 		"spent_phone",  "spent_hygiene",
# 			 		"spent_hh_items", "spent_other", "spent_other_month"
# 			 	)
# ) %>%
mutate(
  category = as.factor(category)
) %>%
  ungroup()

monthly_expenditures_summary <-
  monthly_expenditures_base %>%
  group_by(timepoint, study_arm_overall,category) %>% #  lpg_sufficiency_endline
  summarise(
    n = n(),
    income_mean = mean(expenditure, na.rm = TRUE),
    sd = sd(expenditure, na.rm = TRUE),
    se_expenditure = sd(expenditure, na.rm = TRUE) / sqrt(n())
    ) %>% 
    mutate(
    lower_ci =  income_mean - 1.96 * se_expenditure,
    upper_ci = income_mean + 1.96 * se_expenditure
  )
  

monthly_expenditures_summary

supp.labs <- c("Firewood spending (per month)", "Food spending (per month)")
names(supp.labs) <- c("buy_wood_cost", "spent_food")

fig_monthly_expenditures <-	
  monthly_expenditures_base %>%
  mutate(
    lpg_sufficiency_endline = ordered(lpg_sufficiency_endline, levels = c("lpg_sufficient_endline", "lpg_insufficient_endline"), labels = c("LPG sufficient \nat endline", "LPG insufficient \nat endline")),
    fuel_30_purchased_fuel_endline = 
      # factor(fuel_30_purchased_fuel, levels = c(0, 1), labels = c("Did NOT \n buy fuel \nin past 30 days", "Bought fuel \nin past 30 days ")),
      factor(fuel_30_purchased_fuel_endline, levels = c(0, 1), labels = c("Did NOT \nbuy fuel \nin 30 days before endline", "Bought fuel \nin 30 days before endline")),
    category_label = 
      ordered(
        category,
        levels = c(
          "spent_total_month_with_6mo_monthly",
          "spent_food",
          "buy_wood_cost",
          "buy_lpg_cost",
          "spent_tobacco_pan",
          "spent_clothing_month",
          "spent_debt_month", # There is one value of 50,000 (intervention, midline) that is pulling up the average a lot
          "spent_medical_month",
          "spent_transport", "spent_shelter_month",
          "spent_celebrations_month",   "spent_education_month",
          "spent_phone",  "spent_hygiene",
          "spent_hh_items", "spent_other_month"
        ),
        # labels = 
        # 	c(
        # 		"total", # all expenditures
        # 		"  wood  ", 
        # 		"  food  "#,  
        # 		"other", #"   lpg   ",
        # 		"other", #"pan/\ntobacco",
        # 		"other", #"clothing",
        # 		"other", #"medical",
        # 		"other", # "paying \ndebt",
        # 
        # 		"other", "other",
        # 		"other", "other",
        # 		"other", "other",
        # 		"other", "other"
        # 	)
        labels =
          c(
            "total", # all expenditures
            "  food  ",
            "  wood  ",
            "   lpg   ",
            "pan/\ntobacco",
            "clothing",
            "paying \ndebt",
            "other", # "medical",
            "other", "other", # "transport", "shelter",
            "other", "other",
            "other", "other",
            "other", "other"
          )
      )
  ) %>%
  ungroup() %>%
  group_by(timepoint, study_arm_overall, category_label) %>% #  lpg_sufficiency_endline
  drop_na(category_label) %>% 
  ggplot(aes(x = timepoint, y = expenditure / BDT_USD_exchange_rate_endline, color = study_arm_overall, shape = timepoint, group = study_arm_overall)) +
  # geom_boxplot() +
  # geom_point(size = 3) + # position = position_dodge(width = 0.2),
  stat_summary(fun = "mean", geom = "line", size = 1) +
  stat_summary(fun = "mean", geom = "point", size = 2) +
  stat_summary(
    fun.data = "mean_cl_boot",
    geom = "linerange" #,
    # position = position_dodge(width = 0.2
  ) +
  
  # ggpubr::stat_compare_means(
  # 	# aes(group = timepoint),
  # 	label = "p.signif", #"p.signif" # symnum.args <- list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), symbols = c("****", "***", "**", "*", "ns"))
  # 	# label = "p.format",
  # 	method = "wilcox.test",
  # 	paired = FALSE, # not paired because this is endline only
  # 	# label.y = 18,
  # 	hide.ns = TRUE#,
  # 	# ref.group = ".all."
  # 	# show.legend = TRUE # doesn't show the legend of stas?
# ) +
scale_y_continuous(breaks = seq(0, 70, 2), minor_breaks = seq(0, 70, 1), labels = scales::label_dollar()) +
  scale_color_manual(
    name = "Study_arm",
    breaks = c("intervention", "comparison"),
    # labels = c("Pre-intervention", "Intervention", "Outdoor"),
    labels = c("Intervention", "Comparison"),
    values = c("#138b87",  "#430154"),
    # values = c("#7570b3",  "#d95f02", "#1b9e77")
  ) +
  # viridis::scale_fill_viridis(
  # 	discrete = TRUE,
  # 	end = 2/3
  # ) +
  
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 0, hjust = 1, ),
    #axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  ) + 
  guides(
    color = guide_legend(title = "Study arm"),
    shape = guide_legend(title = "Timepoint")
  ) +
  labs(
    title = "Monthly household expenditure",
    x = "Expenditure category",
    y = "Monthly expenditure (USD)"
  ) + 
  # facet_wrap(~ category_label, ncol = 3) #, scales = "free_y"
  facet_grid(. ~ category_label, scales = "free_y") 
# facet_grid( ~ category, labeller = labeller(category = supp.labs)) # + # these only work with facet_wrap: , strip.position = "bottom", scales = "free_y"
# facet_grid(lpg_sufficiency_endline ~ category) + # fuel_30_purchased_fuel_endline
# coord_cartesian(ylim = c(0, 40))


fig_monthly_expenditures

ggsave(
  fig_monthly_expenditures,
  filename = here::here("/Users/christopherleboa/Library/CloudStorage/GoogleDrive-cleboa@berkeley.edu/.shortcut-targets-by-id/1HGzyHFSinRs5Jh4j7SZsJyb2KPXJ8mh8/Rohingya/Rohingya research - Fuel/Manuscripts/RF105_Indoor air pollution and non-health impacts/RF105B/fig2_monthly_expenditures.png"),
  width = 10,
  height = 6
)


model_data <- survey_data %>% filter(timepoint %in% c("baseline", "endline"))
model_data <- survey_data %>% filter(timepoint %in% c("baseline", "midline"))

dind_fxn(c("spent_food", "buy_wood_cost"), model_data)
```



## Food Security Results 

In this section we analyze the FCS scores and the HDSS scores reported by households 

```{r}
food_dataset <-
	survey_data %>%
	select(
		study_arm_overall,
		timepoint,
		fcn_id, 
		camp_id,
		block_id,
		subblock_id,
		hh_size,
		contains("food"), 
		contains("rice"),
		contains("bread"),
		contains("corn"),
		contains("potatoes"),
		contains("lentils"),
		contains("dairy"),
		contains("veggies"),
		contains("fruit"),
		contains("eggs"),
		contains("fish"),
		contains("poultry"),
		contains("goat_sheep"),
		contains("beef"),
		contains("oil"),
		contains("sugar")
	) %>%
	select(
		-c(
			contains("corner"),
			contains("boil")
		)
	)

FCS_HDDS_data <-
	survey_data %>%
	select(
		study_arm_overall, timepoint, fcn_id, camp_id, block_id, subblock_id, SubmissionDate,timepoint_num, study_arm_overall_num,
		all_of(food_types_consumed_vars), contains("food_consump_adult_day")
	) %>%
	rowwise() %>%
	mutate(
		staple = 
			ifelse(
				sum(rice_adults_week, bread_adults_week, corn_adults_week, potatoes_adults_week, na.rm = TRUE) >= 7, 
				7, 
				sum(rice_adults_week, bread_adults_week, corn_adults_week, potatoes_adults_week, na.rm = TRUE)
			),
		pulses = 
			ifelse(
				lentils_adults_week >= 7, 
				7, 
				lentils_adults_week
			),
		veggies = 
			ifelse(
				veggies_adults_week >= 7, 
				7, 
				veggies_adults_week
			),
		fruit = 
			ifelse(
				fruit_adults_week >= 7, 
				7, 
				fruit_adults_week
			),
		meat_fish = 
			ifelse(
				sum(eggs_adults_week, fish_adults_week, poultry_adults_week, goat_sheep_adults_week, beef_adults_week, na.rm = TRUE) >= 7, 
				7, 
				sum(eggs_adults_week, fish_adults_week, poultry_adults_week, goat_sheep_adults_week, beef_adults_week, na.rm = TRUE)
			),
		dairy = 
			ifelse(
				dairy_adults_week >= 7, 
				7, 
				dairy_adults_week
			),
		sugar = 
			ifelse(
				sugar_adults_week >= 7, 
				7, 
				sugar_adults_week
			),
		oil = 
			ifelse(
				oil_adults_week >= 7, 
				7, 
				oil_adults_week
			),
		# [food_groups]	1	rice
		# [food_groups]	2	bread
		# [food_groups]	3	corn
		# [food_groups]	4	potatoes
		# [food_groups]	5	lentils
		# [food_groups]	6	eggs
		# [food_groups]	7	dairy
		# [food_groups]	8	vegetables
		# [food_groups]	9	fruit
		# [food_groups]	10	fish
		# [food_groups]	11	poultry
		# [food_groups]	12	goat
		# [food_groups]	13	beef
		# [food_groups]	14	oil
		# [food_groups]	15	sugar
		cereals_yn = ifelse(sum(food_consump_adult_day.1, food_consump_adult_day.2, food_consump_adult_day.3, na.rm = TRUE) > 0, 1, 0),
		tubers_yn = ifelse(food_consump_adult_day.4 > 0, 1, 0),
		veggies_yn = ifelse(food_consump_adult_day.8 > 0, 1, 0),
		fruit_yn = ifelse(food_consump_adult_day.9 > 0, 1, 0),
		meat_yn = ifelse(sum(food_consump_adult_day.11, food_consump_adult_day.12, food_consump_adult_day.13, na.rm = TRUE) > 0, 1, 0),
		eggs_yn = ifelse(food_consump_adult_day.6 > 0, 1, 0),
		fish_yn = ifelse(food_consump_adult_day.10 > 0, 1, 0),
		pulses_yn = ifelse(food_consump_adult_day.5 > 0, 1, 0),
		milk_yn = ifelse(food_consump_adult_day.7 > 0, 1, 0),
		oil_yn = ifelse(food_consump_adult_day.14 > 0, 1, 0),
		sugar_yn = ifelse(food_consump_adult_day.15 > 0, 1, 0),
		# did not ask about miscellaneous
		hdds_no_misc = sum(cereals_yn, tubers_yn, veggies_yn, fruit_yn, meat_yn, eggs_yn, fish_yn, pulses_yn, milk_yn, oil_yn, sugar_yn),
		hdds_assume_misc_1 = hdds_no_misc + 1,
		staple_weight = staple * 2,
		pulses_weight = pulses * 3,
		veggies_weight = veggies * 1,
		fruit_weight = fruit * 1, 
		meat_fish_weight = meat_fish * 4,
		milk_weight = dairy * 4,
		sugar_weight = sugar * 0.5, 
		oil_weight = oil * 0.5,
		# did not ask about condiments
		fcs = sum(staple_weight, pulses_weight, veggies_weight, fruit_weight, meat_fish_weight, milk_weight, sugar_weight, oil_weight),
		fcs_category = 
			case_when(
				fcs <= 21 ~ "poor",
				fcs >= 21.5 & fcs <= 35 ~ "borderline",
				fcs > 35 ~ "acceptable"
			),
		fcs_binary = if_else(fcs<=35, 1, 0),
		fcs_category = ordered(fcs_category, levels = c("poor", "borderline", "acceptable"))
	) %>%
	ungroup()

## We did not have the HDDS scores at baseline -- added them later
FCS_HDDS_data %>% 
  group_by(timepoint, study_arm_overall) %>% 
  summarise(
    mean_hdds = mean(hdds_no_misc, na.rm = TRUE), 
    se_hdds = sd(hdds_no_misc, na.rm = TRUE) / sqrt(n())
    ) %>% 
    mutate(
    lower_ci = mean_hdds- 1.96 * se_hdds,
    upper_ci = mean_hdds + 1.96 * se_hdds
  )
  
FCS_HDDS_data %>% 
  group_by(timepoint, study_arm_overall) %>% 
  summarise(
    mean_fcs = mean(fcs, na.rm = TRUE),
    mean_fcs_binary = sum(fcs_binary, na.rm = TRUE) / n() * 100)


#Output dataset to analyze using XGBOOST) 
fcs_output <- FCS_HDDS_data %>% 
  select(fcn_id, timepoint, fcs_binary, study_arm_overall, fcs) %>% 
  write_rds(here::here("4_data/RohingyaFuel_survey_data_fcs.rds"))


plastics <- 
	FCS_HDDS_data %>% 
	filter(timepoint %in% c("baseline", "endline"))

plastics <- 
	FCS_HDDS_data %>% 
	filter(timepoint %in% c("baseline", "midline"))
	
dind_fxn(data = plastics, "fcs")

dind_fxn(data = plastics, "fcs_binary")



```

## PM Results 
```{r}

# https://cran.r-project.org/web/packages/MakefileR/vignettes/demo.html
# 
# Outdoor monitor placement 
# All the Outdoor monitors at the same place and same school at Intervention but
#Pre-Intervention At 2 Mosque(camp 8W and camp 10). All the Baseline outdoor monitor
#and midline outdoor monitor setup as the same location.Note that no different 
#location in school and Mosque. Always had collected one location PM 2.5 data.




#Input Files



### Output Files RDS 



pm_data_min_rds <- here::here("4_data/pm_data_min.rds")

pm_data_nearest_min_rds <- here::here("4_data/pm_data_nearest_min.rds")

pm_data_hour_rds <- here::here("4_data/pm_data_hour.rds")

pm_data_nearest_hour_rds <- here::here("4_data/pm_data_nearest_hour.rds")

pm_data_min_csv <- here::here("4_data/pm_data_min.csv")

pm_data_nearest_min_csv <- here::here("4_data/pm_data_nearest_min.csv")

pm_data_hour_csv <- here::here("4_data/pm_data_hour.csv")

pm_data_nearest_hour_csv <- here::here("4_data/pm_data_nearest_hour.csv")


# Manually move the compiled file into the raw folder of the project
all_pm_data_path_rds_project <- here::here("2_data_raw/PATS+_Data_20220703.rds")

file_pm_data_hour_av_by_hh <- here::here("4_data/pm_data_hour_av_by_hh.rds")
# file_HAPEX_data_base <- here::here("2_data_raw", "HAPEX_Data_20220703.rds")


##############################################################################
# Read file
##############################################################################

pm_data_full <- 
  read_rds(file_in_pm_data_clean_rds) %>% #Read in data file of all PM2.5 data 
	mutate(date = as_date(date)) 

#To create teh fcn_id from the hh id we pull the last digits of the hh id 

pm_data_full <- pm_data_full %>% 	mutate(fcn_id = as.numeric(str_extract(hh_id, ".{6}$") ))

pm_data_full <-  
  pm_data_full %>% left_join(lpg_receive_date, by = "fcn_id") #bind data to when hh starteds receiving lpg


###### Edit dataset to add in the variable for who was a recent receipt 
pm_data_full <- 
  pm_data_full %>%  
  mutate(date = as.Date(dateTime)) %>% 
  #filter(date < first_receive_lpg_ymd ).             #This adds in a variable to determine LPG receipt from
  mutate(
    lpg_enrolled_and_receiving = case_when(
    date < first_receive_lpg_ymd ~ "not yet receiving LPG through distribution program", 
    date < "2020-04-15" & date > first_receive_lpg_ymd ~ "recent receipt lpg", 
    date > "2020-04-15" & date < "2021-01-15" ~ "midline", 
    date > "2022-01-15" ~ "endline", 
    .default = NA, 
    ), 
    study_arm_update = case_when(
      study_arm == "intervention" & lpg_enrolled_and_receiving == "not yet receiving LPG through distribution program" ~ "pre-receipt lpg", 
      study_arm == "intervention" & lpg_enrolled_and_receiving == "recent receipt lpg" ~ "recent receipt lpg", 
      study_arm == "intervention" & is.na(lpg_enrolled_and_receiving)  ~ "unknown receipt lpg", 
      .default = study_arm
    ))

################################################################################
## QC:  Detection of high monitor values
################################################################################
pm_data_full %>%
	filter(timepoint == "baseline") %>%
	filter(study_arm == "intervention") %>%
	ggplot(aes(dateTime, PM_Estimate, color = hh_id_note)) + # aes(nearest_min, PM_Estimate, color = hh_id_note)
	# geom_point(na.rm = TRUE) +
	geom_line() + 
	# 	geom_text(aes(label = hh_id, x = as_datetime(Inf), y = PM_Estimate), hjust = -.1) + # how do I do x = Inf for datetime
	# 	scale_colour_discrete(guide = 'none')  +    
	#   theme(plot.margin = unit(c(1,3,1,1), "lines")) +
	scale_x_datetime(labels = scales::date_format("%Y-%m-%d")) + # "%Y-%m-%d %H:%M" # labels = scales::date_format("%H:%M")
	theme(
		legend.position = "none"
	) + 		
	labs(
		title = "midline_intervention"
	) +
	facet_wrap(date ~ ., scales = "free")

pm_data_high_monitors <-
	pm_data_full %>%
	filter(PM_Estimate > 3000) %>%
	select(timepoint, study_arm, hh_id) %>%
	unique()

pm_data_very_high_monitors <-
	pm_data_full %>%
	filter(PM_Estimate > 10000) %>%
	select(timepoint, study_arm, hh_id) %>%
	unique()


###############################################################
## Create overall analysis dataset 
#############################################################

# drop the endline data that was during the cold season --> we'll analyze this separately
pm_data <-
	pm_data_full %>%
	filter(
	  !(date > as_date("2022-02-02") & date < as_date("2022-03-24")),
	  note %notin% c("qc", "insufficient data")
	  ) %>% 
  mutate(PM_Estimate = if_else(PM_Estimate < 10, 10, PM_Estimate )) #Replacing all # below the lower detection limit with 10 



# uses the actual minute (always rounds down to the nearest min)
pm_data_min <-
	pm_data %>%
	filter(note != "insufficient data") %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note, dateTime_min) %>%
	summarise_at(
		vars(PM_Estimate),
		list(mean),
		na.rm = TRUE
	) %>%
	ungroup()

# rounds to the nearest min (up or down)
pm_data_nearest_min <-
	pm_data %>%
	filter(note != "insufficient data") %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note, nearest_min) %>% # collapses all if they have the same date label, so I hope they don't!
	summarise_at(
		vars(PM_Estimate),
		list(mean),
		na.rm = TRUE
	) %>%
	ungroup()


# uses the actual hour (always rounds down to the nearest hour)
pm_data_hour <-
	pm_data %>%
	filter(note != "insufficient data") %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note, dateTime_hour) %>%
	summarise_at(
		vars(PM_Estimate),
		list(mean),
		na.rm = TRUE
	) %>%
	ungroup() %>%
	mutate(
		over_100 = if_else(PM_Estimate > 100, 1, 0),
		over_500 = if_else(PM_Estimate > 500, 1, 0)
	)

# rounds to the nearest hour (up or down)
pm_data_nearest_hour <-
	pm_data %>%
	filter(note != "insufficient data") %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note, nearest_hour) %>%
	summarise_at(
		vars(PM_Estimate),
		list(mean),
		na.rm = TRUE
	) %>%
	ungroup() %>%
	mutate(
		over_100 = if_else(PM_Estimate > 100, 1, 0),
		over_500 = if_else(PM_Estimate > 500, 1, 0)
	)


# Create variable of average weighted PM data per hh 
pm_data_household <- 
  	pm_data %>%
	filter(note != "insufficient data") %>%
	group_by(timepoint, study_arm, note, hh_id) %>%
	summarise_at(
		vars(PM_Estimate),
		list(mean),
		na.rm = TRUE
	) %>%
	ungroup() %>%
	mutate(
	  child_av_bl = 20.1/24 *PM_Estimate + 3.9/24 * 31,
	  child_av_el = 20.1/24 *PM_Estimate + 3.9/24 * 13, 
	  resp_av_bl = 22.7/24 *PM_Estimate + 1.3/24* 31, 
	  resp_av_el = 22.7/24 *PM_Estimate + 1.3/24* 31, 
	  ch_gt_65_bl = ifelse(child_av_bl >65, 1, 0), 
	  ch_gt_35_bl = ifelse(child_av_bl >35, 1, 0), 
	  ch_gt_65_el = ifelse(child_av_el >65, 1, 0), 
	  ch_gt_35_el = ifelse(child_av_el >35, 1, 0), 
	  resp_gt_65_bl = ifelse(resp_av_bl >65, 1, 0), 
	  resp_gt_35_bl = ifelse(resp_av_bl >35, 1, 0), 
	   resp_gt_65_el = ifelse(resp_av_el >65, 1, 0), 
	  resp_gt_35_el = ifelse(resp_av_el >35, 1, 0)
	) %>% 
  group_by(timepoint, study_arm) %>% 
  summarise(
    sum(ch_gt_65_bl) / n(), 
    sum(ch_gt_35_bl) / n(), 
    sum(ch_gt_65_el) / n(), 
    sum(ch_gt_35_el) / n(), 
    sum(resp_gt_65_bl) / n(), 
    sum(resp_gt_35_bl) / n(), 
    sum(resp_gt_65_el) / n(), 
    sum(resp_gt_35_el) / n())
    
  

###############################################################################
## Save data
###############################################################################
# 
# pm_data_min %>%
# 	saveRDS(pm_data_min_rds)
# 
# pm_data_nearest_min %>%
# 	saveRDS(pm_data_nearest_min_rds)
# 
# pm_data_hour %>%
# 	saveRDS(pm_data_hour_rds)

# pm_data_nearest_hour %>%
# 	saveRDS(pm_data_nearest_hour_rds)

# write.csv(pm_data_min, pm_data_min_csv)
# 
# write.csv(pm_data_nearest_min, pm_data_nearest_min_csv)
# 
# write.csv(pm_data_hour, pm_data_hour_csv)
# 
# write.csv(pm_data_nearest_hour, pm_data_nearest_hour_csv)


#############################################
#Figure of PM data 
##############################################

# Step 1: Aggregate data by 60-minute intervals and calculate means and standard errors
pm_summary <- 
  pm_data %>%
  mutate(nearest_min_60 = floor_date(nearest_min, "60 minutes")) %>%  # Round to nearest 10-minute interval
  group_by(timepoint, study_arm, nearest_min_60) %>%
  summarise(
    PM_Estimate_av = mean(PM_Estimate, na.rm = TRUE),
    count = n_distinct(hh_id),
    se_pm_estimate = sd(PM_Estimate, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  ) %>%
  mutate(
    lower_ci = PM_Estimate_av - 1.96 * se_pm_estimate,
    upper_ci = PM_Estimate_av + 1.96 * se_pm_estimate
  )

pm_data %>% 
  filter(timepoint != "baseline" & study_arm != "intervention") %>% 
  mutate(nearest_min_60 = floor_date(nearest_min, "60 minutes")) %>%  # Round to nearest 10-minute interval
  summarise(
    PM_Estimate_av = mean(PM_Estimate, na.rm = TRUE),
    count = n_distinct(hh_id),
    se_pm_estimate = sd(PM_Estimate, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  ) %>%
  mutate(
    lower_ci = PM_Estimate_av - 1.96 * se_pm_estimate,
    upper_ci = PM_Estimate_av + 1.96 * se_pm_estimate
  )
  

# Step 2: Create the plot with geom_smooth and error bars
fig_pm_day <- 
  ggplot(pm_summary, aes(x = nearest_min_60, y = PM_Estimate_av, group = study_arm)) +
  geom_line(aes(color = study_arm), linewidth = 1) +  # Smooth the line without showing its own confidence interval
  # geom_point(alpha = 0.5) + # Optional: Uncomment if you'd like points on the graph
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci, fill = study_arm), alpha = 0.4) +
  
  # Horizontal reference lines
  geom_hline(yintercept = 35, color = "red", linetype = 2) + #WHO interim goal #3
  geom_hline(yintercept = 65, color = "black", linetype = 4) + #BD air pollution goal 
 # geom_hline(yintercept = 500, color = "black", linetype = 6) +
  
  # Improved x-axis readability
  scale_x_datetime(
    labels = scales::date_format("%H:%M", tz = "Asia/Dhaka"),  # Format to show hour and minute
    breaks = scales::date_breaks("6 hours"),                   # Increase interval between labels
    expand = c(0, 0)
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +  # Rotate labels for readability
  
  # Y-axis scaling
  scale_y_log10(breaks = c(10, 25, 100, 300, 500, 1000), labels = c(10, 25, 100, 300, 500, 1000)) +
  annotation_logticks() +
  
  # Labels and theme
  labs(
    title = "PM2.5 measurement by hour of the day",
    x = "Time",
    y = "PM2.5 (ug/m3)"
  ) +
  theme_classic() +
  theme(
    legend.background = element_blank(),
    panel.spacing = unit(2, "lines"),
    panel.border = element_rect(color = "black", fill = NA),  # Adds a black border to each facet panel
    strip.background = element_blank()   
  ) +
  theme(
  axis.text.x = element_text(size = 9, angle = 45, hjust = 1),
  axis.title.x = element_text(size = 11),
  axis.title.y = element_text(size = 10),
  axis.text.y = element_text(size = 10),
  legend.text = element_text(size = 11),
  legend.title = element_text(size = 12),
  plot.margin = margin(10, 10, 10, 10)
) +
 
  
  # Faceting by timepoint
  facet_wrap(~ timepoint)

fig_pm_day 
# Export the plot with increased resolution and size
ggexport(
  plot = fig_pm_day,
  filename = here::here("6_figures", "fig_pm_time_of_day.png"),
  width = 2100, height = 2100, res = 300
)

ggsave(
  fig_pm_day,
  filename = here::here("6_figures", "fig_pm_time_of_day.png"),
  width = 7,
  height = 7,
  dpi = 300
)


## Compare distributions at endline 
pm_data %>% 
  filter(timepoint == "endline", study_arm != "outdoor") %>% 
  wilcox.test(PM_Estimate ~ as_factor(study_arm), data = ., exact = FALSE)


```



## PM 2.5 Weighted Results
```{r}
#pm2.5 data 
pm_data <- here::here("4_data/pm_data_clean.rds")



pm_data_hour %>% 
  count(timepoint)

#paired survey data 

file_survey_data_base <- here::here("4_data/RohingyaFuel_survey_data_triple.rds")
#This file is the paired survey data containing survey responses on a hh level

survey_data <- read_rds(file_survey_data_base)

#individual level midline survey data (at basline asked for single response per household. At midline asked for a response per hh member)
all_files <- 
  list.files(path = here::here("2_data_raw"), pattern = ".csv", full.names = TRUE)
#finds all files from raw folder with .csv pattern


selected_files <- 
  all_files[str_detect(all_files, "location")]
#selects files with location in the name

midline_location_repeat <- 
  selected_files %>% 
  map_dfr(read_csv, col_types = cols(.default = "c", hours_inside = "d", hours_outside = "d"))
#reads in all selected files 

 file_location_out <- here::here("4_data/weighted_pm2.5_av.csv")
 
 
 all_files <- 
  list.files(path = here::here("2_data_raw/survey_endline_with_review"), pattern = ".csv", full.names = TRUE)
#finds all files from raw folder with .csv pattern


selected_files <- 
  all_files[str_detect(all_files, "hh_members")]
#selects files with location in the name

endline_location_repeat <- 
  selected_files %>% 
  map_dfr(read_csv, col_types = cols(.default = "c", hours_inside = "d", hours_outside = "d"))
#reads in all selected files 



 file_location_out <- here::here("4_data/weighted_pm2.5_av.csv")

```

##Clean data 
```{r}
#Midline 
midline_location_clean <- 
midline_location_repeat %>% 
  mutate(
       hours_inside = if_else(is.na(hours_inside) == TRUE, 24 - hours_outside, hours_inside), 
       hours_outside = if_else(is.na(hours_outside) == TRUE, 24 - hours_inside, hours_outside)#, 
  ) #Some versions had only hours inside and the endline had only hours outside so setting them all to have both with inside + outside == 24

#Endline 
endline_location_clean <- 
endline_location_repeat %>% 
  mutate(
       hours_inside = 24 - hours_outside, 
       hours_outside = hours_outside 
  )

table(survey_data$study_arm)

survey_data_interest <- 
  survey_data %>% 
  select(KEY, name_respondent, target_child_name, hh_id, study_arm, timepoint, starttime)
#from overall survey data find columns needed to specify hh members at midline  
```

## Join data 
```{r}
joined_data <- 
  midline_location_clean %>%
  right_join(survey_data_interest, (.by = c("PARENT_KEY"= "KEY")))

joined_data_end <- 
  endline_location_clean %>%
  right_join(survey_data_interest, (.by = c("PARENT_KEY"= "KEY")))

survey_data_interest %>% 
  count(timepoint)


joined_data %>% 
  count(timepoint, hours_outside)
#join survey responses with individual level data 
```


### baseline results 
At baseline we asked about the respondent and target child time outside only 

###respondent time outside
```{r}
respondent_baseline <- 
survey_data %>% 
  group_by(timepoint, study_arm) %>% 
  summarise(mean_hr_outside_hh = mean(hours_outside), sd_hr_inside = sd(hours_inside)) %>% 
  filter(!is.na(mean_hr_outside_hh)) %>% 
  mutate(individual = "respondent")
  



```


### respondent mean time outside 
```{r}
respondent_midline <- 
joined_data %>% 
  filter(location_name_roster == name_respondent) %>% 
  group_by(timepoint, study_arm, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside, na.rm = TRUE)) %>% 
  mutate(individual = "respondent")
```


#target child mean time outside
```{r}
target_child_midline <- 
joined_data %>% 
  filter(location_name_roster == target_child_name) %>% 
  group_by(timepoint, study_arm, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside)) %>% 
  ungroup() %>% 
	group_by(timepoint) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside), sd = sd(mean_hr_outside)) %>% 
  mutate(individual = "target child")
```

#other adult time spent outside of hh
```{r}
other_member_midline <- 
joined_data %>% 
  filter(
    location_name_roster != target_child_name, 
    location_name_roster != name_respondent
    ) %>% 
  group_by(timepoint, study_arm, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside)) %>% 
   mutate(individual = "other member")




```
#Endline calculations 
```{r}

respondent_endline <-  
  joined_data_end %>% 
  filter(name == name_respondent) %>% 
  group_by(timepoint, study_arm, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside, na.rm = TRUE)) %>% 
  mutate(individual = "respondent")

target_child_endline <- 
  joined_data_end %>% 
  filter(name == target_child_name) %>% 
  group_by(timepoint, study_arm, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside)) %>% 
  mutate(individual = "target child")
  
  
other_member_endline <- 
joined_data_end %>% 
  filter(
    name != target_child_name, 
    name != name_respondent
    ) %>% 
  group_by(timepoint, study_arm, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside)) %>% 
  ungroup() %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside)) %>% 
   mutate(individual = "other member")
  
```

```{r}
data_hours_outside <- 
  bind_rows(
    respondent_baseline,
    respondent_midline,
    target_child_midline, 
    other_member_midline, 
    respondent_endline,
    target_child_endline, 
    other_member_endline
    ) %>% 
  mutate(
    av_time_inside = 24 - mean_hr_outside_hh,
    pct_time_inside = av_time_inside / 24 * 100, 
    study_arm = case_when(
      study_arm == "pre-intervention" ~ "intervention",
      study_arm == "post-intervention" ~ "intervention",
      study_arm == "intervention" ~ "comparison",   
      study_arm == "comparison rd3" ~ "comparison", 
      study_arm == "post-intervention rd3" ~ "intervention",
      study_arm == "intervention follow-up" ~ "comparison",  
      .default = NA), 
    arm_time = str_glue("{timepoint}_{study_arm}"))


# pm_data %>% 
#   #filter(note %notin% c("qc", "insufficient data")) %>%
#   mutate(
#     pm_u400 = if_else(PM_Estimate <400, 1, 0), 
#     pm_u150 = if_else(PM_Estimate <150, 1, 0), 
#     pm_u75 = if_else(PM_Estimate <65, 1, 0), 
#     pm_u50 = if_else(PM_Estimate <50, 1, 0), 
#     pm_u35 = if_else(PM_Estimate <35, 1, 0), 
#   ) %>% 
#   group_by(timepoint, study_arm) %>% 
#   summarise(
#     count_measure = n(), 
#     pct_u_400 = sum(pm_u400) / count_measure, 
#     pct_u_150 = sum(pm_u150) / count_measure, 
#     pct_u_65 = sum(pm_u75) / count_measure, 
#     pct_u_50 = sum(pm_u50) / count_measure,
#     pct_u_35 = sum(pm_u35) / count_measure,
#   )
  
```


# PM2.5 exposures 
instead of doing hh specificn adjusted exposures we multiplied by study mean since not all hh had sensors in them. 
```{r}
pm_data_full <- 
  read_rds(file_in_pm_data_clean_rds) %>% #Read in data file of all PM2.5 data 
	mutate(date = as_date(date)) 

pm_data <-
	pm_data_full %>%
	filter(
	  !(date > as_date("2022-02-02") & date < as_date("2022-03-24")),
	  note %notin% c("qc", "insufficient data")
	  ) %>% 
  mutate(PM_Estimate = if_else(PM_Estimate < 10, 10, PM_Estimate )) #Replacing all # below the lower detection limit with 10 


pm_data_hour <-
	pm_data %>%
	filter(note != "insufficient data") %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note, dateTime_hour) %>%
	summarise_at(
		vars(PM_Estimate),
		list(mean),
		na.rm = TRUE
	) %>%
	ungroup() %>%
	mutate(
		over_100 = if_else(PM_Estimate > 100, 1, 0),
		over_500 = if_else(PM_Estimate > 500, 1, 0)
	)

#Create hh av pm 2.5 dataset
hh_av_pm2.5 <- 
  pm_data_hour %>% 
	group_by(timepoint, study_arm, hh_id) %>% 
	summarise(
		time_range = max(dateTime_hour) - min(dateTime_hour),
		hh_mean = mean(PM_Estimate),
		hh_sd = sd(PM_Estimate)
	)

#summarize by study arm
arm_mean_pm2.5 <- 
  hh_av_pm2.5 %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(
		sensor_on_time = mean(time_range),
		mean_pm2.5_hh = mean(hh_mean), 
		sd_pm2.5_hh = sd(hh_sd)
	) %>% 
  mutate(
    arm_time = str_glue("{timepoint}_{study_arm}")
  ) %>% 
  select(-timepoint)

outdoor_pm2.5 <- 
  arm_mean_pm2.5 %>% 
  filter(study_arm == "outdoor") %>% 
  transmute(
    timepoint,
    mean_pm2.5_outdoor = mean_pm2.5_hh
    )
```
### create weighted dataset of mean pm2.5 * percent time indoors for each group 
```{r}
## Arm level weighted dataset 
combined_hr_outside_pm_weighted <- 
  data_hours_outside %>% 
  left_join(arm_mean_pm2.5, by = "arm_time") %>% 
  mutate(timepoint = timepoint.x, study_arm = study_arm.x) %>% 
  select(-c(timepoint.y, timepoint.x, study_arm.x, study_arm.y)) %>% 
  left_join(outdoor_pm2.5, by = "timepoint") %>% 
  mutate(
    weighted_mean_pm2.5_hh = 
      mean_pm2.5_hh * (pct_time_inside/100) + 
      mean_pm2.5_outdoor * ((100 - pct_time_inside)/100)
    )

combined_hr_outside_pm_weighted %>% 
  select(individual, timepoint, study_arm, pct_time_inside, mean_pm2.5_hh, weighted_mean_pm2.5_hh) %>% 
  #filter(individual == "respondent") %>% 
  write_csv(here::here("table_abode_slide_endline.csv"))

## For target child baseline measure we need to calc separately bc data wasnt recorded in same way at all time points 
20.1/24*296+3.9/24*31

20.1/24*51.2+3.9/24*31



## Create household level analysis of time weighted exposures 
```

Wih the results of this we use the ABODE Model to estimate the health effects of the intervention https://householdenergy.shinyapps.io/abode/

## Physical Health 
```{r}
source(here::here("0_config.R"))
source(here::here("3_data_cleaning/1.5_define_vector_columns.R")) #Pulls in all variable group names
source(here::here("5_analysis/Dif_in_dif_fxn.R")) 
#this is a function that conducts a difference in difference analysis and reports the interaction term of timepoint*study arm as the dif in dif result 


file_in_1 <- here::here("4_data/RohingyaFuel_survey_data_triple.rds") #Overall survey dataset
file_in_2 <- here::here("4_data/pm_data_nearest_min.rds") #Particulate matter sar saved to the nearest minute 
file_in_3 <- here::here("4_data/PM_hh_averages_20220717.rds") #PM data that takes hh averages at each timepoint

# Load input files
survey_data <- read_rds(file_in_1)
pm_data_nearest_min <- read_rds(file_in_2) # PM_Estimate
hh_pm_average_location <- read_rds(file_in_3)


###################
# Add in an accute lower respiratory illness variable to the survey by combining the fever and cough in last 6 months with the questions 

#target_child_cough: In the past 6 months, has ${target_child_name} coughed continuously coughed for more than 2 weeks?
#target_child_fever: In the past 6 months, has ${target_child_name} had a fever for longer than 1 week or a fever >38°C with no explanation?


survey_data <- 
  survey_data %>% 
  mutate(
    target_child_alri = if_else(target_child_clinic_resp_yn == 1 | target_child_resp_rate_yn == 1, 1, 0), 
    target_child_asthma = if_else(target_child_wheezing_yn == 1, 1, 0), 
    target_child_severe_asthma = if_else(target_child_wheezing_yn == 1 & target_child_distrubed_speech_yn == 1, 1, 0)
    )


################################################################################
## Time inside
################################################################################

# At baseline we asked about time inside the main survey
# At midline and endline, we asked about time inside as part of the individual hh member survey

survey_data %>%
	group_by(study_arm_overall) %>%
	summarise_at(
		vars(
			hours_inside, #hours_outside, 
			target_child_hours_inside # target_child_hours_outside, 
		), 
		list(mean), 
		na.rm = TRUE
	) 

## Vector of variables to summarize
table3Vars <- c("hours_inside", "target_child_hours_inside")

# ## Vector of categorical variables that need transformation
# table3FactorVars <- c()

## Create a TableOne object
# tab3 <- CreateTableOne(data = survey_data, vars = table3Vars, factorVars = table3FactorVars, strata = "study_arm")
tab3 <- CreateTableOne(data = survey_data, vars = table3Vars, strata = "study_arm_overall")


kable(print(tab3))
# women in the comparison group spent more time inside, which could be viewed as a good thing by the community

##############################################################################
### Respiratory health 
##############################################################################


respiratory_data <-  #Creates a dataset of health variables 
	survey_data %>%
	select(
		fcn_id, study_arm, camp_id, block_id, subblock_id, 
		all_of(respiratory_vars), all_of(generalhealth_vars)
	)

saveRDS(respiratory_data, here::here("4_data/respiratory_data.rds"))


## Vector of variables to summarize in respiratory health variable 
table2_yn_Vars <- 
	c(
	  
		respiratory_vars_yn,
		breathing_vars,
		nonrespiratory_vars_yn, 
		generalhealth_vars_yn, 
		
		# mental_health_vars_yn,
		MUAC_vars
	)

## Vector of categorical variables that need transformation
table2_yn_FactorVars <- 
	c(
		respiratory_vars_yn, 
		generalhealth_vars_yn,

		nonrespiratory_vars_yn,
			 "target_child_severe_asthma"
		# mental_health_vars_yn
	)

## Create a TableOne object
tab2_yn_bl <- 
	CreateTableOne(
		data = survey_data %>% filter(timepoint %in% c("baseline")), 
		vars = table2_yn_Vars, 
		factorVars = table2_yn_FactorVars, 
		strata = "study_arm_overall"
	)

## Create a TableOne object
tab2_yn_ml <- 
	CreateTableOne(
		data = survey_data %>% filter(timepoint %in% c("midline")), 
		vars = table2_yn_Vars, 
		factorVars = table2_yn_FactorVars, 
		strata = "study_arm_overall"
	)

## Create a TableOne object
tab2_yn_el <- 
	CreateTableOne(
		data = survey_data %>% filter(timepoint %in% c("endline")), 
		vars = table2_yn_Vars, 
		factorVars = table2_yn_FactorVars, 
		strata = "study_arm_overall"
	)

## Print out a table object at each timepoint to compare the two graoups 
tab2_yn_bl
tab2_yn_ml
tab2_yn_el

## Proportion difference Conf Interval listed in paper 

#clinic visit 
prop.test(x = c(176, 255), n=c(437,494), correct = FALSE)

#wheezing 
prop.test(x = c(56, 80), n=c(437,494), correct = FALSE)

#Wheezing with distubed speech 
prop.test(x = c(14, 35), n=c(48,60), correct = FALSE)

#Eye redness
prop.test(x = c(66, 117), n=c(437,494), correct = FALSE)

#Eye itch
prop.test(x = c(41, 86), n=c(437,494), correct = FALSE)

#fever
prop.test(x = c(263, 322), n=c(437,494), correct = FALSE)

#resp redness
prop.test(x = c(38, 98), n=c(437,494), correct = FALSE)

#resp redness
prop.test(x = c(42, 93), n=c(437,494), correct = FALSE)

#resp redness
prop.test(x = c(41, 86), n=c(437,494), correct = FALSE)

#Respondet speech disturb breathlessness 
prop.test(x = c(14, 35), n=c(48,60), correct = FALSE)


#child wheez
prop.test(x = c(165, 251), n=c(437,494), correct = FALSE)

#severe asthma 
prop.test(x = c(98, 153), n=c(437,494), correct = FALSE)



### Based on variables that were diffferent at baseline we selected variables for reporting possible health 
# # Vars diff at baseline: 
# target_child_clinic_resp_yn, target_child_wheezing_yn, target_child_distrubed_speech_yn,
# respondent_disturbed_speech_yn , 
# target_child_eye_red_yn, target_child_eye_itch_yn, 
# respondent_eye_red_yn, respondent_eye_itch_yn, respondent_eye_sore_yn, 


resp_vars_impacted <-
	c(
		"target_child_clinic_resp_yn", 
		"target_child_wheezing_yn",
		"target_child_distrubed_speech_yn",
		"respondent_disturbed_speech_yn", 
		"target_child_eye_red_yn",
		"target_child_eye_itch_yn", 
		"respondent_wheezing_yn", 
		"target_child_resp_rate", 
		"respondent_eye_red_yn",
		"respondent_eye_itch_yn", 
		"respondent_eye_sore_yn",
		#"target_child_alri", 
		#"target_child_asthma", 
		#"target_child_severe_asthma",
		"target_child_cough",
		"target_child_fever",
		"target_child_resp_rate"
	)

model_data <- survey_data %>% filter(timepoint %in% c("baseline", "endline"))
model_data_midline <- survey_data %>% filter(timepoint %in% c("baseline","midline"))

model_data <- survey_data %>% filter(timepoint %in% c("baseline", "endline")) %>%  
  mutate(
    respondent_disturbed_speech_yn = if_else(is.na(respondent_disturbed_speech), 0, respondent_disturbed_speech),
    target_child_distrubed_speech_yn = if_else(is.na(target_child_distrubed_speech), 0, target_child_distrubed_speech)
  )
model_data_midline <- survey_data %>% filter(timepoint %in% c("baseline","midline")) %>% 
    mutate(
    respondent_disturbed_speech_yn = if_else(is.na(respondent_disturbed_speech), 0, respondent_disturbed_speech),
    target_child_distrubed_speech_yn = if_else(is.na(target_child_distrubed_speech), 0, target_child_distrubed_speech)
  )

dind_fxn(resp_vars_impacted, model_data_midline)
dind_fxn(resp_vars_impacted, model_data)
dind_camp_fxn(resp_vars_impacted, model_data)



survey_data %>%
	filter(timepoint %in% c("baseline", "endline")) %>%
	group_by(study_arm_overall, timepoint) %>%
  summarise_at(resp_vars_impacted, list(mean = ~ mean(.x, na.rm = TRUE), sd = ~ sd(.x, na.rm = TRUE))) 


```
## Physical Health Figure 
```{r}


fig_physical_health_child <- 
	survey_data %>%
	select(timepoint, study_arm_overall, fcn_id, all_of(respiratory_vars_yn), all_of(nonrespiratory_vars_yn), all_of(generalhealth_vars_yn)) %>%
	select(-contains("respondent_")) %>%
	gather(-timepoint, -study_arm_overall, -fcn_id, key = "category", value = "present") %>% # fuel_30_purchased_fuel
	filter(category %notin% c("target_child_disturbed_sleep_yn", "target_child_distrubed_speech_yn")) %>%
	
	group_by(timepoint, study_arm_overall, category) %>% 
	# fuel_30_purchased_fuel_endline
	# summarise(prevalence = mean(present, na.rm = TRUE)) %>% #  sd = sd(expenditure, na.rm = TRUE)
	mutate(
		child_resp_group = 
			case_when(
				category %in% c(
					"target_child_cough_yn", "target_child_resp_rate_yn", "target_child_weight_loss_yn", "target_child_wheezing_yn", 
					#"target_child_disturbed_sleep_yn", "target_child_distrubed_speech_yn",
					"target_child_eye_red_yn", "target_child_eye_itch_yn", "target_child_lethargy_yn", "target_child_fever_yn", "target_child_clinic_resp_yn"
				) ~ "child"
			),
		category = 
			ordered(
				category,
				levels = 
					c(					
						"target_child_cough_yn", "target_child_resp_rate_yn", "target_child_wheezing_yn", 
						#"target_child_disturbed_sleep_yn", "target_child_distrubed_speech_yn",
						"target_child_eye_red_yn", "target_child_eye_itch_yn", "target_child_lethargy_yn", "target_child_weight_loss_yn", "target_child_fever_yn", "target_child_clinic_resp_yn"), 
				labels = 
					c(
						"persistant \ncough", "increased \nrespiratory rate \ntoday",  "current \nwheeze", 
						# "sleep disturbed \nby wheeze", "speech disturbed \nby wheeze", 
						"eyes red", "eyes itchy", "lethargic", "unexplained \nweight loss \nin 3 mo.", "fever", "went to clinic \nfor respiratory \ncomplaint"
					)
			)
	) %>% 
	# mutate(expenditure_LCI = expenditure_mean - sd, expenditure_UCI = expenditure_mean + sd) %>%
	ggplot(aes(x = timepoint, y = present, color = study_arm_overall, group = study_arm_overall, shape = timepoint)) + #  y = prevalence, 
	stat_summary(fun = "mean", geom = "line", size = 1) + # , position = position_dodge(width = 0.2)
	stat_summary(fun = "mean", geom = "point", size = 2) + 
	stat_summary(fun.data = "mean_cl_boot", geom = "linerange") +
	# ggpubr::stat_compare_means(
	# 	label = "p.signif", #"p.signif" # symnum.args <- list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), symbols = c("****", "***", "**", "*", "ns"))
	# 	# method = "wilcox.test",
	# 	paired = FALSE, # baseline and endline are paired but the change is not, and on-going and intervention are not
	# 	hide.ns = TRUE
	# ) +
	viridis::scale_fill_viridis(
		discrete = TRUE,
		end = 2/3
	) +
	scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
	scale_color_manual(
		name = "Study arm",
		breaks = c("intervention", "comparison"),
		# labels = c("Pre-intervention", "Intervention", "Outdoor"),
		labels = c("Intervention", "Comparison"),
		values = c("#138b87",  "#430154"),
		# values = c("#7570b3",  "#d95f02", "#1b9e77")
	) +
	theme_bw() +
	theme(
		# axis.text.x = element_text(angle = 0, hjust = 1)
		axis.text.x = element_blank(),
		axis.ticks.x  = element_blank(),
		# axis.line.x = element_blank(),
		legend.position = "none"
	) + 
	labs(
		# title = "Health status over time",
		x =  "", # "Health category",
		y = "Prevalence \namong children <2 years old at baseline",
		shape = "Timepoint",
		color = "Study arm"
	) + 
	facet_grid( ~ category) # fuel_30_purchased_fuel_endline

# fig_physical_health_child

survey_data %>% 
	group_by(timepoint, study_arm_overall) %>% 
	summarise(mean(respondent_resp_rate, na.rm =TRUE), 
						mean(respondent_weight_loss, na.rm = TRUE))

#Figure out where the graph is > 100 
survey_data %>% filter(timepoint == "baseline") %>% select(weight_loss_reported_respondant) %>% #count(weight_loss_reported_respondant)

#At baseline the resp rate variable is 
## resp_rate_reported_respondant
## weight_loss_reported_respondant


fig_physical_health_respondent <- 
	survey_data %>%
  mutate(
    respondent_resp_rate_yn = if_else(is.na(respondent_resp_rate_yn), resp_rate_reported_respondant, respondent_resp_rate_yn), 
    respondent_weight_loss_yn = if_else(is.na(respondent_weight_loss_yn), weight_loss_reported_respondant, respondent_weight_loss_yn)) %>% 
  filter(respondent_weight_loss_yn != 99) %>% 
	select(timepoint, study_arm_overall, fcn_id, all_of(respiratory_vars_yn), all_of(nonrespiratory_vars_yn), all_of(generalhealth_vars_yn), respondent_weight_loss, respondent_resp_rate) %>%
	select(-contains("child_")) %>%
	gather(-timepoint, -study_arm_overall, -fcn_id, key = "category", value = "present") %>% # fuel_30_purchased_fuel
	# pull(category) %>% unique()
	filter(category %notin% c("respondent_disturbed_sleep_yn", "respondent_disturbed_speech_yn")) %>%
	group_by(timepoint, study_arm_overall, category) %>% # fuel_30_purchased_fuel_endline
	mutate(
		# 		 "respondent_cough_yn"            "respondent_resp_rate_yn"        "respondent_weight_loss_yn"      "respondent_wheezing_yn"        
		#  [5] "respondent_disturbed_sleep_yn"  "respondent_disturbed_speech_yn" "respondent_eye_red_yn"          "respondent_eye_itch_yn"        
		#  [9] "respondent_eye_sore_yn"         "respondent_headache_yn"         "respondent_backache_yn"        
		child_resp_group = 
			case_when(
				category %in% c(
					"respondent_cough_yn", "respondent_resp_rate_yn", "respondent_weight_loss_yn", "respondent_wheezing_yn", 
					#"respondent_disturbed_sleep_yn", "respondent_disturbed_speech_yn", 
					"respondent_eye_red_yn", "respondent_eye_itch_yn", "respondent_eye_sore_yn", "respondent_headache_yn", "respondent_backache_yn"
				) ~ "respondent"
			)
	) %>%
	mutate(
		category = 
			ordered(
				category,
				levels = 
					c(					
						"respondent_cough_yn", "respondent_resp_rate_yn", "respondent_wheezing_yn", 
						#"respondent_disturbed_sleep_yn", "respondent_disturbed_speech_yn", 
						"respondent_eye_red_yn", "respondent_eye_itch_yn", "respondent_eye_sore_yn", "respondent_weight_loss_yn", "respondent_headache_yn", "respondent_backache_yn"
					), 
				labels = 
					c(
						"persistant \ncough", "increased \nrespiratory rate \ntoday",  "current \nwheeze", 
						# "sleep disturbed \nby wheeze", "speech disturbed \nby wheeze",
						"eyes red", "eyes itchy", "eyes sore", "unexplained \nweight loss \nin 3 mo.", "headache", "backache"
					)
			)
	) %>%
	filter(!is.na(category)) %>% 
	# mutate(expenditure_LCI = expenditure_mean - sd, expenditure_UCI = expenditure_mean + sd) %>%
	ggplot(aes(x = timepoint, y = present, color = study_arm_overall, group = study_arm_overall, shape = timepoint)) + # y = prevalence
	stat_summary(fun = "mean", geom = "line", size = 1) + # , position = position_dodge(width = 0.2)
	stat_summary(fun = "mean", geom = "point", size = 2) + 
	stat_summary(fun.data = "mean_cl_boot", geom = "linerange") +
	# ggpubr::stat_compare_means(
	# 	label = "p.signif", #"p.signif" # symnum.args <- list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), symbols = c("****", "***", "**", "*", "ns"))
	# 	# method = "wilcox.test",
	# 	paired = FALSE, # baseline and endline are paired but the change is not, and on-going and intervention are not
	# 	hide.ns = TRUE
	# ) +
	viridis::scale_fill_viridis(
		discrete = TRUE,
		end = 2/3
	) +
	scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
	scale_color_manual(
		name = "Study arm",
		breaks = c("intervention", "comparison"),
		# labels = c("Pre-intervention", "Intervention", "Outdoor"),
		labels = c("Intervention", "Comparison"),
		values = c("#138b87",  "#430154"),
		# values = c("#7570b3",  "#d95f02", "#1b9e77")
	) +
	theme_bw() +
	theme(
		axis.text.x = element_text(angle = 45, hjust = 1),
		#axis.text.x = element_blank(),
		axis.ticks.x = element_blank(),
		# axis.line.x = element_blank(),
		legend.position = "none"
	) + 
	labs(
		# title = "Health status over time",
		x =  "", # "Health category",
		y = "Prevalence \namong female caregivers",
		shape = "Timepoint",
		color = "Study arm"
	) + 
	facet_grid( ~ category) # fuel_30_purchased_fuel_endline # , labeller = label_wrap_gen(width = 25, multi_line = TRUE)



# ggarrange(
# 	sp,                                                 # First row with scatter plot
# 	ggarrange(bxp, dp, ncol = 2, labels = c("B", "C")), # Second row with box and dot plots
# 	nrow = 2, 
# 	labels = "A"                                        # Labels of the scatter plot
# ) 

fig_physical_health <-
	ggarrange(
		fig_physical_health_child,
		fig_physical_health_respondent,
		# fig_mental_health_respondent,
		common.legend = TRUE, legend = "right",
		nrow = 2
	)

fig_physical_health

ggsave(
	here::here("6_figures", "fig_physical_health.png"),
	plot = last_plot(),
	scale = 1,
	height = 6,
	width = 10,
	units = "in",
	device = "png"
)

survey_data %>%
	summarise_at(vars(cost_forest_not_wood), list(mean), na.rm = TRUE)
```

## Mental health 

```{r}
fig_mental_health_respondent <- 
  survey_data %>%
	select(timepoint, study_arm_overall, fcn_id, all_of(mental_health_vars)) %>%
	#drop_na() %>% 
#	filter(timepoint %in% c("baseline", "endline")) %>% 
	gather(-timepoint, -study_arm_overall, -fcn_id, key = "category", value = "present") %>% # fuel_30_purchased_fuel
	group_by(timepoint, study_arm_overall, category) %>% # fuel_30_purchased_fuel_endline
	mutate(
		category = 
			ordered(
				category,
				levels = c("enjoyed_life", "self_worth", "hopeful", "sick", "no_appetite","diff_concentrating","fearful","cant_get_going", "life_failure", "suicidal_thoughts_30"),
				# levels = 
				# 	c(					
				# 		"happy_yn", "enjoyed_life_yn", "self_worth_yn", "hopeful_yn",                
				# 		"no_appetite_yn",  "less_talkative_yn",   
				# 		"depressed_yn",  
				# 		# "feeling_anxious_yn", "feeling_worry_yn", "feeling_not_relaxing_yn", "feeling_restless_yn",    
				# 		# "feeling_annoyed_yn", "feeling_afraid_yn", 
				# 		"suicidal_thoughts_30_yn"
				# 	), 
				labels = 
					c(
					  "enjoyed life", "as good \nas others", "hopeful", "sick",
						"no appetite",   "difficulty concentrating", "fearful", "can't get \ngoing",
						"life is a failure", 
						# "anxious", "worried", "unable to \nrelax", "restless", "annoyed", "afraid", 
						"suicidal in \npast 30 days"
					)
			)
	) %>%
	drop_na(category) %>%
	filter(category != "NA") %>% 
	# mutate(expenditure_LCI = expenditure_mean - sd, expenditure_UCI = expenditure_mean + sd) %>%
	ggplot(aes(x = timepoint, y = present, color = study_arm_overall, group = study_arm_overall, shape = timepoint)) + # y = prevalence
	stat_summary(fun = "mean", geom = "line", size = 1) + # , position = position_dodge(width = 0.2)
	stat_summary(fun = "mean", geom = "point", size = 2) + 
	stat_summary(fun.data = "mean_cl_boot", geom = "linerange") +
	viridis::scale_fill_viridis(
		discrete = TRUE,
		end = 2/3
	) +
	#scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
	scale_color_manual(
		name = "Study arm",
		breaks = c("intervention", "comparison"),
		# labels = c("Pre-intervention", "Intervention", "Outdoor"),
		labels = c("Intervention", "Comparison"),
		values = c("#138b87",  "#430154"),
		# values = c("#7570b3",  "#d95f02", "#1b9e77")
	) +
	theme_bw() +
	theme(
		axis.text.x = element_text(angle = 45, hjust = 1),
	#	axis.text.x = element_blank(),
		axis.ticks.x = element_blank()#,
		# axis.line.x = element_blank(),
		# legend.position = "none"
		# legend.position = "bottom",
		# legend.direction = "horizontal"
	) + 
	guides(
		shape = guide_legend(title.position="top", title.hjust = 0.5),
		color = guide_legend(title.position="top", title.hjust = 0.5)
	) +
	labs(
		# title = "Health status over time",
		x =  "", # "Health category",
		y = "",
		shape = "Timepoint",
		color = "Study arm"
	) + 
	facet_wrap( ~ category, nrow = 2) # fuel_30_purchased_fuel_endline # , labeller = label_wrap_gen(width = 25, multi_line = TRUE)

fig_mental_health_respondent

ggsave(
	here::here("6_figures", "fig_mental_health.png"),
	plot = last_plot(),
	scale = 1,
	height = 6,
	width = 10,
	units = "in",
	device = "png"
)


```

## Time Use 
```{r}
##########################################################################
## Livestyle changes since LPG distribution
##########################################################################

# lpg_changes_lifestyle is select_multiple... table percent of hh that answered each?

survey_data %>%
  group_by(timepoint, study_arm_overall) %>%
  summarise_at(
    vars(starts_with("lpg_changes_lifestyle")),
    list(mean), 
    na.rm = TRUE
  ) %>%
  gather(-timepoint, -study_arm_overall, key = "lifestyle_change", value = "pc_hh")




##########################################################################
# Time use
##########################################################################

# "Think about a day before you obtained LPG at the distribution center and compare it to now, when you do get LPG from the distribution center. Compared to before, do you think that YOU currently spend MORE or LESS time on each of the following activities?"
# 
# Same question for children's time
# 
# [more_less]	1	more 
# [more_less]	2	same
# [more_less]	3	less
# 
# For the group of questions "time_free_lpg", at baseline the relevance was "selected(${fuel_30_receive_lpg},'1') and (selected(${collect_wood_g},'1') or selected(${collect_wood_b},'1'))" - this means we ONLY asked the time use questions to family's who's CHILDREN collected wood. That's fine for the group "time_child_free_lpg" but not for the adult respondent question! 
# 	
# 	Post-intervention might have better recall because they more recently transition; so assess separately and combine if it seems reasonable to do so.
# At endline, the Skip logic was selected(${fuel_ever_receive_lpg},'1') and (selected(${collect_wood_g_ever},'1') or selected(${collect_wood_b_ever},'1')) and (selected(${timepoint, study_arm_overall},'3') or selected(${study_arm},'5')) 
# 
# activity left column, more-less on top row





##########################################################################
# Change in respondent's time
##########################################################################

time_respondent_more_less <-
  survey_data %>%
  # At baseline, comparison hh had already not used fuel for a year, 
  # so use only the results from the intervention group at midline, who will have better recall
  filter(study_arm_overall == "intervention" & timepoint == "midline") %>%
  #filter(study_arm_overall %in%  c("intervention")) %>%
  select(fcn_id, timepoint, study_arm_overall, starts_with("time_")) %>% 
  select(!contains("_child_")) %>%
  # filter(!is.na(time_child_cooking)) %>% # this question was only answered if girls or boys were reported to collect firewood
  # count() # There were only 38 respondents of 597 hh that answered the intervention survey
  gather(-fcn_id, -timepoint, -study_arm_overall, key = "activity", value = "more_less") %>%
  filter(!is.na(more_less)) %>% # There are still some hh with na, because they reported not recently harvesting wood? 
  group_by(activity) %>%
  count(more_less) %>%
  mutate(
    pc = n / sum (n) # sum(n) = 99 because this many hh answered these questions
  ) %>% # make the less ones negative
  ungroup() %>%
  # necessary to apply prop.test to each row
  rowwise() %>%
  mutate(
    lower = ifelse(n > 0, prop.test(n, n/pc)$conf.int[1], 88),
    upper = ifelse(n > 0, prop.test(n, n/pc)$conf.int[2], NA)
  ) %>%
  mutate(
    # Change sign to negative if the value was less
    pc = ifelse(more_less == 3, pc * (-1), pc),
    lower = ifelse(more_less == 3, lower * (-1), lower),
    upper = ifelse(more_less == 3, upper * (-1), upper),
    more_less = factor(more_less, levels = c(1, 2, 3), labels = c("more", "same", "less"))
  )



##### Make fig #########

fig_time_respondent_more_less <-
  time_respondent_more_less %>%
  filter(more_less != "same") %>%
  # no people reported that they spend time gathering non-wood items so remove this
  filter(!is.na(activity)) %>%
  filter(activity %in% c(
    "time_harvesting_wood",
    "time_cooking",
    "time_selling_food",
    "time_washing_dishes",
    "time_washing_clothes",
    "time_collecting_water",
    "time_unskilled_labor",
    "time_employment_ngo",
    "time_accompanying_children",
    "time_caring_for_children",
    "time_caring_for_others",
    "time_eating",
    "time_learning",
    "time_nothing",
    "time_socializing",
    "time_sleeping"
  )) %>% 
#  filter(is.na(activity)) %>% 
  mutate(
    activity = 
      ordered(
        activity, 
        levels = 
          c(
            "time_harvesting_wood",
            "time_gathering_nonwood_items",
            "time_cooking",
            "time_selling_food",
            "time_washing_dishes",
            "time_washing_clothes",
            "time_collecting_water",
            "time_unskilled_labor",
            "time_employment_ngo",
            "time_accompanying_children",
            "time_caring_for_children",
            "time_caring_for_others",
            "time_eating",
            "time_learning",
            "time_nothing",
            "time_socializing",
            "time_sleeping"
          ),
        labels = 
          c(
            "Harvesting wood",
            "Gathering non-wood items",
            "Cooking", 
            "Selling food",
            "Washing dishes",
            "Washing clothes",
            "Collecting water", 
            "Working as unskilled labor",
            "Wokring for an NGO or wage laborer",
            "Accompanying children",
            "Caring for children",  
            "Caring for others",
            "Eating",
            "Learning", 
            "Doing nothing",
            "Socializing", 
            "Sleeping"
          )
      )
  ) %>%
  ggplot(aes(x = activity, y = pc, fill = more_less)) +
  geom_col() +
  geom_linerange(aes(ymin = lower, ymax = upper)) + # , position = position_dodge(0.9)
  viridis::scale_fill_viridis(
    discrete = TRUE,
    begin = 9/10,
    end = 3/10, 
    name = "Amount of time",
    breaks = c("more", "less"),
    labels = c("More", "Less")
  ) + 
  # scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + # Percentage labels rounded to the nearest integer
  scale_y_continuous(labels = function(x) scales::percent(abs(x))) + # Percentage labels rounded to the nearest integer	
  theme_bw() +
theme(
  axis.text.x = element_text(size = 9, angle = 45, hjust = 1),
  axis.title.x = element_text(size = 11),
  axis.title.y = element_text(size = 10),
  axis.text.y = element_text(size = 10),
  legend.text = element_text(size = 11),
  legend.title = element_text(size = 12),
  plot.margin = margin(10, 10, 10, 10)
) +
  labs(
    title = "",
    x = "Respondent Activity",
    y = "Percent of households \nreporting change (n = 475)"
  ) # + 
# facet_wrap(~ more_less)

fig_time_respondent_more_less

ggsave(
  here::here("6_figures", "fig1_time_respondent_more_less.png"),
  plot = last_plot(),
  scale = 1,
  height = 8,
  width = 8,
  units = "in",
  device = "png"
)

# # Skip logic: selected(${fuel_ever_receive_lpg},'1') and (selected(${collect_wood_g_ever},'1') or selected(${collect_wood_b_ever},'1')) and (selected(${study_arm},'3') or selected(${study_arm},'5')) 
# survey_data %>% 
# 	filter(study_arm %in%  c("post-intervention", "intervention follow-up")) %>%
# 	select(study_arm, fcn_id, fuel_ever_receive_lpg, collect_wood_g_ever, collect_wood_b_ever, starts_with("time_child"))




##########################################################################
# Change in children's time
##########################################################################

time_child_more_less <-
  survey_data %>%
  # At baseline, comparison hh had already not used fuel for a year, 
  # so use only the results from the intervention group at midline, who will have better recall
  filter(study_arm_overall == "intervention" & timepoint == "midline") %>%
  #filter(study_arm_overall %in%  c("intervention")) %>%
  select(fcn_id, timepoint, study_arm_overall, starts_with("time_child")) %>% 
  # filter(!is.na(time_child_cooking)) %>% # this question was only answered if girls or boys were reported to collect firewood
  # count() # There were only 38 respondents of 597 hh that answered the intervention survey
  gather(-fcn_id, -timepoint, -study_arm_overall, key = "activity", value = "more_less") %>%
  filter(!is.na(more_less)) %>% # There are still some hh with na, because they reported not recently harvesting wood? 
  group_by(activity) %>%
  count(more_less) %>%
  mutate(
    pc = n / sum (n) # sum(n) = 99 because this many hh answered these questions
  ) %>% # make the less ones negative
  ungroup() %>%
  # necessary to apply prop.test to each row
  rowwise() %>%
  mutate(
    lower = ifelse(n > 0, prop.test(n, n/pc)$conf.int[1], 88),
    upper = ifelse(n > 0, prop.test(n, n/pc)$conf.int[2], NA)
  ) %>%
  mutate(
    # Change sign to negative if the value was less
    pc = ifelse(more_less == 3, pc * (-1), pc),
    lower = ifelse(more_less == 3, lower * (-1), lower),
    upper = ifelse(more_less == 3, upper * (-1), upper),
    more_less = factor(more_less, levels = c(1, 2, 3), labels = c("more", "same", "less"))
  )



#### Make fig ####

fig_time_child_more_less <-
  time_child_more_less %>%
  filter(more_less != "same") %>%
  # We didn't ask about children working, but should have as we see in the IDIs this was the case
  mutate(
    activity = 
      ordered(
        activity, 
        levels = 
          c(
            "time_child_harvesting_wood",
            "time_child_gathering_nonwood_items", 
            "time_child_cooking", 
            "time_child_cleaning",
            "time_child_collecting_water",
            "time_child_school", 
            "time_child_nothing",
            "time_child_socializing",
            "time_child_sleeping"
            
          ),
        labels = 
          c(
            "Harvesting wood",
            "Gathering non-wood items",
            "Cooking", 
            "Cleaning",  
            "Collecting water",
            "Going to school", 
            "Doing nothing",
            "Socializing", 
            "Sleeping"
          )
      )
  ) %>%
  ggplot(aes(x = activity, y = pc, fill = more_less)) +
  geom_col() +
  geom_linerange(aes(ymin = lower, ymax = upper)) + # , position = position_dodge(0.9)
  viridis::scale_fill_viridis(
    discrete = TRUE,
    begin = 9/10,
    end = 3/10, 
    name = "Amount of time",
    breaks = c("more", "less"),
    labels = c("More", "Less")
  ) + 
  # scale_y_continuous(labels = function(x) scales::percent_format(abs(x), accuracy = 1)) + # Percentage labels rounded to the nearest integer
  scale_y_continuous(labels = function(x) scales::percent(abs(x))) + # Percentage labels rounded to the nearest integer
  theme_classic() +
  theme_bw() +
theme(
  axis.text.x = element_text(size = 9, angle = 45, hjust = 1),
  axis.title.x = element_text(size = 11),
  axis.title.y = element_text(size = 10),
  axis.text.y = element_text(size = 10),
  legend.text = element_text(size = 11),
  legend.title = element_text(size = 12),
  plot.margin = margin(10, 10, 10, 10)
) +
  labs(
    title = "",
    x = "Child Activity",
    y = "Percent of households \nreporting change (n = 99)"
  )

fig_time_child_more_less


library(ggpubr)
library(patchwork)
library(here)

# Arrange plots with shared legend
combined_plot <- ggarrange(
  fig_time_respondent_more_less,
  fig_time_child_more_less,
  ncol = 1, nrow = 2,
  common.legend = TRUE,
  legend = "bottom",
  align = "v"  # Ensures vertical alignment
)

# Export the plot with increased resolution and size
ggexport(
  plot = combined_plot,
  filename = here("6_figures", "fig_time_child_more_less.png"),
  width = 2100, height = 2500, res = 300
)


# # Skip logic: selected(${fuel_ever_receive_lpg},'1') and (selected(${collect_wood_g_ever},'1') or selected(${collect_wood_b_ever},'1')) and (selected(${study_arm_overa},'3') or selected(${study_arm_overa},'5')) 
# survey_data %>% 
# 	filter(study_arm %in%  c("post-intervention", "intervention follow-up")) %>%
# 	select(study_arm, fcn_id, fuel_ever_receive_lpg, collect_wood_g_ever, collect_wood_b_ever, starts_with("time_child"))

```

#Mental health results 
```{r}

#### Model if depression symptoms changed 

CES_D_data <-
	survey_data %>%
	rowwise() %>% 
	mutate(
		CES_D_score = sum(c_across(c(mental_health_bad_vars, mental_health_good_vars))) # use all_of() when using select and use c_across() when using other verbs
	) %>%
	ungroup() %>%
	# CES_D >16 meaning at risk for depression has not been validated in Bangladesh
	mutate(
		CES_D_o16 = ifelse(CES_D_score > 16, "at-risk", "not at risk"),
		CES_D_o16_score = ifelse(CES_D_score > 16, 1, 0)
	)

CES_D_output <- 
  CES_D_data %>%
  select(timepoint, study_arm_overall, fcn_id, CES_D_score, CES_D_o16, CES_D_o16_score) %>% 
  write_rds(here::here("4_data/RohingyaFuel_survey_data_CES_D.rds"))

CES_D_data %>%
	tabyl(study_arm, CES_D_o16) %>%
	adorn_percentages("row") %>%
	adorn_pct_formatting(digits = 2) %>%
	adorn_ns() %>%
	select(study_arm, 'at-risk') # no need to also display "not at risk" since it is just 100%-'at-risk'


CES_D_data_model <- 
	CES_D_data %>% 
	filter(timepoint %in% c("baseline", "endline")) %>% 
	mutate(study_arm_overall_num = if_else(study_arm_overall == "intervention", 1, 0))

model_data <- 
  survey_data %>% 
  filter(timepoint %in% c("baseline", "endline")) %>% 
  mutate(study_arm_overall_num = if_else(study_arm_overall == "intervention", 1, 0))


dind_fxn(var_interest = "CES_D_o16_score", CES_D_data_model)
dind_fxn(var_interest = "suicidal_thoughts_30_yn", model_data)

model_data_mid <- 
survey_data %>%
  filter(timepoint %in% c("baseline", "midline")) 

CES_D_data_model_mid <- 
	CES_D_data %>% 
	filter(timepoint %in% c("baseline", "midline")) %>% 
	mutate(study_arm_overall_num = if_else(study_arm_overall == "intervention", 1, 0))

dind_fxn(var_interest = "CES_D_o16_score", CES_D_data_model_mid)
dind_fxn(var_interest = "suicidal_thoughts_30_yn", model_data_mid)

```

