---
title: "PM_analysis"
author: "Laura Kwong"
date: "11/06/2019"
output:
  word_document: default
  html_document: default
---
R verion 3.6.1 downloaded 6 Nov 2019


https://cran.r-project.org/web/packages/MakefileR/vignettes/demo.html

Message from Jamil 
"All the Outdoor monitors at the same place and same school at Intervention but Pre-Intervention At 2 Mosque(camp 8W and camp 10). All the Baseline outdoor monitor and Endline outdoor monitor setup as the same location.Note that no different location in school and Mosque. Always had collected one location PM 2.5 data."

```{r setup, include=FALSE}
library(tableone)
library(janitor) #tabyl() adorn_...()
library(dplyr)
library(readxl)
library(lubridate)
library(tidyverse)
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(echo = TRUE)

`%notin%` <- Negate(`%in%`)
```

```{r file_paths}
#Input Files
list_of_file_path_pats_pre_intervention <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1Ed4fav2PP395AS4U4w0aAZnBCEUym8XG/ALL DATA_BASELINE_2020/Pre_intervention/PATS+"

list_of_file_path_pats_intervention <- 
	"/Volumes/GoogleDrive/.shortcut-targets-by-id/1Ed4fav2PP395AS4U4w0aAZnBCEUym8XG/ALL DATA_BASELINE_2020/Intervention/PATS+"


list_of_file_path_pats_post_intervention <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1TPfOuuXHpcynwDGFP8R-HFUesipMSRAO/ALL DATA_MIDLINE_2021/Pre-Intervention/Pats+"

list_of_file_path_pats_intervention_fu <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1TPfOuuXHpcynwDGFP8R-HFUesipMSRAO/ALL DATA_MIDLINE_2021/Intervention/Pats+"


list_of_file_path_hapex_pre_intervention <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1Ed4fav2PP395AS4U4w0aAZnBCEUym8XG/ALL DATA_BASELINE_2020/Pre_intervention/HAPEX"

list_of_file_path_hapex_intervention <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1Ed4fav2PP395AS4U4w0aAZnBCEUym8XG/ALL DATA_BASELINE_2020/Intervention/HAPEX"

list_of_file_path_hapex_post_intervention <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1TPfOuuXHpcynwDGFP8R-HFUesipMSRAO/ALL DATA_MIDLINE_2021/Pre-Intervention/Hapex"

list_of_file_path_hapex_intervention_fu <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1TPfOuuXHpcynwDGFP8R-HFUesipMSRAO/ALL DATA_MIDLINE_2021/Intervention/Hapex"

### Output Files RDS 
# all_pm_data_path_rds <- "C:/Users/admin/Google Drive (lakwong@stanford.edu)/Rohingya/Rohingya research - Fuel/Sensors/ALL DATA/PATS+_Data_20210114.rds"

all_pm_data_path_rds <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1HGzyHFSinRs5Jh4j7SZsJyb2KPXJ8mh8/Rohingya/Rohingya research - Fuel/Sensors/PATS+_Data_20220628.rds"

all_hapex_data_path_rds <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1HGzyHFSinRs5Jh4j7SZsJyb2KPXJ8mh8/Rohingya/Rohingya research - Fuel/Sensors/Hapex_Data_20220628.rds"

all_hapex_data_path_csv <- "/Volumes/GoogleDrive/.shortcut-targets-by-id/1HGzyHFSinRs5Jh4j7SZsJyb2KPXJ8mh8/Rohingya/Rohingya research - Fuel/Sensors/Hapex_Data_20220628.csv"

file_out_pm_data_base <- here::here("4_data/pm_data_base.rds")

pm_data_min_rds <- here::here("4_data/pm_data_min.rds")

pm_data_nearest_min_rds <- here::here("4_data/pm_data_nearest_min.rds")

pm_data_hour_rds <- here::here("4_data/pm_data_hour.rds")

pm_data_nearest_hour_rds <- here::here("4_data/pm_data_nearest_hour.rds")

pm_data_min_csv <- here::here("4_data/pm_data_min.csv")

pm_data_nearest_min_csv <- here::here("4_data/pm_data_nearest_min.csv")

pm_data_hour_csv <- here::here("4_data/pm_data_hour.csv")

pm_data_nearest_hour_csv <- here::here("4_data/pm_data_nearest_hour.csv")


# Manually move the compiled file into the raw folder of the project
#file_pm_data_base <- here::here("2_data_raw", "PATS+_Data_20210114.rds")
file_pm_data_base <- all_pm_data_path_rds
file_HAPEX_data_base <- here::here("2_dat_raw", "HAPEX_Data_20220628.rds")
```

## File of Pats+ Data
```{r}
list_of_files_pats_pre_intervention <-   
	list.files(
		path = list_of_file_path_pats_pre_intervention,
		recursive = TRUE, 
		pattern = "*.csv", 
		full.names = TRUE 
	)

length(list_of_files_pats_pre_intervention) #134

list_of_files_pats_intervention <-   
	list.files(
		path = list_of_file_path_pats_intervention,
		recursive = TRUE, 
		pattern = "*.csv", 
		full.names = TRUE 
	)

length(list_of_files_pats_intervention) #95

list_of_files_pats_post_intervention <-   
	list.files(
		path = list_of_file_path_pats_post_intervention,
		recursive = TRUE, 
		pattern = "*.csv", 
		full.names = TRUE 
	)

length(list_of_files_pats_post_intervention) #60

list_of_files_pats_intervention_fu <-   
	list.files(
		path = list_of_file_path_pats_intervention_fu,
		recursive = TRUE, 
		pattern = "*.csv", 
		full.names = TRUE 
	)

length(list_of_files_pats_intervention_fu) #48

list_of_files_pats <- 
	c(list_of_files_pats_pre_intervention, list_of_files_pats_intervention, list_of_files_pats_post_intervention, list_of_files_pats_intervention_fu)

all_pm_data <- 
	list_of_files_pats %>%
	set_names(sub(".*/", "", list_of_files_pats)) %>% # added file_name as first column value
	map_dfr(
		~ read_csv(
			.x,
			col_types = 
				cols(
					"c", "d", "d", "d", "d", "d", "d", 
					"d", "d", "d", "d", "d", "d", "d", "d", "d"
				),
			skip = 31, 
			col_names = FALSE, 
		),
		.id = "file_name" # labeled first column with as "file_name"
	) %>% 
	# select(-X) %>% # I don't know why there is an empty column X at the end
	mutate(
		# study_arm = str_extract(str_extract(file_name, "^(?:[^_]*_){2}[0-9]{1}"), "[0-9]$")
		file_name = str_replace(file_name, "\\..*","")  # takes off the .csv
	) %>%
	`colnames<-`( # must be exactly `colnames<-`
		c(
			"file_name", "dateTime",	
			"V_power",	"degC_sys",	"degC_air",	"RH_air",	
			"degC_CO",	"CO_PPM",	"status",	"ref_sigDel",	
			"low20avg",	"high320avg",	"motion",	"CO_mV",	
			"ignore",	"iButton_Temp",	"PM_Estimate"#, # "study_arm"
		)
	) 
#  mutate(dateTime_lubridated = lubridate::ymd_hms(dateTime, tz = "Asia/Dhaka", locale = Sys.getlocale("LC_TIME"), truncated = 3)) %>%

all_pm_data %>%
	saveRDS(all_pm_data_path_rds)

all_pm_data %>%
	saveRDS(file_pm_data_base)

```


# Hapex Data 
```{r}
list_of_files_hapex_pre_intervention <-   
	list.files(
		path = list_of_file_path_hapex_pre_intervention,
		recursive = TRUE, 
		pattern = "*.csv", 
		full.names = TRUE 
	)

list_of_files_hapex_intervention <-   
	list.files(
		path = list_of_file_path_hapex_intervention,
		recursive = TRUE, 
		pattern = "*.csv", 
		full.names = TRUE 
	)

list_of_files_hapex <- c(list_of_files_hapex_pre_intervention, list_of_files_hapex_intervention)


all_hapex_data <- 
	list_of_files_hapex %>%
	set_names(sub(".*/", "", list_of_files_hapex)) %>% # added file_name as first column value
	map_dfr(
		~ read_csv(
			.x,
			col_types = 
				cols("c", "d", "d"),
			skip = 29, 
			col_names = FALSE, 
		),
		.id = "file_name" # labeled first column with as "file_name"
	) %>% 
	mutate(
		# 			study_arm = str_extract(str_extract(file_name, "^(?:[^_]*_){3}[0-9]{1}"), "[0-9]$")
		file_name = str_replace(file_name, "\\..*","") # takes off the .csv
	) %>%
	`colnames<-`(
		c(
			"file_name", "timestamp",	"mother_compliance",	"mother_pm"# , # "study_arm"
		)
	) 

all_hapex_data %>%
	saveRDS(all_hapex_data_path_rds)

all_hapex_data %>%
	saveRDS(all_hapex_data_path_rds)

write.csv(all_hapex_data, all_hapex_data_path_csv)

#   mutate(dateTime_lubridated = lubridate::ymd_hms(dateTime, tz = "Asia/Dhaka", locale = Sys.getlocale("LC_TIME"), truncated = 3)) %>%
```

# Clean data

Still not clean, must look at google sheet for other adjustments that need to be made. 

https://berkeleyair.com/monitoring-instruments-sales-rentals/particle-and-temperature-sensor-pats/
Lower particulate matter detection limit (PM2.5): 10 to 20 μg/m3
Upper particulate matter detection limit (PM2.5): 30,000 to 50,000 μg/m3

--> exclue anything below 20 ug/m3 and above 30,000 ug/m3

```{r load_data, include=FALSE} 
pm_data_not_censored_raw <- 
	readRDS(file = file_pm_data_base) %>%
	filter(V_power > 3.6) %>% # If the battery voltage is not more than 3.6, the PM manual notes that the reading may not be accurate
	separate(file_name, into = c("PM_monitor", "date", "study_arm", "hh_id_note"), sep = "_", extra = "merge", remove = FALSE) # for some reason if I sep into five columns right away, those with no "note" are missing a study arm

# pm_data_not_censored_raw %>%
# 	select(hh_id_note) %>%
# 	unique() %>%
# 	arrange() %>% View()
```

```{r}
pm_data_not_censored <-
	pm_data_not_censored_raw %>%
	# There is an "error" because some file names don't have "QC" after the test name - the space where "QC" would be is replaced with an NA. This is good because the files were actually not "QC" file - NA is how they should be marked!
	mutate(
		dateTime = 
			if_else(
				is.na(ymd_hms(dateTime)) == FALSE, 
				ymd_hms(dateTime), 
				mdy_hm(dateTime)
			),
		dateTime_min = round_date(dateTime, unit = "minute"),
		dateTime_min_dhaka = as.POSIXct(dateTime_min, tz = "Asia/Dhaka"), # + 6 * 60 * 60, # , tz = "Asia/Dhaka"
		dateTime_hour = round_date(dateTime, unit = "hour"),
		dateTime_hour_dhaka = as.POSIXct(dateTime_hour, tz = "Asia/Dhaka"), #+ 6 * 60 * 60, # , tz = "Asia/Dhaka"
		
		timepoint = ifelse(dateTime < "2019-11-18", "baseline", "endline"),
		
		# 4FPP11_school #baseline
		hh_id_note = ifelse(hh_id_note %in% c("4FPP11_School", "4FPP11_school"), "4EPP11_school", hh_id_note),
		
		# 8WDI18 should be 8WI18; xxx_mosjid should be xxx_mosque instead of mosjid #endline
		hh_id_note = ifelse(hh_id_note %in% c("8WI18_Mosjid", "8WI18_mosjid", "8WI18_Mosque", "8WI18_mosque"), "8WI18_mosque", hh_id_note),
		hh_id_note = ifelse(hh_id_note %in% c("8WDI18_Mosjid", "8WDI18_mosjid", "8WDI18_Mosque", "8WDI18_mosque"), "8WI18_mosque", hh_id_note),
		
		
		# 10D12_mosque is the old block name for 10GG9_mosque  #endline
		# note = ifelse(timepoint == "baseline" & hh_id_note == "10D12_mosque", "mosque", note),
		hh_id_note = ifelse(hh_id_note %in% c("10D12_Mosque", "10D12_mosque"), "10GG9_mosque", hh_id_note)
	) %>%
	separate(hh_id_note, into = c("hh_id", "note"), sep = "_", extra = "merge", remove = TRUE) %>% # I do want a variable hh_id_note but first clean up the case (str_to_lower) of the note then recombine.
	mutate(
		note = 
			if_else(is.na(note), "normal", str_to_lower(note)),
		study_arm =
			if_else(note %in% c("school", "mosque"), "outdoor", study_arm),
		study_arm =
			ordered(
				as.character(study_arm),
				levels = c("0", "1", "outdoor"),
				labels = c("intervention", "comparison", "outdoor")
			)
	) %>%
	unite(col = "hh_id_note", c(hh_id, note), remove = FALSE) %>%
	# # Using separate makes the resulting time into characters, which is not what I want; 
	# # using hms to convert them out of character format produced a period, not a time of day
	# separate(dateTime_min, into = c("dateTime_min_extraDate", "nearest_min"), sep = " ", remove = FALSE) %>%
	# separate(dateTime_hour, into = c("dateTime_hour_extraDate", "nearest_hour"), sep = " ", remove = FALSE) %>%
	
	# Instead, keep the values in POSIXct and use trunc to chop off the days
	mutate(
		nearest_min =  as.POSIXct(paste("2000-01-01", paste(hour(ymd_hms(dateTime_hour)), minute(ymd_hms(dateTime_min)), sep = ":")), "Asia/Dhaka"),
		nearest_hour = as.POSIXct(paste("2000-01-01", paste(hour(ymd_hms(dateTime_hour)), "00", sep = ":")), tz = "Asia/Dhaka")
	) %>%
	
	select(timepoint, study_arm, hh_id, note, hh_id_note, dateTime, dateTime_min, nearest_min, dateTime_hour, nearest_hour, everything())

pm_data_base <-
	pm_data_not_censored %>%
	mutate(PM_Estimate = ifelse(PM_Estimate < 10, runif(0, 10, 1), PM_Estimate)) %>% 
	filter(PM_Estimate < 50000)  # use 10 ug/m3 as lower limit and 30000 ug/m3 as upper limit; https://berkeleyair.com/platform-for-integrated-cookstove-assessment/
# The PM monitor max is 50,000 ppm; anything above this is a fluke. Checked with Allie Sherris and she said that sometime when smoke directly hits the monitor the PM reading can go above 50,000

saveRDS(pm_data_base, file_out_pm_data_base)
```


# Check data quality

## Insufficient data
Were any hh recorded for less than 48 hours but not recorded as "Insufficient data"?

```{r}
pm_data_hour_per_monitor_pre_revision <-
	pm_data_base %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note, dateTime_hour) %>%
	summarise_at(
		vars(PM_Estimate),
		list(mean),
		na.rm = TRUE
	) %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note) %>%
	count() %>%
	ungroup() %>%
	rename(hours_recording = n)

pm_data_hour_per_monitor_pre_revision %>%
	filter(timepoint == "baseline") %>%
	filter(hours_recording < 24)

pm_data_hour_per_monitor_pre_revision %>%
	filter(timepoint == "endline") %>%
	# ggplot(aes(x = hours_recording))+
	# geom_histogram(binwidth = 5)
	filter(hours_recording < 24)

#20 of the 174 observations are not qc or school and <24 hours - not sure if we should throw these out like we did for baseline or not; for now I will NOT toss them out
```


Only exclude hh data if hr recorded was < 12 hours (this is arbitrary), (thuought about 10 hr, also arbitrary, there is only 1 hh that has 11 hr)
<12 hr

10G108351
8wDI21101274
4E277068

4EPP10188395
4EPP11277012
4EPP12500391
4EPP15184706




```{r}
# Label files will insufficient data
pm_data <- 
	pm_data_base %>%
	mutate(
		
		# Baseline (16 hh insufficient <24 hours; do not remove the qc and school that are <24 hours)
		# 10G108351_normal
		note = ifelse(timepoint == "baseline" & hh_id_note == "10G108351_normal", "insufficient data", note),
		hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "10G108351_normal", "10G108351_insufficient data", hh_id_note),
		# 8wDI21101274_normal
		note = ifelse(timepoint == "baseline" & hh_id_note == "8wDI21101274_normal", "insufficient data", note),
		hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "8wDI21101274_normal", "8wDI21101274_insufficient data", hh_id_note),
		# 4E277068_normal
		note = ifelse(timepoint == "baseline" & hh_id_note == "4E277068_normal", "insufficient data", note),
		hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "4E277068_normal", "4E277068_insufficient data", hh_id_note),
		# # 10G193127_normal
		# note = ifelse(timepoint == "baseline" & hh_id_note == "10G193127_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "10G193127_normal", "10G193127_insufficient data", hh_id_note),
		# 				# 8wDI18100959_normal
		# note = ifelse(hh_id_note == "8wDI18100959_normal", "insufficient data", note),
		# hh_id_note = ifelse(hh_id_note == "8wDI18100959_normal", "8wDI18100959_insufficient data", hh_id_note),
		# 				# 8wDI20101777_qc - less than 24 hr
		# note = ifelse(hh_id_note == "8wDI20101777_qc", "insufficient data", note),
		# hh_id_note = ifelse(hh_id_note == "8wDI20101777_qc", "8wDI20101777_insufficient data", hh_id_note),
		# # 4E109511_normal - less than 24 hr
		# note = ifelse(timepoint == "baseline" & hh_id_note == "4E109511_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "4E109511_normal", "4E109511_insufficient data", hh_id_note),
		# 		# 4E184125_normal - less than 24 hr
		# note = ifelse(timepoint == "baseline" & hh_id_note == "4E184125_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "4E184125_normal", "4E184125_insufficient data", hh_id_note),
		# 		# 4E188920_normal - less than 24 hr
		# note = ifelse(timepoint == "baseline" & hh_id_note == "4E188920_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "4E188920_normal", "4E188920_insufficient data", hh_id_note),
		# 		# 4E279919_normal - less than 24 hr
		# note = ifelse(timepoint == "baseline" & hh_id_note == "4E279919_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "4E279919_normal", "4E279919_insufficient data", hh_id_note),
		# 		# 4E280333_normal - less than 24 hr
		# note = ifelse(timepoint == "baseline" & hh_id_note == "4E280333_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "4E280333_normal", "4E280333_insufficient data", hh_id_note),
		# 		# 4E280680_normal - less than 24 hr
		# note = ifelse(timepoint == "baseline" & hh_id_note == "4E280680_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "4E280680_normal", "4E280680_insufficient data", hh_id_note),
		# 				# 4E280686_normal - less than 24 hr
		# note = ifelse(timepoint == "baseline" & hh_id_note == "4E280686_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "4E280686_normal", "4E280686_insufficient data", hh_id_note),
		# 				# 4E280792_normal - less than 24 hr
		# note = ifelse(timepoint == "baseline" & hh_id_note == "4E280792_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "4E280792_normal", "4E280792_insufficient data", hh_id_note),
		# 				# 4E280794_normal - less than 24 hr
		# note = ifelse(timepoint == "baseline" & hh_id_note == "4E280794_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "4E280794_normal", "4E280794_normal_insufficient data", hh_id_note),
		# 				# 4E283832_normal - less than 24 hr
		# note = ifelse(timepoint == "baseline" & hh_id_note == "4E283832_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "4E283832_normal", "4E283832_normal_insufficient data", hh_id_note),
		# 				# 44E302711_normal  - less than 24 hr
		# note = ifelse(timepoint == "baseline" & hh_id_note == "4E302711_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "4E302711_normal", "4E302711_insufficient data", hh_id_note),
		
		# 8wDH21291216_insufficient - but has 14 hours of data so include it
				note = ifelse(timepoint == "baseline" & hh_id_note == "8wDH21291216_insufficient data", "normal data", note),
		hh_id_note = ifelse(timepoint == "baseline" & hh_id_note == "8wDH21291216_insufficient data", "8wDH21291216_normal", hh_id_note),
		
		
		
		# Endline
		# 4E188395_normal - less than 24 hr
		note = ifelse(timepoint == "endline" & hh_id_note == "4EPP10188395_normal", "insufficient data", note),
		hh_id_note = ifelse(timepoint == "endline" & hh_id_note == "4EPP10188395_normal", "4EPP10188395_insufficient data", hh_id_note),
		# 4E188395_normal - less than 24 hr
		note = ifelse(timepoint == "endline" & hh_id_note == "4E188395_normal", "insufficient data", note),
		hh_id_note = ifelse(timepoint == "endline" & hh_id_note == "4E188395_normal", "4E188395_insufficient data", hh_id_note),
		# 44E302711_normal  - less than 24 hr
		note = ifelse(timepoint == "endline" & hh_id_note == "4EPP11277012_normal", "insufficient data", note),
		hh_id_note = ifelse(timepoint == "endline" & hh_id_note == "4EPP11277012_normal", "4EPP11277012_insufficient data", hh_id_note),
		# 		# 8WDI20101415_normal
		# note = ifelse(timepoint == "endline" & hh_id_note == "8WDI20101415_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "endline" & hh_id_note == "8WDI20101415_normal", "8WDI20101415_insufficient data", hh_id_note),
		
		# 	4EPP15184706_normal
		note = ifelse(timepoint == "endline" & hh_id_note == "4EPP15184706_normal", "insufficient data", note),
		hh_id_note = ifelse(timepoint == "endline" & hh_id_note == "4EPP15184706_normal", "4EPP15184706_insufficient data", hh_id_note),
		# 		# 8WDI20101415_normal
		# note = ifelse(timepoint == "endline" & hh_id_note == "8WDI20101415_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "endline" & hh_id_note == "8WDI20101415_normal", "8WDI20101415_insufficient data", hh_id_note),
		# 		# 8WDI20101574_normal
		# note = ifelse(timepoint == "endline" & hh_id_note == "8WDI20101574_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "endline" & hh_id_note == "8WDI20101574_normal", "8WDI20101574_insufficient data", hh_id_note),
		# 		# 8WDI20101723_normal
		# note = ifelse(timepoint == "endline" & hh_id_note == "8WDI20101723_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "endline" & hh_id_note == "8WDI20101723_normal", "8WDI20101723_insufficient data", hh_id_note),
		# 		# 	8wDI18100959 # Saw earlier but not on 210126
		# note = ifelse(timepoint == "endline" & hh_id_note == "8wDI18100959_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "endline" & hh_id_note == "8wDI18100959_normal", "8wDI18100959_insufficient data", hh_id_note),
		# 		# 4E184708
		# note = ifelse(timepoint == "endline" & hh_id_note == "4E184708_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "endline" & hh_id_note == "4E184708_normal", "4E184708_insufficient data", hh_id_note),
		# 4EPP12500391_normal
		note = ifelse(timepoint == "endline" & hh_id_note == "4EPP12500391_normal", "insufficient data", note),
		hh_id_note = ifelse(timepoint == "endline" & hh_id_note == "4EPP12500391_normal", "4EPP12500391_insufficient data", hh_id_note),
		# 		# 4EPP15184706_normal
		# note = ifelse(timepoint == "endline" & hh_id_note == "4EPP15184706_normal", "insufficient data", note),
		# hh_id_note = ifelse(timepoint == "endline" & hh_id_note == "4EPP15184706_normal", "4EPP15184706_insufficient data", hh_id_note)
		
		# Baseline: 8WI18 14-16 Sept; 17-19 Sept; 21-23 Sept, 24-26 Sept 2019
		# Baseline: 10GG9 12-14 Oct; 15-17 Oct; 20-22 Oct; 23-25 Oct, 27-29 Oct 2019
		# Endline: 4EPP11 1-3 Oct, 4-6 Oct, 7-9 Oct, 10-12 Oct, 13-15 Oct, 20-22 Oct, 24-26 Oct, 27-29 Oct 2020
		
		
		
		
		
	)

# pm_data %>%
# 	mutate(
# 			PM_Estimate = 
# 			case_when(
# 				dateTime > "2019-09-27" & dateTime < "2020-09-01" & hh_id == "8WI18" ~ 0,
# 				dateTime > "2019-10-30" & dateTime < "2020-09-01" & hh_id == "10GG9" ~ 0,
# 			 dateTime > "2020-10-30" & hh_id == "4EPP11" ~ 0
# 		)
# 	) %>%
# 	filter(hh_id %in% c("8WI18", "10GG9", "4EPP11")) %>%
# 	arrange(desc(dateTime))

# pm_data %>%
# 	filter(hh_id %in% "8WI18", dateTime > "2019-09-26") %>%
# 	select(dateTime, PM_Estimate)


pm_data_hour_per_monitor <-
	pm_data %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note, dateTime_hour) %>%
	summarise_at(
		vars(PM_Estimate),
		list(mean),
		na.rm = TRUE
	) %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note) %>%
	count() %>%
	ungroup() %>%
	rename(hours_recording = n)

pm_data_hour_per_monitor %>%
	filter(hours_recording < 24)
```

### File naming?
Are files named correctly? (above we fixed names for "insufficient data" here check "qc" - are qc files named qc, not qc files not qc?)

```{r, fig.height=5, fig.width=14}
hhid_with_qc <-
	pm_data %>%
	filter(note == "qc") %>%
	distinct(hh_id)

# pm_data_not_censored %>%
# 	filter(hh_id %in% hhid_with_qc$hh_id) %>%
# 	filter(hh_id == "4E179029") %>%
# 	View()

# 4E179029 is labeled as "qc" but there's no accompanying file to be the not qc file, so rename 4E179029_qc to 4E179029

pm_data <- 
	pm_data %>%
	mutate(
		note = ifelse(hh_id_note == "4E179029_qc", "normal", note),
		hh_id_note = ifelse(hh_id_note == "4E179029_qc", "4E179029_normal", hh_id_note)
	)

pm_data %>%
	filter(note == "qc") %>%
	distinct(hh_id)
```

8wDI18224646				
8wDI20274944				
10D193579				
10G105368				
10G105460				
10G108169				
10G116129				
10F113975				
9G600021				
10H286043
4E280792				
4E277017				
4E179247				
4F283027				
4F180644				
4F296441				
4E179624				
8WDI18224646				
8WDH21290495				
8WDI21101595
10D12193591				
10F40201619				
4EPP10188920				
4EPP11277068				
4EPP12283062				
4EPP15179029

On 26 Jan 2021 became 27 hh













# Create analysis datasets

# Check the dates, label for post-intervention (after baseline data was collect in Nov 2019)

The last baseline pre-intervention measurement was taken on 30 Oct 2019 
The last baseline intervention measurement was taken 18 Nov 2019

```{r}
# uses the actual minute (always rounds down to the nearest min)
pm_data_min <-
	pm_data %>%
	filter(note != "insufficient data") %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note, dateTime_min) %>%
	summarise_at(
		vars(PM_Estimate),
		list(mean),
		na.rm = TRUE
	) %>% 	
	ungroup()

# rounds to the nearest min (up or down)
pm_data_nearest_min <-
	pm_data %>%
	filter(note != "insufficient data") %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note, nearest_min) %>% # collapses all if they have the same date label, so I hope they don't! 
	summarise_at(
		vars(PM_Estimate),
		list(mean),
		na.rm = TRUE
	) %>% 	
	ungroup()
	

# uses the actual hour (always rounds down to the nearest hour)
pm_data_hour <-
	pm_data %>%
	filter(note != "insufficient data") %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note, dateTime_hour) %>%
	summarise_at(
		vars(PM_Estimate),
		list(mean),
		na.rm = TRUE
	) %>%
	ungroup() %>%
	mutate(
		over_100 = if_else(PM_Estimate > 100, 1, 0),
		over_500 = if_else(PM_Estimate > 500, 1, 0)
	)

# rounds to the nearest hour (up or down)
pm_data_nearest_hour <-
	pm_data %>%
	filter(note != "insufficient data") %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note, nearest_hour) %>%
	summarise_at(
		vars(PM_Estimate),
		list(mean),
		na.rm = TRUE
	) %>%
	ungroup() %>%
	mutate(
		over_100 = if_else(PM_Estimate > 100, 1, 0),
		over_500 = if_else(PM_Estimate > 500, 1, 0)
	)

pm_data_min %>%
	saveRDS(pm_data_min_rds)

pm_data_nearest_min %>%
	saveRDS(pm_data_nearest_min_rds)

pm_data_hour %>%
	saveRDS(pm_data_hour_rds)

pm_data_nearest_hour %>%
	saveRDS(pm_data_nearest_hour_rds)

write.csv(pm_data_min, pm_data_min_csv)

write.csv(pm_data_nearest_min, pm_data_nearest_min_csv)

write.csv(pm_data_hour, pm_data_hour_csv)

write.csv(pm_data_nearest_hour, pm_data_nearest_hour_csv)
```


```{r}
# pm_data_nearest_min %>%
# 	filter(hh_id_note == )
```

# Compare quality control and normal files
```{r, fig.width=18, fig.height=10}
qc_check_1 <-
	pm_data %>%
	filter(
		hh_id_note %in% 
			c(
				"10D193579_normal", "10D193579_qc",
				"10F113975_normal", "10F113975_qc",
				"10G105368_normal", "10G105368_qc",
				"10G105460_normal", "10G105460_qc",
				"10G108169_normal", "10G108169_qc",
				"10G116129_normal", "10G116129_qc"
			),
		timepoint == "baseline"
	) %>% 
	ggplot(aes(dateTime_min, PM_Estimate, color = hh_id_note)) +
	geom_line(na.rm = TRUE) +
	# geom_hline(yintercept = 100, color = "grey", lty = 2) + 
	# geom_hline(yintercept = 500, color = "black", lty = 2) +
	scale_x_datetime(labels = scales::date_format("%Y-%m-%d %H:%M")) + # labels = scales::date_format("%H:%M")
	scale_color_brewer(palette = "Paired") + # Unsuprisingly, palette = "Paired" is probably the best, max size is 12
	# Max size of palette = Accent is 8, Set1 is 9, of Set2 is 8, of Set3 is 10?
	# The palette = "Accent" or "Set[x]" worked better then the type = "divergent"
	# scale_color_brewer(type = "div", palette = "Spectral") + 
	theme_classic() +
	theme(
		legend.position = "none"
	) + 
	labs(
		title = "Quality control comparison",
		y = "PM 2.5 (ug/m3)",
		x = "Time"
	) +
	facet_wrap(. ~ hh_id, ncol = 3, scales = "free") # facet_grid splits ONLY on the horizontal or vertical direction while facet_wrap only has a horizontal dimension
# facet_grid(vertical ~ horizontal) - plots on the same row cannot have different y-axes, similarly, only one x-axis per column
# facet_wrap only stacks plots horizontally - each plot is indep so can each can have diff x and y axes

qc_check_2 <-
	pm_data %>%
	filter(
		hh_id_note %in% 
			c(
				"10H286043_normal", "10H286043_qc",
				"8wDI18224646_normal", "8wDI18224646_qc",
				"8wDI20101777_normal", "8wDI20101777_qc",
				"4E277017_normal", "4E277017_qc",
				"4E280792_normal", "4E280792_qc",
				"4F180644_normal", "4F180644_qc"
			),
		timepoint == "baseline"
	) %>%
	ggplot(aes(dateTime_min, PM_Estimate, color = hh_id_note)) +
	geom_line(na.rm = TRUE) +
	scale_x_datetime(labels = scales::date_format("%Y-%m-%d %H:%M")) + # labels = scales::date_format("%H:%M")
	scale_color_brewer(palette = "Paired") + 
	theme_classic() +
	theme(
		legend.position = "none"
	) + 
	labs(
		title = "Quality control comparison",
		y = "PM 2.5 (ug/m3)",
		x = "Time"
	) +
	facet_wrap(. ~ hh_id, ncol = 3, scales = "free")

qc_check_3 <-
	pm_data %>%
	filter(
		hh_id_note %in% 
			c(
				"4E280792_normal", "4E280792_qc",
				"4F283027_normal", "4F283027_qc",
				"8wDI20274944_normal", "8wDI20274944_qc",
				"9G600021_normal", "9G600021_qc",
				"4F296441_normal", "4F296441_qc",
				"4E179247_normal", "4E179247_qc"
			),
		timepoint == "baseline"
	) %>%
	ggplot(aes(dateTime_min, PM_Estimate, color = hh_id_note)) +
	geom_line(na.rm = TRUE) +
	scale_x_datetime(labels = scales::date_format("%Y-%m-%d %H:%M")) + # labels = scales::date_format("%H:%M")
	scale_color_brewer(palette = "Paired") + 
	theme_classic() +
	theme(
		legend.position = "none"
	) + 
	labs(
		title = "Quality control comparison",
		y = "PM 2.5 (ug/m3)",
		x = "Time"
	) +
	facet_wrap(. ~ hh_id, ncol = 3, scales = "free")

qc_check_1
qc_check_2
qc_check_3

# ggsave(
# 	here::here("docs", "qc_check_3.png"),
# 	plot = last_plot(),
# 	scale = 0.8,
# 	height = 6,
# 	width = 10,
# 	units = "in",
# 	device = "png"
# )

# Are the outdoor values reasonable?
pm_data %>%
	# filter(study_arm == "pre-intervention") %>%
	filter(
		note %in% c("mosque", "school")
	) %>% # PM07745L_20191115_1_4F180644and PM07776R_20191115_1_4F180644_QC; PM07781I_20191115_1_4F296441 and PM07782G_20191115_1_4F296441_QC
	# filter(dateTime_min > "2019-09-25", dateTime_min < "2019-09-26") %>%
	ggplot(aes(dateTime, PM_Estimate, color = hh_id_note)) + # aes(nearest_min, PM_Estimate, color = hh_id_note)
	geom_point(na.rm = TRUE) +
	# geom_hline(yintercept = 100, color = "grey", lty = 2) + 
	# geom_hline(yintercept = 500, color = "black", lty = 2) +
	scale_x_datetime(labels = scales::date_format("%Y-%m-%d")) + # "%Y-%m-%d %H:%M" # labels = scales::date_format("%H:%M")
	# theme(
	# 	legend.position = "none"
	# ) 
	# facet_grid(hh_id ~ ., scales = "free")
	facet_wrap(hh_id_note ~ ., scales = "free")

# pm_data_min$hh_id_note %>% unique()

pm_data %>%
	# filter(study_arm == "pre-intervention") %>%
	filter(
		note %in% c("mosque", "school")
	) %>% 
	group_by(hh_id_note) %>%
	summarise(min = min(PM_Estimate, na.rm =  TRUE), max = max(PM_Estimate, na.rm = TRUE))

```
Do NOT use geom_line because it make it look like the monitor was on in between these testing days



# Sample size
Now that we know the quality of the files is fine, determine the size of the data analysis sets

```{r}
pm_data_hour_per_monitor %>%
	filter(note %notin% c("qc", "insufficient data")) %>%
	group_by(timepoint, study_arm) %>%
	summarise_at(
		vars(hours_recording),
		list(total_hours = sum, mean_hours = mean, median_hours = median)
	) %>%
	left_join(
		pm_data %>%
	filter(note %notin% c("qc", "insufficient data")) %>%
			distinct(timepoint, study_arm, hh_id) %>%
			group_by(timepoint, study_arm) %>%
			count(),
		by = c("timepoint", "study_arm")
	) %>%
	select(timepoint, study_arm, n, everything())
```
Baseline
Intervention group: n = 111, hr = 5827, mean = 52 hr/hh
Comparison group: n = 63, hr = 3289, mean = 52 hr/hh
Outdoor group: n = 3, hr = 856, mean = 285 hr/location

Endline
Intervention group: n = 49, hr = 2463, mean = 50 hr/hh
Comparison group: n = 41, hr = 2101, mean = 51 hr/hh
Outdoor group: n = 3, hr = 369, mean = 123 hr/location



# Plot min-by-min data
```{r, fig.width=18, fig.height=10}
pm_data_min %>%
	filter(note %notin% c("qc", "insufficient data")) %>%
	ggplot(aes(dateTime_min, PM_Estimate, color = hh_id)) +
	geom_line(na.rm = TRUE) +
	# geom_hline(yintercept = 100, color = "grey", lty = 2) + 
	# geom_hline(yintercept = 500, color = "black", lty = 2) +
	theme(
		legend.position = "none"
	) + 
	facet_grid( ~ study_arm, scales = "free_y")

pm_data_nearest_min %>%
	filter(note %notin% c("qc", "insufficient data")) %>%
	ggplot(aes(nearest_min, PM_Estimate, color = hh_id)) +
	geom_line(na.rm = TRUE) +
	# geom_hline(yintercept = 100, color = "grey", lty = 2) +
	# geom_hline(yintercept = 500, color = "black", lty = 2) +
	scale_x_datetime(labels = scales::date_format("%H:%M")) +
	theme(
		legend.position = "none"
	) +
	facet_grid( ~ study_arm, scales = "free_y")


# Note that day 1 800 hr and day 2 800 hr are both plotted, so this graph has 2x as many points as study hh. 
pm_data_hour %>%
	filter(note %notin% c("qc", "insufficient data")) %>%
	ggplot(aes(dateTime_hour, PM_Estimate, color = hh_id)) +
	geom_line(na.rm = TRUE) +
	geom_hline(yintercept = 100, color = "grey", lty = 2) + 
	geom_hline(yintercept = 500, color = "black", lty = 2) +
	theme(
		legend.position = "none"
	) + 
	facet_grid( ~ study_arm, scales = "free")

pm_data_nearest_hour %>%
	filter(note %notin% c("qc", "insufficient data")) %>%
	ggplot(aes(nearest_hour, PM_Estimate, color = hh_id)) +
	geom_line(na.rm = TRUE) +
	geom_hline(yintercept = 100, color = "grey", lty = 2) +
	geom_hline(yintercept = 500, color = "black", lty = 2) +
	scale_x_datetime(labels = scales::date_format("%H:%M")) +
	theme(
		legend.position = "none"
	) +
	facet_grid( ~ study_arm, scales = "free")

pm_data_nearest_hour %>%
	filter(note %notin% c("qc", "insufficient data")) %>%
	group_by(study_arm, nearest_hour) %>%
	summarise(PM_Estimate_mean = mean(PM_Estimate)) %>%
	ggplot(aes(nearest_hour, PM_Estimate_mean, color = study_arm)) +
	geom_line(na.rm = TRUE) +
	geom_hline(yintercept = 100, color = "black", lty = 2) +
	geom_hline(yintercept = 500, color = "black", lty = 2) +
	scale_x_datetime(labels = scales::date_format("%H:%M")) +
	viridis::scale_color_viridis(
		discrete = TRUE,
		name = "Study arm",
		breaks = c("pre-intervention", "intervention", "outdoor"),
		labels = c("Pre-intervention", "Intervention", "Outdoor")
	) +
	labs(
		title = "PM 2.5 measurement by hour of the day",
		x = "Time",
		y = "PM 2.5 (ug/m3)"
	) +
	theme_classic()

```

```{r, fig.width=18, fig.height=10}
# pm_data_nearest_min %>%
# 	filter(note != "qc") %>%
# # replace 2000-01-02 with 2000-01-10 e.g. 2000-01-01 07:26:00      2000-01-02 07:26:00
# 	mutate(nearest_min_correct = str_replace(nearest_min, pattern = "2000-01-02", replacement = "2000-01-01")) %>% # # study_arm = str_extract(str_extract(file_name, "^(?:[^_]*_){2}[0-9]{1}"), "[0-9]$")
# 	arrange(desc(nearest_min))


# day_time_lims <- as.POSIXct(strptime(c("2000-01-01 00:00", "2000-01-01 23:59"), format = "%Y-%m-%d %H:%M"))

fig_pm_day <-
	pm_data %>% # 1,039,924 rows of data (each is every 10 seconds)
	filter(note %notin% c("qc", "insufficient data")) %>%
	
	# sample_n(100000) %>% # sampling only 10% of the data makes the CI appear, but I still don't see why they don't appear earlier! Are the se really so small they can't be seen?
	
	# slice(1:1000) %>%
	# group_by(study_arm, nearest_min) %>% 
	# arrange(desc(study_arm)) %>% 
	
  # arrange(timepoint, study_arm, note, hh_id, nearest_hour) %>% filter(note %in% c("school", "mosque")) %>% View()
	
		# 	dateTime_min = round_date(dateTime, unit = "minute"),
		# dateTime_min = as.POSIXct(dateTime_min) + 6 * 60 * 60, # , tz = "Asia/Dhaka"
		# dateTime_hour = round_date(dateTime, unit = "hour"),
		# dateTime_hour = as.POSIXct(dateTime_hour) + 6 * 60 * 60, # , tz = "Asia/Dhaka"
	
	# # make a consistent day (KEEPING ALL THE DATA, NOT AVERAGING OVER Multiple same minutes of different day)
	# mutate(
	# 	nearest_min =  as.POSIXct(paste("2000-01-01", paste(hour(ymd_hms(dateTime_hour)), minute(ymd_hms(dateTime_min)), sep = ":"))),
	# 	nearest_hour = as.POSIXct(paste("2000-01-01", paste(hour(ymd_hms(dateTime_hour)), "00", sep = ":")))
	# ) %>%
	
	ggplot(aes(nearest_min, PM_Estimate, color = study_arm, group = study_arm)) + # , fill = study_arm
	# geom_point(alpha = 0.001) +
	# geom_jitter(alpha = 0.1, width = 1500, height = 0) + # This width was trial and error
	geom_smooth(span = 0.1, se = TRUE) + # default is loess for <1000 points, gam (?),  local polynomial regression fitting, # 	`geom_smooth()` using method = 'gam' and formula 'y ~ s(x, bs = "cs")'

		# stat_smooth(level = 0.95, aes(fill = study_arm)) + 
	# stat_summary(geom = "ribbon", fun.data = "mean_cl_boot", alpha = 0.1) + # this does not work
 # stat_summary(geom = "line", fun = mean) +
	# stat_summary(geom = "smooth", fun.data = mean_cl_boot) +
	# geom_smooth(stat = 'summary', fun.data = mean_cl_boot) + 
	# span = alpha controls the size of the neighborhood used for estimating the point in question
	# geom_line(na.rm = TRUE) +
	# 	geom_smooth(
	#   	stat = 'summary', 
	#   	# color = 'red', fill = 'red', 
	#   	alpha = 0.5, 
	#     fun.data = median_hilow, # Hmisc::smedian.hilow, computes the sample median and a selected pair of outer quantiles having equal tail areas
	#   	fun.args = list(conf.int = 0.5) # plots the 25th and 75th percentiles, for max and min use conf.int = 1
	#   	) +
	geom_hline(yintercept = 25, color = "red", lty = 2) +
	# annotate("text", x = 0, y = 25, label = "25") +
	geom_hline(yintercept = 100, color = "black", lty = 2) +
	geom_hline(yintercept = 500, color = "black", lty = 2) +
	scale_x_datetime(
		labels = scales::date_format("%H:%M", tz = "Asia/Dhaka"), # tz = "Asia/Dhaka"
		breaks = scales::date_breaks("4 hours"),
		# limits = day_time_lims,
		expand = c(0, 0)
	) +
	scale_y_log10(breaks = c(10, 25, 100, 300), labels = c(10, 25, 100, 300)) +
	annotation_logticks() +
	scale_color_manual(
		name = "Monitor location",
		breaks = c("intervention", "comparison", "outdoor"),
		# labels = c("Pre-intervention", "Intervention", "Outdoor"),
		labels = c("\nInside \nintervention \nhouseholds \n", "\nInside \ncomparison \nhouseholds \n", "\nOutdoors \n"),
		values = c("#138b87",  "#430154", "#fde725"),
		# values = c("#7570b3",  "#d95f02", "#1b9e77")
	) +
	
	# purple: #430154   yellow: #fde725   teal: #138b87
	
	# purple: #7570b3, orange: #d95f02, teal: #1b9e77
	
	# viridis::scale_color_viridis(
	# 	discrete = TRUE,
	# 	name = "Study arm",
	# 	breaks = c("pre-intervention", "intervention", "outdoor"),
	# 	labels = c("Pre-intervention", "Intervention", "Outdoor"),
	# 	option = "D",
# 	# direction = -1#,
# 	begin = 0,
# 	end = 1
# ) +
labs(
	title = "PM2.5 measurement by hour of the day",
	x = "Time",
	y = "PM2.5 (ug/m3)"
) +
	theme_classic() +
	theme(
		legend.background = element_blank(),
		panel.spacing = unit(2, "lines")
	) + 
	facet_wrap( ~ timepoint)

fig_pm_day

ggsave(
	here::here("docs", "PM_by_hour_of_day_log_smooth_span_0.3.png"),
	plot = last_plot(),
	scale = 1,
	height = 6,
	width = 10,
	units = "in",
	device = "png"
)

pm_data %>% 
	filter(note %notin% c("qc", "insufficient data")) %>%
	filter(study_arm == "intervention", timepoint == "baseline") %>%
	select(nearest_min) %>% 
	unique() %>% 
	head()

pm_data %>% 
	filter(note %notin% c("qc", "insufficient data")) %>%
	filter(study_arm == "intervention", timepoint == "baseline") %>%
	# pull(nearest_min) %>% 
	# unique() %>% 
	# head()
		filter(nearest_min == "2000-01-01 07:10:00 +06") %>%
	# filter(nearest_min %in% c("2000-01-01 07:10:00 +06")) %>% # 269 rows "2000-01-01 07:15:00 +06" When I do 
	group_by(hh_id, nearest_min) %>%
	slice(1) %>%
	ungroup() %>% # still has 111 rows, one for each hh 
	ggplot(aes(x = nearest_min, y = PM_Estimate)) +
	geom_point()
	stat_summary(geom = "linerange" , fun.data = mean_cl_normal())
	
```
"2000-01-01 07:10:00 +06" "2000-01-01 07:11:00 +06" "2000-01-01 07:12:00 +06" "2000-01-01 07:13:00 +06" "2000-01-01 07:14:00 +06" "2000-01-01 07:15:00 +06"



# Hourly summary

I can't just look at how many hours the monitor was above 100 or 500, because the monitors were in place for different amounts of time. 

One way to summarize is to this would be to calculate the total number of hours it was operating, then determine the fraction of 24 hours that was over 100 or 500 ppm 

```{r}
pm_data_hour_summary_by_fraction_time_recorded <-
	pm_data_hour %>%
	filter(note != "qc") %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note) %>%
	summarize_at(
		vars(over_100, over_500),
		list(sum)
	) %>%
	gather(-c(timepoint, study_arm, note, hh_id, hh_id_note), key = "indicator", value = "hr_above_threshold") %>%
	left_join(pm_data_hour_per_monitor %>% select(hh_id_note, hours_recording), by = "hh_id_note") %>%
	mutate(
		pc_time_above_threshold = hr_above_threshold / hours_recording,
		hr_day_above_threshold = pc_time_above_threshold * 24
	)
```

Another way to summarize the data, which is what Allie has done for the ventilation project, it so normalize all test to 48 hours just cut off all data after 48 hours, and use this. The means that each time period of the day is measured twice and measurements are unaffected by what time of day they started. (If they started just before cooking breakfast and the monitor ran for 52 hours then cooking breakfast would be captured 3 times, rather than just twice with a 38 hour time period or if the recording has started just a bit later.)

```{r}
pm_data_hour_summary_by_48_hr <-
	pm_data_hour %>%
	filter(note != "qc") %>%
	group_by(timepoint, hh_id_note) %>%
	slice(1:48) %>% # took the first 48 hours, but some had less than 48 hours (I only tossed if less than 24)
	ungroup() %>%
	group_by(timepoint, study_arm, note, hh_id, hh_id_note) %>%
	summarize_at(
		vars(over_100, over_500),
		list(sum)
	) %>%
	gather(-c(timepoint, study_arm, note, hh_id, hh_id_note), key = "indicator", value = "hr_above_threshold") %>%
	mutate(
		pc_time_above_threshold = hr_above_threshold / 48, # This isn't right - need to divide by actual recording time
		hr_day_above_threshold = pc_time_above_threshold * 24 
	)

pm_data_hour_summary_by_48_hr %>%
	group_by(timepoint, study_arm, indicator) %>%
	summarise(median = median(hr_day_above_threshold), mean = mean(hr_day_above_threshold), sd = sd(hr_day_above_threshold)) %>%
	arrange(indicator, timepoint, study_arm)
```



## Plot data

Add pairwise p-value comparisons 
https://www.r-bloggers.com/add-p-values-and-significance-levels-to-ggplots/

```{r, fig.width=18, fig.height=10}
pm_data_hour_summary_comparisons <- 
	list(
		c("Inside \nnew intervention \nhouseholds", "Inside \non-going intervention \nhouseholds"),
		# c("Inside \nnew intervention \nhouseholds", "\nOutdoors \n"),
		c("Inside \non-going intervention \nhouseholds", "\nOutdoors \n")
	)

indicator.labs <- 
	c(
		over_100 = "PM2.5 over 100 ug/m3",
		over_500 = "PM2.5 over 500 ug/m3"
	)

pm_data_hour_summary_by_48_hr %>% 
	mutate(
		study_arm = 
			ordered(
				study_arm,
				levels = c("pre-intervention", "intervention", "outdoor"),
				labels = c("Inside \nnew intervention \nhouseholds", "Inside \non-going intervention \nhouseholds", "\nOutdoors \n")
			)
	) %>%
	# for the method where the entire recording time is used, replace "pm_data_hour_summary_by_48_hr" with 
	# "pm_data_hour_summary_by_fraction_time_recorded" and change the title to (Hours above threshold based on entire recording period)
	ggplot(aes(x = study_arm, y = hr_day_above_threshold, color = study_arm)) +
	geom_boxplot() +
	geom_jitter(alpha = 0.2, width = 0.4, height = 0) +
	# scale_color_discrete() + 
	ggpubr::stat_compare_means(
		comparisons = pm_data_hour_summary_comparisons,
		label = "p.format", #"p.signif" 
		method = "t.test",
		
		# label.y = c(17, 20, 23),
		label.y = c(17, 20),
		hide.ns = TRUE#,
		# ref.group = ".all."
	) +
	viridis::scale_color_viridis(
		discrete = TRUE,
		# The following is to control the legend
		name = "Monitor location",
		labels = c("\nInside \nnew intervention \nhouseholds \n", "\nInside \non-going intervention \nhouseholds \n", "\nOutdoors \n")
	) +
	labs(
		# title = "Hours per day exceeding PM2.5 threshold",
		title = "Hours exceeding 100 ug/cm3 PM2.5 per day",
		y = "Hours per day",
		x = "Monitor location"
	) +
	theme_bw() +
	theme(
		legend.position = "none",
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		# axis.title.x = element_blank(),
		# axis.text.x = element_blank(),
		axis.ticks.x = element_blank()
	) +
	coord_cartesian(ylim = c(0, 23)) +
	facet_grid(
		~ timepoint # , # 	indicator ~ timepoint,
		# labeller = labeller(indicator = indicator.labs)
	)

ggsave(
	here::here("docs", "pm_data_hour_summary_by_48_hr.png"),
	plot = last_plot(),
	scale = 1,
	height = 6,
	width = 10,
	units = "in",
	device = "png"
)
```

```{r}
	pm_data_hour %>% 
	group_by(timepoint, study_arm, hh_id) %>% 
	summarise(
		time_range = max(dateTime_hour) - min(dateTime_hour),
		hh_mean = mean(PM_Estimate),
		hh_sd = sd(PM_Estimate)
	) %>% 
	ungroup() %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(
		mean(time_range),
		mean(hh_mean), 
		sd(hh_sd)
	) %>% 
	write_csv("/Users/ChrisLeBoa/GitHub/RohingyaLPG/4_data/pm_hh_av_220630.csv")



pm_data_average <-  
	pm_data_hour %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(
		max(dateTime_hour) - min(dateTime_hour),
		mean(PM_Estimate), 
		sd(PM_Estimate)
	)

pm_data_average %>% 
	knitr::kable()
	
```

Indoor time weighted PM Average 
```{r}
survey_data %>% 
	group_by(timepoint, study_arm, hh_id) %>% 
	summarise(mean_hr_outside = mean(hours_outside)) %>% 
	ungroup() %>% 
	group_by(timepoint, study_arm) %>% 
	summarise(mean_hr_outside_hh = mean(mean_hr_outside)) 


```

